---
title: "Sea otter survey map creator"
author: "Wendel Raymond"
date: "June 8, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Map generator for sea otter surveys
This script will make a map of where sea otter surveys should be conducted based on a point. All you will need is the Lat/Long of your site!

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(sp)
library(rgdal)
library(rgeos)
library(raster)
library(gdistance)
library(spatstat)
library(leaflet)
library(DT)
library(sf)
```

```{r load data}
## Prince of Wales Water Polygon ##
h2o.utm <- readOGR(dsn = "../ALL_DATA/spatial_data", layer = "POW_water_UTM")
h2o.latlong <- spTransform(h2o.utm, CRS("+init=epsg:4326"))
```

## Create survey area
### Where is your site?
Input Lat/Long in decimal degrees below. Make sure that the site is "in the water"! Otherwise this wont work.
```{r site}
site <- structure(list(id = "site", longitude = -132.899774, latitude = 55.192876), .Names = c("id", "longitude", "latitude"), class = "data.frame", row.names = c(NA, -1L))
xy <- site[,c(2,3)]

site <- SpatialPointsDataFrame(coords = xy, data = site,
                               proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))

site <- spTransform(site, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0"))
```

### Make the polygon
Some spatial math happens here. Its scary.
```{r}
buff <- gBuffer(site, byid = TRUE, width = 3704, quadsegs = 10) # create buffer
buff <- spTransform(buff, CRS("+init=epsg:4326")) # transform buffer
buff.water <- gIntersection(h2o.latlong, buff, byid = TRUE) # clip the buffer area by water so we only have water area left
buff.water <- spTransform(buff.water, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0")) # change projection back to UTM
e <- extent(buff.water) # save the extent of the polygon for later use
r <- raster(xmn = e@xmin, xmx = e@xmax, ymn = e@ymin, ymx = e@ymax, ncol = (e@xmax - e@xmin) / 50, nrow = (e@ymax - e@ymin) / 50, crs = "+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0") # create a raster with 50 X 50 meter grid cells. This raster is "empty"
wr <- rasterize(buff.water, r, crs = "+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0") # append water polygon data to raster. This raster is "full"
wr[wr] <- 50 # convert all raster cell values to a value of 50 (because 50 meters)
wt <- transition(wr, transitionFunction = function(x){50}, directions = 8) # conver raster to transition layer (required for accCost() below)
wt <- geoCorrection(wt, type = "r", scl = FALSE) # not really sure what this actually does but you have to do it
sa <- accCost(wt, site) # calculate the cumulative cost distance
values(sa) <- (values(sa) * 50) # multiply cost values by 50 to reflect cost in terms of actual distance
sa[values(sa) > 3700] <- NA # Convert cost rasters > 3700 to NA, now the raster will reflect the true survey area
survey.poly <- rasterToPolygons(sa, dissolve = TRUE) # covert raster to polygon
survey.poly.utm <- spTransform(survey.poly, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")) # define projection
survey.poly.latlong <- spTransform(survey.poly, CRS("+init=epsg:4326"))
```

### Whats it look like?
```{r make map}
site.latlong <- spTransform(site, CRS("+init=epsg:4326"))
leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(data = site, ~longitude, ~latitude, color = "black", fillOpacity = 1, stroke = FALSE, radius = 5) %>% 
  addPolygons(data = survey.poly.latlong, stroke = NA, fillColor = "yellow", fillOpacity = 0.5, group = "POW")

#leaflet() %>% 
  #addTiles(owi.usgs.gov/blog/basemaps) %>% 
  #addCircleMarkers(data = site, ~longitude, ~latitude, color = "black", fillOpacity = 1, stroke = FALSE, radius = 5) %>% 
  #addPolygons(data = survey.poly.latlong, stroke = NA, fillColor = "yellow", fillOpacity = 0.5, group = "POW")
```


