---
title: "EDA_salmon_data"
author: "Lia Domke"
date: "10/7/2019"
output: html_document
---

# Libraries
```{r libraries, echo = FALSE}
library(tidyverse)
library(corrgram)
library(MASS)
library(pscl)
library(visreg)
library(readxl)
library(lubridate)
library(mgcv)
library(reshape2)
library(cowplot)
```

# Data Entry
This file is based on the "DataCleaning_Seine_2019" R Markdown script. Extracted relevant salmon abundances (with zeros where we seined but caught no salmon), environmental information (from YSI meter), habitat information (i.e. shoot/flowering shoot density/m2), and otter density by site. 

allsites - includes distance to anadramous stream for all noaa sites and 17/19 sites. 
```{r, echo = FALSE}
dat <- read.csv("FISH604_combined_10-5-19.csv")
allsites <- read_xls("../ALL_DATA/Lia_fish/dist2_anad_allsites_102319.xls", sheet = 1)
biom <- read.csv("../ALL_DATA/seagrass_biomass_conversions.csv") 
eel17 <- read.csv("..//ALL_DATA/seagrass_biometrics_CLEAN.csv")
env17 <- read.csv("../ALL_DATA/eelgrass_bio_sed_transect_derived.csv")
name <- read.csv("site_code_names.csv", header = TRUE)

```
# Data Clean up
## Main data frame
```{r}
# Take a look at data
glimpse(dat)

# do some minor clean up 
dat <- dat[-42,-1]
dat$year <- as.factor(dat$year)
dat[,21:25] <- data.frame(lapply(dat[,21:25], as.numeric), stringsAsFactors = FALSE) # make sure salmon abundance is numeric
dat1 <- dat %>%
  rowwise() %>%
  mutate(abundance = sum(SALCHIN, SALCHUM, SALCOHO, SALPINK, SALSOCK))

dat2 <- dat1 %>%
  filter(juli_date < 180)
```

## Distance
allsites needs to be combined with environmental information about the sites
```{r}
str(allsites)
# 2017 2019 sites information is at the bottom
dist <- allsites[616:661,-c(1:2,4:6,11)]

dist17 <- dist %>%
  filter(habitat == "eelgrass", year == "2017")%>%
  rename(site = site_event) 

dist19 <- dist %>%
  filter(habitat == "eelgrass", year == "2019")%>%
  rename(site = site_event) 

names1 <- name %>%
  dplyr::select(site, site_code)
names1 <- names1[-c(22:30),]
names1 <- data.frame(lapply(names1, as.character), stringsAsFactors = FALSE)
colnames(names1) <- c("place", "site") # make sure what you are joining has the same column name
dist17.2 <- left_join(dist17, names1, by = "site") %>% # join by site
  dplyr::select(-site) %>%  # remove site code column
  rename(site = place) # rename site name

# slight changes to names on dist19
levels(as.factor(dist19$site))
dist19$site <- as.factor(dist19$site)
levels(dist19$site)[levels(dist19$site)=="Naukati"] <- "Naukati Bay"
levels(dist19$site)[levels(dist19$site)=="South Wadleigh"] <- "South Wadleigh Island"
levels(dist19$site)[levels(dist19$site)=="Chusini"] <- "Chusini Cove"
levels(dist19$site)[levels(dist19$site)=="Goats mouth Inlet"] <- "Goats mouth inlet"
levels(dist19$site)[levels(dist19$site)=="Kaguk Bay"] <- "Kaguk Cove"

dist_comb <-rbind(dist19, dist17.2)
dist_all <- dist_comb %>%
  mutate(dist_anad_km = NEAR_DIST/100) %>%
  dplyr::select(-NEAR_DIST)

# combine with total data
dist_all$year <- as.factor(dist_all$year)

dat3 <- left_join(dat2, dist_all)
```

## Seagrass biomass
```{r}
str(biom) 
# 2019
# convert biomass to g/m2 for both shoots and flowering shoots
# note: flowering shoot estimation is likely an underestimation because 
# flowering biomass is more (because they're taller) than normal shoots. 
biom_site <- biom %>%
  mutate(shoot_biomass_gm2 = (avg_biomass * density_m2)) %>% 
  mutate(flowering_biomass_gm2 = (avg_biomass * flowering_m2)) %>%
  mutate(total_biomass_gm2 = (flowering_biomass_gm2 + shoot_biomass_gm2)) %>%
  group_by(site) %>%
  summarise(avg_biom_site_gm2 = mean(total_biomass_gm2)) %>%
  mutate(year = "2019")

# 2017
str(eel17)

biom17 <- eel17 %>%
  mutate(shoot_dw = shoot_foil_dw - shoot_foil, na.rm = T) %>%
  group_by(site, quadrat) %>%
  summarise(avg_shoot_dw = mean(shoot_dw))

eel_hab17 <- env17 %>%
  mutate(year = "2017") %>%
  mutate(date = ymd(date)) %>%
  dplyr::select(quadrat, site, date, year, date_julian,
         eelgrass_shoots_msq,flowering_shoots_msq) %>%
  na.omit()

df <- left_join(eel_hab17, biom17) %>%
  mutate(total_shoot_m2 = (eelgrass_shoots_msq + flowering_shoots_msq)) %>%
  mutate(total_biomass_gm2 = total_shoot_m2 * avg_shoot_dw, na.rm = T) %>%
  group_by(site) %>%
  summarise(avg_biom_site_gm2 = mean(total_biomass_gm2, na.rm = T))

# change site names in 2017 for df 
names1 <- name %>%
  dplyr::select(site, site_code)
names1 <- names1[-c(22:30),]
names1 <- data.frame(lapply(names1, as.character), stringsAsFactors = FALSE)
colnames(names1) <- c("place", "site") # make sure what you are joining has the same column name
df2 <- left_join(df, names1, by = "site") # join by site

df3 <- df2 %>%
  dplyr::select(-site) %>%  # remove site code column
  rename(site = place) %>% # rename site name
  mutate(year = "2017")

# Combine 2017 and 2019 biomass, with e/ other and then the main df (dat)
biom_all <- rbind(df3, biom_site)
biom_all$year <- as.factor(biom_all$year)


dat4 <- left_join(dat3, biom_all, by = c("site", "year"))
```


# Exploratory Analaysis (EDA)
```{r}
# visualize relationships among variables: scatterplot matricies
dat <- dat4
library(corrgram)
corrgram(dat[,c(4,5,8,14,17,18,20,21,24:30,34:35)], lower.panel=panel.shade, upper.panel=panel.ellipse,
         diag.panel=panel.density)

pairs(dat[,c(4,5,8,14,17,18,20,21,24:30,34:35)], lower.panel = panel.smooth)

# is there a correlatino between sea otter density and seagrass density
glimpse(dat)
cor(dat$avg_density, dat$avg_shoot, use = "complete.obs")
# based on pearson correlation there is a slight negative correlation. Is it statistical?
plot(dat$avg_density, dat$avg_shoot)
summary(lm(avg_shoot ~ avg_density + juli_date, data = dat))
# nope, should probably include them together in the models...

# graph abundance data 
dat$site <- reorder(dat$site, -dat$avg_density)
dat %>%
  group_by(site, avg_density, year) %>%
  summarise(abundance = as.numeric(sum(SALCHIN, SALCHUM, SALCOHO, SALPINK, SALSOCK))) %>%
  ggplot() + geom_bar(aes(x = site, y = abundance, fill = year), stat = "identity", position = "dodge") + theme(axis.text.x = element_text(angle = 90))

# look at the sites against the average sea otter density
ggplot(data = dat) + geom_bar(aes(x = site, y = avg_density, fill = year), stat = "identity") + theme(axis.text.x = element_text(angle = 90))


# visualize distribution of salmon abundance
hist(x = dat$abundance)
boxplot(dat$abundance)
# distribution of abundances
# Can see that there are a lot of zeros and a few low, some mid, and only a few high abundances
plot(table(dat$abundance))


```

# Models
## Binomial models 
(1) Predictor variables: avg_density, juli_date, 
(2) Binomial family (salmon is present or not)
(3) Logit link (because its the binomial family)
### Graphical exploration
```{r}
hist(as.numeric(dat$abundance > 0))
dat$year <- as.factor(dat$year)
summary(dat)

plot((abundance > 0) ~ avg_density, data = dat)
plot((abundance >0) ~ avg_shoot, data = dat)
plot((abundance >0) ~ avg_flowering, data = dat)
plot((abundance >0) ~ juli_date, data = dat)
plot((abundance>0) ~ avg_biom_site_gm2, data = dat)
plot((abundance>0) ~ dist_anad_km, data = dat)
# hard to see any real patterns of presence of salmon with otter density or shoot density, flowering density
# or julian date

table((dat$abundance >0), dat$year)
# there are more sites with salmon than without in 2019, likely due to the time of sampling
# makes sense that 2017 has about half and half due to the even spread of sampling across the summer. 
table((dat$abundance >0), dat$juli_date)
# appears that there are more "false" i.e. no salmon later in the summer when compared to earlier in the summer, once again makes sense based on what we know about out migration of salmon. 
plot(abundance ~ year, data = dat)

dat$binomial[dat$abundance > 0] <- 1
dat$binomial[dat$abundance == 0] <- 0  
# convert to 0, 1 for modelling

plot(dat$juli_date, dat$binomial)

ggplot(dat, aes(avg_density, binomial, color = year)) + geom_jitter(width = 0.5, height = 0.05) + facet_wrap(~year, ncol = 1)

ggplot(dat, aes(dist_anad_km, binomial, color = year)) + geom_jitter(width = 0.5, height = 0.05) + facet_wrap(~year, ncol = 1)

ggplot(data = dat, aes(x = reorder(site, -avg_density), y = avg_density, fill = year)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90)) +facet_wrap(~year, ncol = 1)

# finally lets look at a corrigram of the response variables
library(corrgram)
corrgram(dat[,c(1,6,8,19,21,24,30)], lower.panel=panel.shade, upper.panel=panel.ellipse,
         diag.panel=panel.density)
# No distinguishable pattern aside from the decline in abundance over time
```

### Model fitting and selection
Want to start by fitting a full model including interaction

Haven't incorporated dist anad or biomass seagrass here yet
```{r}
#Try a fit that includes sea otter density and date, including an interaction
fit1 <- glm(binomial ~ avg_density*juli_date*year, family = binomial(link = logit), data = dat)
summary(fit1)
# try without interaction (not significant)
fit1.red <- glm(binomial ~ avg_density+juli_date+year, family = binomial(link = logit), data = dat)
summary(fit1.red)

fit1.time <- glm(binomial ~ juli_date+year, family = binomial(link = logit), data = dat[-41,])
summary(fit1.time)
# compare AIC values and Analysis of Deviance
AIC(fit1, fit1.red, fit1.time) # reduced has slightly lower AIC value
anova(fit1, fit1.red, fit1.time, test = "Chisq") # the null hypothesis is rejected indicating
# that the true model is the second model that includes avg_density, juli_date, and y ear
anova(fit1, test = "Chisq")

# Try another fit using seagrass densities and date
# If the seagrass and sea otter have a hypothesized relationship (based on WR work) they should 
# be in included separately. 
fit2.intx <- glm(binomial ~ avg_shoot * avg_flowering * juli_date * year, family= binomial(link = logit), data = dat[-41,])
summary(fit2.intx) # somethign weird happened here... it did not converge...
# drop the interactions, not significant
fit2 <- glm(binomial ~ avg_shoot + avg_flowering + juli_date + year, family = binomial(link = logit), data = dat[-41,])
summary(fit2)
# looks like julian date is important.... 
# lets drop the other non significant values and see 
fit2.red <- glm(binomial ~ juli_date + year, family = binomial(link = logit), data = dat[-41,])
summary(fit2.red)

anova(fit2.intx, fit2, fit2.red, test= "Chisq")
AIC(fit2.intx, fit2, fit2.red) # fit 2 reduced only reduces the AIC values by 3... 
anova(fit2.intx, test = "Chisq")

# How do we look at these two models with different parameters if the  models aren't nested? 

```

### Visualize the binomial models 
```{r}
visreg(fit1.red, scale = "response", overlapy = T, gg=T)
visreg(fit2, scale = "response", overlay = T, gg = T)

# diagnostic plots taken with a grain of salt for binomial models
par(mfrow=c(2,2))
plot(fit1.red, which=1:4)

# potential outliers with large influence based on Cook's distance
dat[4,] # Kaguk (high density, seined in july)
dat[6,] # Guktu (high, density, seined in August)

# Try and refit the model (fit1.red) without these outliers
fit1.red.up <- glm(binomial ~ avg_density+juli_date+year, family = binomial(link = logit), data = dat[-c(4,6),])
summary(fit1.red.up)

visreg(fit1.red.up, scale = "response", overlap = T, gg=T)
par(mfrow=c(2,2))
plot(fit1.red.up, which=1:4) # does this look better?

```

## Abundance based models (Poisson and Negative Binomial)
Okay so we looked at the data using a strictly binomial model (i.e. presence absence) of all salmon species. 
Can we try to model the salmon abundance (this makes the assumption that all salmon species are influenced by the same conditions)
### Graphical exploration of salmon abundance
```{r}
table(dat$SALCHIN); table(dat$SALCHUM); table(dat$SALCOHO); table(dat$SALPINK); table(dat$SALSOCK)
table(dat$SALCHIN>0); table(dat$SALCHUM>0); table(dat$SALCOHO>0); table(dat$SALPINK>0); table(dat$SALSOCK>0)
# Notice that there are many more zeros than positive numbers. 
table(dat$abundance>0)
prop.table(table(dat$abundance>0))
# 68% of the data has a positive abundance
prop.table(table(dat$SALCHUM>0))
prop.table(table(dat$SALPINK>0))
# more positive abundances of chum than pink, but we'll include all salmon together in the model using
# abundance

hist(dat$abundance)
hist(dat$SALCHUM)
hist(dat$SALPINK)
hist(dat$SALCOHO)
# yup a lot of zeros but some positive values. 
```

```{r, echo = FALSE}
# try to fit to a glm using poisson distribution
# have to add a constant to abundance data because poisson doens't like zeros
# this glm framework automatically transforms the data
fit <- glm(abundance+1 ~ avg_density*year*juli_date*I(juli_date^2)*avg_biom_site_gm2*dist_anad_km, data = dat, family = poisson)
summary(fit)

# residuals vs fitted appear to show an increase in variance, check summary output
# the normal QQ plot indicates a couple worrisome points (case numbers 16 and 25 and 9) ; however
# the majority of the points fall along the qqline
plot(fit)
summary(fit)
# the residual deviance is greater than the df--this could indicate that there is overdispersion in the data

# try fitting a quasi poission model to better account for the overdispersion
fit.qp <- glm(abundance+1 ~ avg_density*year*juli_date*I(juli_date^2), data = dat, family = quasipoisson)
summary(fit.qp)
#year, date and their interactions appear to be significant. Residual deviance is extremely higher than
# than df.... overdispersion. data looks weird
plot(fit.qp)
# the residuals against the fitted values looks somewhat better; however, the qqplot looks like it might
# have a stepwise pattern. A few spurrious points (case numbers 16, 9, 29)

# try even better accounting for the overdispersion through fitting a negative binomial with includes
# another parameter (theta) to better account for increasing variance
fit.nb <- glm.nb(abundance ~ year*juli_date*avg_density+I(juli_date^2), data = dat, init.theta=0.535, control=glm.control(maxit = 50))
summary(fit.nb)
# for some reason can't run the glm.nb including *I(juli_date^2) it says that the algorithm does not converge.... even if you use the initial theta of the model without the parameter.have to add it in

fit.nb2 <- glm.nb(abundance ~ year:juli_date + juli_date:avg_density + year:avg_density + juli_date + avg_density + year, data = dat)
summary(fit.nb2)
library(lmtest)
# Which model is better?
lrtest(fit.nb2, fit.nb) # there isn't a significant reduction of deviance by including the other interaction variable. drop density*juliday
AIC(fit.nb2); AIC(fit.nb) # basically the same AIC value 

# Out of curiosity lets look at if we drop all interaction terms aside form julday:year
fit.nb3 <- glm.nb(abundance ~ avg_density + juli_date + year + juli_date*year, data = dat)
summary(fit.nb3)
lrtest(fit.nb3, fit.nb2)

# Since we know there is a high abundance of zero in the data try and fit the hurdle model
library(pscl)
fit.hurdle <- hurdle(abundance ~ avg_density + juli_date + year, data = dat[-41,], dist = "negbin")
summary(fit.hurdle)


###### try glm with cubic date
fit.nb.linear <- glm.nb(abundance ~ year+juli_date+avg_density+I(juli_date^2), data = dat, control=glm.control(maxit = 50))

summary(fit.nb.linear)

fit.nb.linear.PNK <- glm.nb(SALPINK ~ year+juli_date+avg_density+I(juli_date^2)+avg_biom_site_gm2+dist_anad_km, data = dat,init.theta=0.535, control=glm.control(maxit = 5000))
summary(fit.nb.linear.PNK)
visreg(fit.nb.linear.PNK, scale = "response", partial = TRUE)
```

# GAM models
```{r}

# try something else out with more flexibility for the julian date
library(mgcv)
gam.all <- gam(abundance ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km, data = dat, family = nb(link = "log"))

summary(gam.all)

a1 <- visreg(gam.all, "juli_date", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab("Julian Date") + ylab(NULL) + 
  geom_point() + coord_cartesian(ylim = c(0, 300))

a2 <- visreg(gam.all, "avg_density", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Sea otter density (#/",km^2,")"))) + 
  ylab(NULL) + geom_point() + coord_cartesian(ylim = c(0, 300))
  
a3 <- visreg(gam.all, "avg_biom_site_gm2", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Eelgrass density (g/",m^2,")"))) + 
  ylab(NULL) + geom_point() + coord_cartesian(ylim = c(0, 300))

a4 <- visreg(gam.all, "dist_anad_km", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Distance to anadromous stream (",km^2,")"))) + 
  ylab(NULL) + geom_point() + coord_cartesian(ylim = c(0, 300))

plot1 <- plot_grid(a1, a4, a2, a3, align = "hv", label_y = "Salmon abundance", vjust = 0)
save_plot("WSNPlot1.jpg", plot1)
```


## Gam by species
```{r}
#BY species
gam.coho <- gam(SALCOHO ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km, data = dat, family = nb(link = "log"))

# coho 
summary(gam.coho)
visreg(gam.coho, scale = "response")
co.so <- visreg(gam.coho, "avg_density", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Sea otter density (#/",km^2,")"))) + 
  ylab("Coho abundance") + geom_point() + coord_cartesian(ylim = c(0, 150))

co.eel <- visreg(gam.coho, "avg_biom_site_gm2", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Eelgrass biomass (g/",m^2,")"))) + 
  ylab("Coho abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))

co.dist <- visreg(gam.coho, "dist_anad_km", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Distance from anadromous stream (",km^2,")"))) + 
  ylab("Coho abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))  
# Pink salmon
gam.pink <- gam(SALPINK ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km, data = dat, family = nb(link = "log"))

summary(gam.pink)
visreg(gam.pink)

p.so <- visreg(gam.pink, "avg_density", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Sea otter density (#/",km^2,")"))) + 
  ylab("Pink abundance") + geom_point() + coord_cartesian(ylim = c(0, 150))

p.eel <- visreg(gam.pink, "avg_biom_site_gm2", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Eelgrass density (g/",m^2,")"))) + 
  ylab("Pink abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))

p.dist <- visreg(gam.pink, "dist_anad_km", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(NULL) + 
  ylab("Pink abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))  

gam.chum <- gam(SALCHUM ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km, data = dat, family = nb(link = "log"))

summary(gam.chum)
visreg(gam.chum)
#
ch.so <- visreg(gam.chum, "avg_density", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Sea otter density (#/",km^2,")"))) + 
  ylab("Chum abundance") + geom_point() + coord_cartesian(ylim = c(0, 150))

ch.eel <- visreg(gam.chum, "avg_biom_site_gm2", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(expression(paste("Eelgrass density (g/",m^2,")"))) + 
  ylab("Chum abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))

ch.dist <- visreg(gam.chum, "dist_anad_km", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab(NULL) + 
  ylab("Chum abundance") + geom_point() +
  coord_cartesian(ylim = c(0, 150))  

plot.dist <- plot_grid(p.dist, ch.dist, co.dist, align = "hv", vjust = 0)
save_plot("WSN_dist_19.jpg", plot.dist)

plot.hab <- plot_grid(p.eel, ch.eel, co.eel, align = "hv")
save_plot("WSN_hab_19.jpg", plot.hab)

plot.otts <- plot_grid(p.so, ch.so, co.so, align = "hv")
save_plot("WSN_otts_19.jpg", plot.otts)
```


## GAM models with long df
```{r}
# convert to long dataframe
# subset dataframe
dat1 <- dat[, c(1,6,8,23:29,34,35)]
dat_long <- melt(dat1, id = c("site", "avg_density", "year", "date", "juli_date", "dist_anad_km", "avg_biom_site_gm2"), variable.name = "SpCode", value.name = "abundance")

q1 <- ggplot(dat_long, aes(x = juli_date, y = abundance)) + 
  geom_point() +
  theme_classic() + 
  xlab("Julian Date") + ylab("Abundance")
q1 + stat_smooth(data = dat_long, method = "gam", formula = y ~ s(x), se = TRUE)


# make model
model <- gam(abundance ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km + SpCode, data = dat_long, family = nb(link = "log"))

g1 <- visreg(model, "juli_date", scale = "response", gg = TRUE, partial = TRUE) + 
  theme_classic() +
  xlab("Julian Date") + ylab("Salmon abundance")
g1 + facet_wrap(SpCode)

m1 <- gam(abundance ~ s(juli_date, k = 4) + avg_density + year + avg_biom_site_gm2 + dist_anad_km, data = dat, family = nb(link = "log"))



```

