---
title: "NOAA_Seine_ByHab-salmon"
author: "Lia Domke"
date: "10/23/2019"
output: html_document
---
# Libraries
```{r}
library(readxl)
library(tidyverse)
require(reshape2)
library(vegan)
```
# Input Data
```{r}
allsites <- read_xls("../ALL_DATA/Lia_fish/dist2_anad_allsites_102319.xls", sheet = 1)
fish <- read.csv("../ALL_DATA/noaa_seak_fish_atlas_CLEAN.csv")
```

# Data cleaning
Comment on format: EventID in fish and site_event SHOULD correspond. EventID is equal to *each* time the seine net went into the water regardless if it was at the same site at a different time. There may be duplicates of SiteID as it represents each *unique* site.
```{r}
# remove the non-noaa sites (i.e. those done in 2017 and 2019)
# besides those entries have funky incorrect info
noaa <- allsites[-c(616:661),]

# lets look at the data
names(fish)
names(noaa)
head(fish)

# want to combine the distance to anadromous stream with the beach seine data. 
noaa <- rename(noaa, EventID = site_event) # change site_event to EventID to be able to: 
fish$EventID <- as.numeric(fish$EventID)
noaa$EventID <- as.numeric(noaa$EventID)


seak_fish <- noaa %>%
  group_by(EventID) %>% # group by EventID first so that it will replicate dist for each row
  left_join(fish, noaa[,c(3,12)], by = "EventID") %>% # join the anadromous distance (in meters) to the       fish data frame by the EventID
  dplyr::select(SiteID, EventID, Date, Season, Mon, SeasonNoYear, Year, Gear, Temp, Salinity, NEAR_DIST, Region, Locale, Location.y, SubLocale.y, Nickname, Habitat, Lat1, Long1, SpCode, Sp_CommonName, Sp_ScientificName, Length, Unmeasured, taxon)

# double check to make sure we're only looking at SEAK and BSEINE gear
seak_fish <- seak_fish %>%
  filter(Region == "southeastern Alaska", Gear == "BSEINE") %>%
  rename(Dist_anad_m = NEAR_DIST, Latitude = Lat1, Longitude = Long1)

# Extract environmental only data 
env <- seak_fish %>%
  dplyr::select(SiteID, EventID, Date, Year, Temp, Salinity, Dist_anad_m, Habitat, Latitude, Longitude) %>%
  distinct()

# Calculate fish abundance
str(seak_fish)
seak_fish$abundance <- as.numeric(ifelse(is.na(seak_fish$Length), paste(seak_fish$Unmeasured), 1)) 

# summarise abundance by site, seine event, and species
sum_fish <- seak_fish %>%
  group_by(SiteID, EventID, Date, Mon, Season, Year, SpCode, Sp_CommonName, Sp_ScientificName) %>% 
  summarise(abundance = sum(abundance))


# long --> wide
# This includes ALL species (not just salmon). We'll leave this for now because it matches the
# environmental dataframe. But eventually we'll have to remove the non-salmon species. BUT we want
# retain the 0 where a seine was done but no salmon were caught. 
df_wide <- dcast(sum_fish, SiteID + EventID + Date + Mon + Season + Year ~ SpCode, value.var = "abundance", fill = 0)


# wide -- > long, convserves zeros and site/event ID information

df_long <- melt(df_wide, id = c("SiteID", "EventID", "Date", "Mon", "Season", "Year"), variable.name = "SpCode", value.name = "abundance" )

sal_long <- df_long %>%
  filter(SpCode == "SALCHUM" | SpCode == "SALCOHO"| 
      SpCode == "SALSOCK"| SpCode == "SALCHIN"
      | SpCode == "SALPINK")

# keeping all the zeros go back to wide! 
sal_wide <- dcast(sal_long, SiteID + EventID + Date + Mon + Season + Year ~ SpCode, value.var = "abundance", fill = 0) 

# REMOVE ALL SEINES WHERE THEY CAUGHT LESS THAN 10 SALMON
sal_wide <- sal_wide[which(rowSums(sal_wide[,7:11]) > 10),]
sal_long <- melt(sal_wide, id = c("SiteID", "EventID", "Date", "Mon", "Season", "Year"), variable.name = "SpCode", value.name = "abundance" )
```

# Data Exploration
We have two dataframes: sal_wide and sal_long have the seine information for salmon only abundance from all over southeast alaska (n = 615). env contains the environmental information: habitat type (categorical with 4 levels), temp, salinity, date, (and location)
```{r}
# species distribution
# mainly chum and pink, with a few coho
g <- ggplot(sal_long, aes(x = as.factor(EventID), y = abundance)) + geom_bar(stat = "identity")
g + facet_wrap(~SpCode)

# overall abundance, heavily zero-inflated! 
hist(sal_long$abundance)
# there are maybe over 500 occurences where salmon are present and over 2500 where they arent 
hist(as.numeric(sal_long$abundance>0))

# what if we transform our abundances
# log transformation
g <- ggplot(sal_long, aes(x = as.factor(EventID), y = log(abundance))) + geom_bar(stat = "identity")
g + facet_wrap(~SpCode)
# we can see the abundances now.... doesn't look normal

# 4th root transformation
g <- ggplot(sal_long, aes(x = as.factor(EventID), y = (abundance)^(0.25))) + geom_bar(stat = "identity")
g + facet_wrap(~SpCode)
# might be able to see more data if 4th root.... 

# add tests of normality for the data (not residuals). Are the data above normal?, Sorta.... not really. 
non <- qplot(sample = abundance, data = sal_long) + stat_qq_line()
non + facet_wrap(vars(SpCode))

p <- qplot(sample = log(abundance), data = sal_long) + stat_qq_line()
p + facet_wrap(vars(SpCode)) + theme(strip.text = element_text(size = 20))

frt <- qplot(sample = (abundance^0.25), data = sal_long) + stat_qq_line()
frt + facet_wrap(vars(SpCode))
```
Alright so the data doens't look *great* Lets try transformation and scaling to get comparable data

## Seine exploration - transformation / scaling 
```{r}
# what does boxcox recommend? Theory suggests 4th root
require(MASS)
Rmod <- lm(formula = abundance+1 ~ SpCode, data = sal_long)
summary(Rmod)
boxcox(Rmod) # doesn't really come up with anything. 

# 4th root transformation 
sal_long.tr <- sal_long %>%
  group_by(SiteID, EventID, Date, Mon, Season, Year, SpCode) %>%
  summarise(abundance.4 = abundance^(0.25))

sal_wide.tr <- dcast(sal_long.tr, SiteID + EventID + Date + Mon + Season + Year ~ SpCode, value.var = "abundance.4", fill = 0)

# lets considering scaling/standardizing the data. Theory suggests by SPECIES MAXIMUM. 
# mean by column
means <- colMeans(x = sal_wide.tr[,7:11], na.rm = TRUE)
species <- colnames(sal_wide.tr)[7:11]
df <- remove_rownames(data.frame(species, means))
EventID <- pull(sal_wide.tr[2])
SiteID <- pull(sal_wide.tr[1])
Date <- pull(sal_wide.tr[3])
Mon <- pull(sal_wide.tr[4])
Season <- pull(sal_wide.tr[5])
Year <- pull(sal_wide.tr[6])

# add in habitat by EventID
hab <- env[,c(2,8)]

# 0 - 1 scale of means
hist(df$means)
ggplot(df, aes(species, means)) + geom_col(position = "dodge")

# Scale to SPECIES MAXIMUM
y <- sal_wide.tr[,7:11]/max(sal_wide.tr[,7:11])
sal.sc <- cbind(SiteID, EventID, Date, Mon, Season, Year, y)
sal.sc <- left_join(sal.sc, hab, by = "EventID")

# After scaling & transformation, melt the dataframe back into long format to look at data distribution. 
sal_long_sc <- melt(sal.sc, id = c("SiteID", "EventID", "Date", "Mon", "Season", "Year", "Habitat"), variable.name = "SpCode", value.name = "abundance" )

# look at scaled and transformed distribution
g <- ggplot(sal_long_sc, aes(x = as.factor(EventID), y = abundance, fill=Habitat)) + geom_bar(stat = "identity")
g + facet_wrap(~SpCode)
# looks like salmon are occurring in multiple habitats... 
```

Cool beans looks like our sal data is already to go. We now have to look at the environmental data and make sure we're comparing the different env variables on the same scale... may require transformation and scaling

## Environmental data - transformation / scaling
```{r}
# change distance to anadromous stream to km 
env1 <- env %>%
  mutate(Dist_anad_km = Dist_anad_m/100) %>%
  dplyr::select(-Dist_anad_m)

env_long <- melt(env1, id = c ("SiteID", "EventID", "Date", "Year", "Latitude", "Longitude", "Habitat"), variable.name = "Environmental", value.name = "Value")

# Hard to compare environmental when they use different units. 
g <- ggplot(env_long,aes(x = reorder(as.factor(EventID), -Value), y = Value)) + geom_bar(stat = "identity")
g + facet_wrap(~Environmental)

# make sure habitat levels are correct:
levels(as.factor(env1$Habitat)) # mistake with sand-gravel
levels(env1$Habitat)[levels(env1$Habitat)=="Sand-Gravel"] <- "Sand-gravel"
levels(as.factor(env1$Habitat)) # only 5 levels now! 

# Scale data to mean 0 standard deviation 1 for only the cont. variables
env2 <- data.frame(scale(env1[,c(5,6,10)]))
env3 <- cbind(env2, env1$EventID)
colnames(env3)[colnames(env3) == "env1$EventID"] <- "EventID"
env.sc <- full_join(env1[,c(1:4,7:9)], env3, by = "EventID")
```

Lets look at what the species composition (of salmon) look like on a nmds plot
We have 3 dataframes to use for this:
Fish (both have been transformed and scaled) - sal.sc (wide) , sal_long_sc (long)
Environment (scaled) - env.sc

# Species biplot
```{r}
row.names(sal.sc) <- sal.sc$EventID
sal.sc1 <- sal.sc[,-c(1:6, 12)]

# now nmds and calculating dissimilarity index does not work if there are ENTIRE
# ROWS that have zeros. So we can ONLY compute where salmon ARE PRESENT. Duh. 
# So we have to remove all zero rows

sal.present <- sal.sc1[which(rowSums(sal.sc1) > 0),]
sal.EventID <- rownames(sal.present)

# Need to create bray-curtis dissimilarity index:
require(vegan)
dist.bray <- vegdist(sal.present, method = "bray")
round(dist.bray,2) # lower triangular matrix (vector of class 'dist')

# computer the NMDS iteratively using metaMDS
# based on the bray curtis distances found above: 
sp.nmds <- metaMDS(dist.bray, k = 2, autotransform = FALSE, trymax = 500)

# Examine output, which includes the two major ordination axes and Kruskal's stress value:
sp.nmds$stress

# How good did the nmds do? 
sp.sh <- Shepard(dist.bray, sp.nmds$points)
stressplot(sp.nmds)

# plot the data
ordiplot(sp.nmds, display="sites", type="t", cex=1)
plot(sp.nmds$point, col = as.factor(env.sc.sub$Habitat))


# redo the bray curtis: 
dist.bray2 <- vegdist(sal.sub.sc2, method = "bray")
round(dist.bray2, 2)
sp.nmds <- metaMDS(dist.bray2, k = 2, autotransform = FALSE, trymax = 100)
# replot the data
ordiplot(sp.nmds, display="sites", type="t", cex=1)
plot(sp.nmds$point, col = as.factor(env.sc.sub$Habitat))

# filter your environmental information by where salmon present eventID
env.sc.sub <- subset(env.sc, EventID %in% sal.EventID)

plot(sp.nmds$points, col=as.factor(env.sc.sub$Habitat), pch=16, cex=1.5, asp=1);
#ordispider(sp.nmds, env.sc.sub$Habitat, col=1:5, label=T);
ordihull(sp.nmds, env.sc.sub$Habitat, col=1:5, lty=2);legend("topright", legend=levels(as.factor(env.sc.sub$Habitat)), pch=16, col=1:5, cex=0.5)

```
#Environmental biplots
``` {r}
require(corrgram)
corrgram(env.sc.sub[,c(1,2,4,8:10)])

row.names(env.sc.sub) <- env.sc.sub$EventID
env.sc.sub1 <- env.sc.sub[,-c(1:7)]

# Create euclidea based dist
dist.env <- vegdist(env.sc.sub1, method = "euclidean", na.rm = T)
env.mds <- metaMDS(dist.env, k = 2, autotransform = F)
env.mds$stress

ordiplot(env.mds, display="sites", type="t", cex=1)
plot(env.mds$point, col = as.factor(env.sc.sub$Habitat)) # what does this plot show...?

# ordination with environmental variables 
ordisurf(sp.nmds, env.sc.sub$Temp, bubble=T, cex=5, 
         main = "Ordination with Temperature", 
         xlab = "nMDS1", ylab = "nMDS2")

ordisurf(sp.nmds, env.sc.sub$Salinity, bubble=T, cex=5, 
         main = "Ordination with Salinity", 
         xlab = "nMDS1", ylab = "nMDS2")

ordisurf(sp.nmds, env.sc.sub$Dist_anad_km, bubble=T, cex=5, 
         main = "Ordination with Distance from anadromous stream (km)", 
         xlab = "nMDS1", ylab = "nMDS2")

ordisurf(sp.nmds, env.sc.sub$Habitat, bubble=T, cex=5, 
         main = "Ordination with habitat", 
         xlab = "nMDS1", ylab = "nMDS2")
```