---
title: "Data cleaning and preparation"
author: "Wendel Raymond"
date: "November 29, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r Libraries, echo = FALSE, include=FALSE}
library(dplyr); library(tidyr); library(ggplot2)
theme_set(theme_classic())
```


# Data cleaning and preparation
Below are the steps and rational for cleaning and prepping raw data so that it is ready for analysis. 
Data are from the 2017 field season sampling eelgrass sites on Prince of Wales Island Alaska.

## Raw Data
Raw data include data collected in the field on the eelgrass transect (eg.tran), data collected from processing eelgrass samples collected in the field (eg. bio). This can be thought of as the eelgrass biometrics. And finally site level data such as date, site name, temperature, salinity, etc (eg.site).

```{r import data, cache = TRUE, echo = FALSE, include = FALSE}
# seagrass biometrics
eg.bio <- read.csv("RAW_seagrass_biometrics_2017.csv", stringsAsFactors = FALSE, header = TRUE)
colnames(eg.bio)[1] <- "site" # for some reason the sie column has a weird name

# seagrass transect
eg.tran <- read.csv("https://raw.githubusercontent.com/APECS-ak/seagrass_2017/master/RAW_seagrass_transect_2017.csv", stringsAsFactors = FALSE, header = TRUE)

# seagrass site
eg.site <- read.csv("https://raw.githubusercontent.com/APECS-ak/seagrass_2017/master/RAW_seagrass_site_2017.csv", stringsAsFactors = FALSE, header = TRUE)
```


Here are our data.
Eeglrass biometrics
```{r str eg.bio, echo = FASLE}
str(eg.bio)
```



Eelgrass Transect
```{r str eg.tran, echo=FALSE}
# datachunk creator: WR
str(eg.tran)
```


Eelgrass Site
```{r str eg.site, echo=FALSE}
# datachunk creator: WR
str(eg.site)
```


## Cleaning missing values
A few times when processing samples either a grazer was lost or the grazer was so small that it did not register a mass on the scale. In these instances we want to still account for the animal but we need to fill in a value for the foil masses. 

If a grazer column has a count but has NA for foil weights then we will fill in dummy values for the foil masses so that the grazer mass is equal to 0.0001 grams, the smalles amount measurable by the scale. This does not have to be the way we do this. This is just one way.
```{r filling missing values}
### this still does not work but I am working on it - WR ###

for(s in c("2017_H_03", "2017_H_04", "2017_L_02", "2017_L_03", "2017_L07"))
miss.dat <- eg.bio %>% 
  filter(plant == 1) %>% # row that holds all grazer data
  filter(site == "2017_H_03" & quadrat == 5)

miss.dat$gastropod_foil <- 0.0001
miss.dat$gastropod_foil_dw <- 0.0002

eg.bio <- eg.bio %>% 
  anti_join(miss.dat, by = c("site", "plant", "quadrat")) %>% 
  bind_rows(miss.dat) %>% 
  arrange(site, quadrat, plant)

```

# Data Exploration, Initial Prep, and Summaries
### Originally created 10.19.2017; Wendel Raymond

Checking the data
```{r checking data}
# datachunk creator: WR
### Eelgrass Transect ###
str(eg.tran)
levels(eg.tran$site)
levels(eg.tran$primary_obeserver)
levels(eg.tran$secondary_observer)
range(eg.tran$quadrat)
range(eg.tran$macroalgae_cover_0.25msq)
range(eg.tran$eelgrass_shoots_0.25msq)
hist(eg.tran$eelgrass_shoots_0.25msq)
hist(eg.tran$macroalgae_cover_0.25msq)
hist(eg.tran$diatom_cover_0.25msq)
```


Changing numerics to factors
```{r number to factors}
# datachunk creator: WR
## Transect ##
eg.tran$quadrat <- as.factor(eg.tran$quadrat)
```

Changing a few column names so its not confusing ###
```{r changing column names}
# datachunk creator: WR


## Start and End times ##
# Site
colnames(eg.site)[6] <- "site_start_time"
colnames(eg.site)[7] <- "site_end_time"

# Transect
colnames(eg.tran)[6] <- "transect_start_time"
colnames(eg.tran)[7] <- "transect_end_time"

```

Cleaning up dates

# MOST OF THE CODE BELOW GOES BEYOND TYPICAL CLEANING OF DATASET! 
```{r Calculations}

#####----- Calculations -----#####
## Fill absent grazers with 0s so that cacluations below will work ##
eg.bio[,89:94][is.na(eg.bio[,89:94])] <- 0

## Crustacean Grazers Mass ##
eg.bio$crust_mass <- (eg.bio$iso_mass + eg.bio$gamm_mass +  eg.bio$caprel_mass + eg.bio$crab_mass)

## Gastropod Grazers Mass ##
eg.bio$gastro_mass <- (eg.bio$limp_mass + eg.bio$gast_mass)

## Total Grazer Mass ##
eg.bio$graz_massT <- rowSums(eg.bio[, 89:94], na.rm = TRUE)

#####----- Quadrat level Summaries -----#####
## standard error of the mean fucntion to use later ##
st.er <- function(x, na.rm = TRUE) {
  stopifnot(is.numeric(x))
  return(sd(x, na.rm = na.rm)/sqrt(length(x)))
}

## Convert Transect data to per meter ##
eg.tran$eelgrass_shoots_msq <- (4 * eg.tran$eelgrass_shoots_0.25msq)
eg.tran$flowering_shoots_msq <- (4 * eg.tran$flowering_shoots_0.25msq)
eg.tran$macroalgae_cover_msq <- (1 * eg.tran$macroalgae_cover_0.25msq)
eg.tran$diatom_cover_msq <- (1 * eg.tran$diatom_cover_0.25msq)

## Biometrics data summarized by site and quadrat - shoots and rhizomes ##
quad.bio <- data.frame(
  eg.bio %>% 
    group_by(site, quadrat) %>% 
    summarise(s_shoot_area = mean(leaf_areaT, na.rm = TRUE),
              s_epi_mass = mean(epi_mass, na.rm = TRUE),
              s_shoot_mass = mean(shoot_mass, na.rm = TRUE),
              s_rhi_mass = mean(rhi_mass, na.rm = TRUE),
              s_node1 = mean(node1, na.rm = TRUE),
              s_node2 = mean(node2, na.rm = TRUE),
              s_node3 = mean(node3, na.rm = TRUE),
              s_node4 = mean(node4, na.rm = TRUE),
              s_node5 = mean(node5, na.rm = TRUE),
              s_exshoot_mass = mean(exshoot_mass, na.rm = TRUE),
              s_exepi_mass = mean(exepi_mass, na.rm = TRUE))
)

# Extract Grazer biomasses
quad.graz <- data.frame(eg.bio[eg.bio$plant == 1,]) # extract just plant 1 which has all the grazer data
quad.graz <- quad.graz[order(quad.graz[,1], quad.graz[,4]),] # order so that it matches everything else
quad.graz <- data.frame(quad.graz[,c(1, 4, 89:97)]) # reduce to get grazer data only
quad.graz[is.na(quad.graz)] <- 0 # turn NAs to 0s becasue if we sampled everything so if it was not there its a 0

## Combined Transect and Biometrics data to give site summaries ##
site.quad <- merge(eg.site[,c(1, 2)], eg.tran, by = "site")
site.quad <- merge(site.quad, quad.bio, by = c("site", "quadrat"))
site.quad <- merge(site.quad, quad.graz, by = c("site", "quadrat"))

### Quadrat level caclulations ###
## Aboveground Biomass ##
site.quad$ag_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_shoot_mass)

## Below Ground Biomass ##
site.quad$bg_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_rhi_mass)

## Epiphytes per eeglrass area ##
site.quad$epimass_shootarea <- (site.quad$s_epi_mass / site.quad$s_shoot_area)

## Epiphytes per eelgrass mass ##
site.quad$epimass_shootmass <- (site.quad$s_epi_mass / site.quad$s_shoot_mass)

## Grazer Mass per Quadrat ##
# this is just equal to graz_massT

## Grazer mass per eelgrass mass ##
site.quad$grazmass_shootmass <- (site.quad$graz_massT / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Crustacean mass per eelgrass mass ##
site.quad$crustmass_shootmass <- (site.quad$crust_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Gastropod mass per eelgrass mass ##
site.quad$gastromass_shootmass <- (site.quad$gastro_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass)) 

#####----- Master Compile and Calculations -----#####
### Site Level Data ###
tran.dat <- data.frame(rbind(eg.tran[1, c(1, 4:8)], eg.tran[9, c(1, 4:8)], eg.tran[17, c(1, 4:8)], eg.tran[25, c(1, 4:8)], eg.tran[33, c(1, 4:8)], eg.tran[41, c(1, 4:8)], 
                             eg.tran[49, c(1, 4:8)],eg.tran[57, c(1, 4:8)], eg.tran[65, c(1, 4:8)], eg.tran[73, c(1, 4:8)], eg.tran[81, c(1, 4:8)], eg.tran[89, c(1, 4:8)], 
                             eg.tran[97, c(1, 4:8)], eg.tran[105, c(1, 4:8)], eg.tran[113, c(1, 4:8)], eg.tran[121, c(1, 4:8)], eg.tran[129, c(1, 4:8)], eg.tran[137, c(1, 4:8)], 
                             eg.tran[145, c(1, 4:8)], eg.tran[153, c(1, 4:8)], eg.tran[161, c(1, 4:8)]))

### Master ###
dat <- data.frame(cbind(eg.site[, c(1:3, 32, 4:9)], tran.dat[, 2:5], so.index[, 6:13], eg.site[, 14:26]))

## Transect data summarized by site ##
site.tran <- data.frame(
  eg.tran %>% 
    group_by(site) %>% 
    summarise(shoot_dens = (mean(eelgrass_shoots_0.25msq * 4)),
              shoot_dens_se = (st.er(eelgrass_shoots_0.25msq * 4)),
              macro_dens = (mean(macroalgae_cover_0.25msq * 1)),
              macro_dens_se = (st.er(macroalgae_cover_0.25msq * 1)),
              diatom_dens = (mean(diatom_cover_0.25msq * 1)),
              diatom_dens_se = (st.er(diatom_cover_0.25msq * 1)),
              flower_dens = (mean(flowering_shoots_0.25msq * 4)),
              flower_dens_se = (st.er(flowering_shoots_0.25msq * 4)))
)

## Biometrics data summarized by site ##
site.bio <- data.frame(
  site.quad %>% 
    group_by(site) %>% 
    summarise(shoot_area = (mean(s_shoot_area, na.rm = TRUE)),
              shoot_area_se = (st.er(s_shoot_area)),
              epi_mass = (mean(s_epi_mass, na.rm = TRUE)),
              epi_mass_se = (st.er(s_epi_mass)),
              shoot_mass = (mean(s_shoot_mass, na.rm = TRUE)),
              shoot_mass_se = (st.er(s_shoot_mass)),
              rhi_mass = (mean(s_rhi_mass, na.rm = TRUE)),
              rhi_mass_se = (st.er(s_rhi_mass)),
              node1 = (mean(s_node1, na.rm = TRUE)),
              node1_se = (st.er(s_node1)),
              node2 = (mean(s_node2, na.rm = TRUE)),
              node2_se = (st.er(s_node2)),
              node3 = (mean(s_node3, na.rm = TRUE)),
              node3_se = (st.er(s_node3)),
              node4 = (mean(s_node4, na.rm = TRUE)),
              node4_se = (st.er(s_node4)),
              node5 = (mean(s_node5, na.rm = TRUE)),
              node5_se = (st.er(s_node5)),
              exshoot_mass = (mean(s_exshoot_mass, na.rm = TRUE)),
              exshoot_mass_se = (st.er(s_exshoot_mass)),
              exepi_mass = (mean(s_exepi_mass, na.rm = TRUE)),
              exepi_mass_se = (st.er(s_exepi_mass)),
              abvgnd_mass = (mean(ag_mass, na.rm = TRUE)),
              abvgnd_mass_se = (st.er(ag_mass)),
              blwgnd_mass = (mean(bg_mass, na.rm = TRUE)),
              blwgnd_mass_se = (st.er(bg_mass)),
              epiphmass_shootarea = (mean(epimass_shootarea, na.rm = TRUE)),
              epiphmass_shootarea_se = (st.er(epimass_shootarea)),
              epiphmass_shootmass = (mean(epimass_shootmass, na.rm = TRUE)),
              epiphmass_shootmass_se = (st.er(epimass_shootmass)),
              grazer_mass = (mean(graz_massT, na.rm = TRUE)),
              grazer_mass_se = (st.er(graz_massT)),
              crus_mass = (mean(crust_mass, na.rm = TRUE)),
              crus_mass_se = (st.er(crust_mass)),
              gast_mass = (mean(gastro_mass, na.rm = TRUE)),
              gast_mass_se = (st.er(gastro_mass)),
              grazermass_shootmass = (mean(grazmass_shootmass, na.rm = TRUE)),
              grazermass_shootmass_se = (st.er(grazmass_shootmass)),
              crusmass_shootmass = (mean(crustmass_shootmass, na.rm = TRUE)),
              crusmass_shootmass_se = (st.er(crustmass_shootmass)),
              gastmass_shootmass = (mean(gastromass_shootmass, na.rm = TRUE)),
              gastmass_shootmass_se = (st.er(gastromass_shootmass)))
)

### Merge Transect and Biometrics data to Master dat ###
## Transect ##
dat <- merge(dat, site.tran, by = "site")

## Biometrics ##
dat <- merge(dat, site.bio, by = "site")

### Clean up ###
dat$specific_conductivity_transect <- as.numeric(dat$specific_conductivity_transect)

#####----- Export -----#####
write.csv(dat, "Eelgrass_and_Grazer_Data_2017.csv", row.names = FALSE)
```

