---
title: '--- in_progress_file(Eelgrass_data_exploration)'
author: "Wendel Raymond"
date: "December 6, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Exploration of eelgrass data
This script explores the data collected in summer 2017 in order to get a sense of what we collected and where to take analyses from here.

```{r libraries, echo = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(ggplot2)
library(cowplot)

theme_set(theme_classic())
```

```{r standard error function, echo = FALSE}
st.er <- function(x, na.rm = TRUE) {
  stopifnot(is.numeric(x))
  return(sd(x, na.rm = na.rm)/sqrt(length(x)))
}
```

## Data
There are a few potential data set to load for these analyses. Currently loaded are eelgrass and grazer data (add additions here and in code :))
```{r loading data}
eg.dat <- read.csv("../ALL_DATA/eelgrass_and_grazer_2017_derived.csv", stringsAsFactors = FALSE, header = TRUE)

crab.dat <- read.csv("../ALL_DATA/crab_simple_site_2017_derived.csv", stringsAsFactors = FALSE, header = TRUE)

# clean up some column names to avoid confusion later on
colnames(eg.dat)[3] <- "date_eelgrass_tran"
colnames(eg.dat)[4] <- "date_julian_eelgrass_tran"
```

## Exploratory analyses
These analyses focus on looking for patterns and relationships in the data. The primary hypothesis that we will eventaually be testing is whether or not sea otter mediate a trophic cascade in the Southeast Alaska eelgrass commnities.

### Eelgrass data
Plots and summary stats.

#### Effect of sea otter index
Primary producers
```{r Primary producers sea otter index}
## shoot density ##
SHDN.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = shoot_dens), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = shoot_dens - shoot_dens_se, ymax = shoot_dens + shoot_dens_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Shoot density +/- se' ~(m^-2))) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Aboveground biomass ##
ABGB.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = abvgnd_mass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = abvgnd_mass - abvgnd_mass_se, ymax = abvgnd_mass + abvgnd_mass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Above ground mass +/- se' ~(g/m^-2))) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Belowground biomass ##
BLGB.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = blwgnd_mass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = blwgnd_mass - blwgnd_mass_se, ymax = blwgnd_mass + blwgnd_mass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Below ground mass +/- se' ~(g/m^-2))) +
  lims(y = c(0, 80)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Second rhizome node ##
RHI2.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = node2), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = node2 - node2_se, ymax = node2 + node2_se), size = 1) +
  labs(x = "Sea otter Index", y = "Rhizome node #2 (cm)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Epiphyte mass ##
EPIM.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = epi_mass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = epi_mass - epi_mass_se, ymax = epi_mass + epi_mass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Epiphyte mass  +/- se (g)')) +
  lims(y = c(0, 0.04)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Epiphyte load ##
EPIL.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = epiphmass_shootmass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = epiphmass_shootmass - epiphmass_shootmass_se, ymax = epiphmass_shootmass + epiphmass_shootmass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Epiphyte load +/- se' ~(g/g^-2))) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Macroalgae ##
MAPC.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = macro_dens), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = macro_dens - macro_dens_se, ymax = macro_dens + macro_dens_se), size = 1) +
  labs(x = "Sea otter index", y = "Macroalgae cover (%)") +
  lims(y = c(0, 75)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2))

## Diotoms ##
DTPC.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = diatom_dens), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = diatom_dens - diatom_dens_se, ymax = diatom_dens + diatom_dens_se), size = 1) +
  labs(x = "Sea otter index", y = "Diatom cover (%)") +
  lims(y = c(0, 100)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```

Nutrients - day of sampling
```{r nutrients day of sampling}
## Day of nutrients ##
NO.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NOX_site), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NOX_site - NOX_site_se, ymax = NOX_site + NOX_site_se), size = 1) +
  labs(x = "Sea otter index", y = "Nitrate +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NH4.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NH4_site), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NH4_site - NH4_site_se, ymax = NH4_site + NH4_site_se), size = 1) +
  labs(x = "Sea otter index", y = "Ammonium +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

PO4.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = PO4_site), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = PO4_site - PO4_site_se, ymax = PO4_site + PO4_site_se), size = 1) +
  labs(x = "Sea otter index", y = "Phosphate +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

TN.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = Ntotal_site), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = Ntotal_site - Ntotal_site_se, ymax = Ntotal_site + Ntotal_site_se), size = 1) +
  labs(x = "Sea otter index", y = "Total N +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NP.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NP_site), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NP_site - NP_site_se, ymax = NP_site + NP_site_se), size = 1) +
  labs(x = "Sea otter index", y = "N:P +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

```

Nutrients - nutrient day
```{r nutrients nutrient day}
NO1m.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NOX_1m_ND), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NOX_1m_ND - NOX_1m_ND_se, ymax = NOX_1m_ND + NOX_1m_ND_se), size = 1) +
  labs(x = "Sea otter index", y = "Nitrate +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NH41m.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NH4_1m_ND), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NH4_1m_ND - NH4_1m_ND_se, ymax = NH4_1m_ND + NH4_1m_ND_se), size = 1) +
  labs(x = "Sea otter index", y = "Ammonium +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

PO41m.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = PO4_1m_ND), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = PO4_1m_ND - PO4_1m_ND_se, ymax = PO4_1m_ND + PO4_1m_ND_se), size = 1) +
  labs(x = "Sea otter index", y = "Phosphate +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

TN1m.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = Ntotal_1m_ND), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = Ntotal_1m_ND - Ntotal_1m_ND_se, ymax = Ntotal_1m_ND + Ntotal_1m_ND_se), size = 1) +
  labs(x = "Sea otter index", y = "Total N +/- se (umol/L)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NP1m.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = NP_1m_ND), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = NP_1m_ND - NP_1m_ND_se, ymax = NP_1m_ND + NP_1m_ND_se), size = 1) +
  labs(x = "Sea otter index", y = "N:P +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```

Grazers
```{r grazers sea otter index}
## Grazer mass ##
GRZM.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = grazer_mass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = grazer_mass - grazer_mass_se, ymax = grazer_mass + grazer_mass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Grazer mass +/- se (g)')) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Grazer load ##
GRZL.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = grazermass_shootmass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = grazermass_shootmass - grazermass_shootmass_se, ymax = grazermass_shootmass + grazermass_shootmass_se), size = 1) +
  labs(x = "Sea otter Index", y = bquote('Grazer load +/- se' ~(g/g^-2))) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Crustacean load ##
CRSL.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = crusmass_shootmass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = crusmass_shootmass - crusmass_shootmass_se, ymax = crusmass_shootmass + crusmass_shootmass_se), size = 1) +
  labs(x = "Sea otter index", y = bquote('Crustacean load +/- se' ~(g/g^-2))) +
  lims(y = c(0, 0.15)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2))

## Gastropod load ##
GASL.SOII <- ggplot(eg.dat) +
  geom_point(aes(x = PCA2, y = gastmass_shootmass), size = 4) +
  geom_errorbar(aes(x = PCA2, ymin = gastmass_shootmass - gastmass_shootmass_se, ymax = gastmass_shootmass + gastmass_shootmass_se), size = 1) +
  labs(x = "Sea otter index", y = bquote('Gastropod load +/- se' ~(g/g^-2))) +
  lims(y = c(0, 0.10)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```

#### Effect of time

Primary producers
```{r primary producers jday}
## Shoot density ##
SHDN.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = shoot_dens - shoot_dens_se, ymax = shoot_dens + shoot_dens_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = shoot_dens, color = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Shoot density +/- se' ~(m^-2))) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Aboveground biomass ##
ABGB.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = abvgnd_mass - abvgnd_mass_se, ymax = abvgnd_mass + abvgnd_mass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = abvgnd_mass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Aboveground mass +/- se' ~(g/m^-2))) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Belowground biomass ##
BLGB.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = blwgnd_mass - blwgnd_mass_se, ymax = blwgnd_mass + blwgnd_mass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = blwgnd_mass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Belowground mass +/- se' ~(g/m^-2))) +
  lims(y = c(0, 80)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Second rhizome node ##
RHI2.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = node2 - node2_se, ymax = node2 + node2_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = node2, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = "Rhizome node #2 (cm)") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Epiphyte mass ##
EPIM.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = epi_mass - epi_mass_se, ymax = epi_mass + epi_mass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = epi_mass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Epiphyte mass  +/- se (g)')) +
  lims(y = c(0, 0.04)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Epiphyte load ##
EPIL.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = epiphmass_shootmass - epiphmass_shootmass_se, ymax = epiphmass_shootmass + epiphmass_shootmass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = epiphmass_shootmass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Epiphyte mass / Shoot mass +/- se' ~(g/g^-2))) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Macroalgae ##
MAPC.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = macro_dens - macro_dens_se, ymax = macro_dens + macro_dens_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = macro_dens, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = "Macroalgae cover (%)") +
  lims(y = c(0,75)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Diatoms ##
DTPC.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = diatom_dens - diatom_dens_se, ymax = diatom_dens + diatom_dens_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = diatom_dens, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = "Diatom cover (%)") +
  lims(y = c(0,125)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```
 
Nutrients - day of sampling
```{r}
NO.JDAY <- ggplot(eg.dat) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = NOX_site), size = 4) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = NOX_site - NOX_site_se, ymax = NOX_site + NOX_site_se), size = 1) +
  labs(x = "Date", y = "Nitrate +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NH4.JDAY <- ggplot(eg.dat) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = NH4_site), size = 4) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = NH4_site - NH4_site_se, ymax = NH4_site + NH4_site_se), size = 1) +
  labs(x = "Date", y = "Ammonium +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

PO4.JDAY <- ggplot(eg.dat) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = PO4_site), size = 4) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = PO4_site - PO4_site_se, ymax = PO4_site + PO4_site_se), size = 1) +
  labs(x = "Date", y = "Phosphate +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

TN.JDAY <- ggplot(eg.dat) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = Ntotal_site), size = 4) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = Ntotal_site - Ntotal_site_se, ymax = Ntotal_site + Ntotal_site_se), size = 1) +
  labs(x = "Date", y = "Total N +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

NP.JDAY <- ggplot(eg.dat) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = NP_site), size = 4) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = NP_site - NP_site_se, ymax = NP_site + NP_site_se), size = 1) +
  labs(x = "Date", y = "N:P +/- se") +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```

Grazers
```{r}
## Grazer mass ##
GRZM.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = grazer_mass - grazer_mass_se, ymax = grazer_mass + grazer_mass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = grazer_mass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Grazer mass +/- se (g)')) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Grazer load ##
GRZL.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = grazermass_shootmass - grazermass_shootmass_se, ymax = grazermass_shootmass + grazermass_shootmass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = grazermass_shootmass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Grazer load +/- se' ~(g/g))) +
  lims(y = c(0, 0.25)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Crustacean load ##
CRSL.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = crusmass_shootmass - crusmass_shootmass_se, ymax = crusmass_shootmass + crusmass_shootmass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = crusmass_shootmass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Crustacean load +/- se' ~(g/g))) +
  lims(y = c(0, 0.15)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")

## Gastropod load ##
GASL.JDAY <- ggplot(eg.dat) +
  geom_errorbar(aes(x = date_julian_eelgrass_tran, ymin = gastmass_shootmass - gastmass_shootmass_se, ymax = gastmass_shootmass + gastmass_shootmass_se), size = 1) +
  geom_point(aes(x = date_julian_eelgrass_tran, y = gastmass_shootmass, col = PCA2), size = 4) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(x = "Date", y = bquote('Gastropod load +/- se' ~(g/g))) +
  lims(y = c(0, 0.10)) +
  theme(text = element_text(size = 12), axis.ticks = element_line(size = 2), legend.position = "none")
```

## Exporting plots
Lets save all these exploratory plots for other to easily access
```{r exporting plots}
ggsave(plot = ABGB.JDAY, "Figures/aboveground_mass_jday.png", dpi = 500)
ggsave(plot = ABGB.SOII, "Figures/aboveground_mass_seaotter.png", dpi = 500)
ggsave(plot = BLGB.JDAY, "Figures/belowground_mass_jday.png", dpi = 500)
ggsave(plot = BLGB.SOII, "Figures/belowground_mass_seaotter.png", dpi = 500)
ggsave(plot = CRSL.JDAY, "Figures/crustacean_mass_jday.png", dpi = 500)
ggsave(plot = CRSL.SOII, "Figures/crustacean_mass_seaotter.png", dpi = 500)
ggsave(plot = DTPC.JDAY, "Figures/diatom_pc_jday.png", dpi = 500)
ggsave(plot = DTPC.SOII, "Figures/diatom_pc_SOII.png", dpi = 500)
ggsave(plot = EPIL.JDAY, "Figures/epiphyte_load_jday.png", dpi = 500)
ggsave(plot = EPIL.SOII, "Figures/epiphyte_load_seaotter.png", dpi = 500)
ggsave(plot = EPIM.JDAY, "Figures/epiphyte_mass_jday.png", dpi = 500)
ggsave(plot = EPIM.SOII, "Figures/epiphyte_mass_seaotter.png", dpi = 500)
ggsave(plot = GASL.JDAY, "Figures/gastropod_load_jday.png", dpi = 500)
ggsave(plot = GASL.SOII, "Figures/gastropod_load_seaotter.png", dpi = 500)
ggsave(plot = GRZL.JDAY, "Figures/grazer_load_jday.png", dpi = 500)
ggsave(plot = GRZL.SOII, "Figures/grazer_load_seaotter.png", dpi = 500)
ggsave(plot = GRZM.JDAY, "Figures/grazer_mass_jday.png", dpi = 500)
ggsave(plot = GRZM.SOII, "Figures/grazer_mass_seaotter.png", dpi = 500)
ggsave(plot = MAPC.JDAY, "Figures/macroalgae_pc_jday.png", dpi = 500)
ggsave(plot = MAPC.SOII, "Figures/macroalgae_pc_seaotter.png", dpi = 500)
ggsave(plot = NH4.JDAY, "Figures/ammonium_jday.png", dpi = 500)
ggsave(plot = NH4.SOII, "Figures/ammonium_seaotter.png", dpi = 500)
ggsave(plot = NO.JDAY, "Figures/nitrate_jday.png", dpi = 500)
ggsave(plot = NO.SOII, "Figures/nitrate_seaotter.png", dpi = 500)
ggsave(plot = NO1m.SOII, "Figures/nitrate_nutday_1m_seaotter.png", dpi = 500)
ggsave(plot = NP.JDAY, "Figures/ntop_jday.png", dpi = 500)
ggsave(plot = NP.SOII, "Figures/ntop_SOII.png", dpi = 500)
ggsave(plot = NP1m.SOII, "Figures/totalN_nutday_1m_SOII.png", dpi = 500)
ggsave(plot = PO4.JDAY, "Figures/phosphate_jday.png", dpi = 500)
ggsave(plot = PO4.SOII, "Figures/phosphate_seaotter.png", dpi = 500)
ggsave(plot = PO41m.SOII, "Figures/phosphate_nutday_1m_seaotter.png", dpi = 500)
ggsave(plot = RHI2.JDAY, "Figures/rhizome_node2_jday.png", dpi = 500)
ggsave(plot = RHI2.SOII, "Figures/rhizome_node2_seaotter.png", dpi = 500)
ggsave(plot = SHDN.JDAY, "Figures/shoot_density_jday.png", dpi = 500)
ggsave(plot = SHDN.SOII, "Figures/shoot_density_seaotter.png", dpi = 500)
ggsave(plot = TN.JDAY, "Figures/totaln_jday.png", dpi = 500)
ggsave(plot = TN.SOII, "Figures/totaln_jday.png", dpi = 500)
ggsave(plot = TN1m.SOII, "Figures/totaln_nutday_1m_jday.png", dpi = 500)
```

