---
title: '---in_progress_file(Crab_data_calculations).Rmd'
author: "Wendel Raymond"
date: "December 6, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r libraries, echo = FALSE}
library(dplyr)
library(tidyr)
library(vegan)
library(ggplot2)

theme_set(theme_classic())
```

```{r functions, echo = FALSE}
st.er <- function(x, na.rm = TRUE) {
  stopifnot(is.numeric(x))
  return(sd(x, na.rm = na.rm)/sqrt(length(x)))
}
```

# Crab pot calculations
From the raw data this script will export a file summarized by site ready for analysis. The goal will be to summaries this data at the site level. Summaries will occur in a few different ways to prep the data for different types on analysis. There are X files generated here. Simple summaries...(fill in more here as appropriate)

## Data import
All we need is the crab data and the crab length weight conversions. This can be merged with other data that already has been summarized in other scripts. The merging can either happen here or in other scripts depending on the purpose.

```{r data import}
crab <- read.csv("../ALL_DATA/seagrass_crab_pot_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

crabLW <- read.csv("../ALL_DATA/crab_length_weight_conversion_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

Checking the data
```{r checking data}
str(crab)
str(crabLW)
```

## Cleaning up dat columns
Since setting and retrieving crab pots did not happen at the same time as the eelgrass transect there should be a separate date for the crab pots

```{r converting to julian day}
crab$date_set <- as.Date(crab$date_set, format = "%m/%d/%Y")
crab$date_set_juliean <- format(crab$date_set, "%j")
crab$date_pulled <- as.Date(crab$date_pulled , format = "%m/%d/%Y")
crab$date_pulled_julian <- format(crab$date_pulled, "%j")
```

## Calculations
The first thing to do is to add the length - weight conversions to the staring data frame so that we can convert carapace widths the biomass. This will be done by adding the species specific coefficients to the data frame. Note the this conversion is to what is considered sea otter edible biomass. Also note that fish are recorded in this data that might be useful, but from this point on we are going to remove all fishes

```{r crabs only}
crab <- crab %>% 
  filter(taxon == "Decapoda")
```

Now we will add length weight conversion coefficients
```{r adding length to weight conversion}
crab <- merge(crab, crabLW, by = "sp_code")
crab <- crab[,c(1:21, 23:29)] # remove duplicated 
colnames(crab)[14] <- "taxon"
```

Calculate mass
```{r calcualte mass}
crab$mass_g <- (crab$a_mean * (crab$carapace_width_mm)^crab$b_mean)
range(crab$mass_g, na.rm = TRUE)

# Some example plots
ggplot(crab, aes(mass_g)) +
  geom_histogram()

ggplot(crab, aes(mass_g)) +
  geom_histogram() +
  facet_wrap(~site)

ggplot(crab, aes(mass_g)) +
  geom_histogram() +
  facet_wrap(~sp_code)
```

### Summary calculations
Generally we want to summaries by site.

#### Mass, counts, species
Summaries by site and species
```{r crab site and species}
crab.site.sp <- crab %>% 
  filter(taxon == "Decapoda") %>% # make sure we only have crabs
  group_by(site, sp_code) %>% 
  summarise(total_crab_sp = n(),
            width = mean(carapace_width_mm), 
            width_se = st.er(carapace_width_mm),
            mass = mean(mass_g),
            mass_se = st.er(mass_g))
```

Summaries by site only
```{r crab site summary}
crab.site <- crab %>% 
  filter(taxon == "Decapoda") %>% # make sure we only have crabs
  group_by(site) %>% 
  summarise(total_crab = n(),
            crab_width = mean(carapace_width_mm), 
            crab_width_se = st.er(carapace_width_mm),
            crab_mass = mean(mass_g),
            crab_mass_se = st.er(mass_g))
```

#### Diversity calculations
To calculate diversity we have to do a bit of data manipulation in order for the functions to run. For each site we will calculate Shannon-wiener and Simpson diversity.
```{r diversity calculations}
crab.site.sp.wide <- spread(crab.site.sp[, 1:3], key = sp_code, value = total_crab_sp)
crab.site.sp.wide[is.na(crab.site.sp.wide)] <- 0

crab.site.sp.wide$shan_divese <- diversity(crab.site.sp.wide[2:7], index = "shannon")
crab.site.sp.wide$simp_divese <- diversity(crab.site.sp.wide[2:7], index = "simpson")
```

Now we can append it to the rest of the data
```{r append diversity to site}
crab.site <- merge(crab.site, crab.site.sp.wide[, c(1, 8:9)], by = "site")
```

## Export simple summaries
Exporting simple site level summaries of total crabs, width, mass, and diversity. This file can then be loaded in elsewhere for analysis.
```{r export simple summaries}
write.csv(crab.site, "../ALL_DATA/crab_simple_site_2017_derived.csv", row.names = FALSE)
```

