---
title: "Cleaning_raw_biometrics"
author: "Tiff Stephens"
date: "11/30/2017"
output: html_document
---


```{r Libraries, echo = FALSE, include=FALSE}
library(dplyr); library(tidyr); library(ggplot2)
theme_set(theme_classic())
```

Import data
```{r}
# datachunk: TAS

sg.bio <- read.csv("https://raw.githubusercontent.com/APECS-ak/seagrass_2017/master/RAW_seagrass_biometrics_2017.csv", stringsAsFactors = FALSE, header = TRUE)
```

# Checking the data
```{r}
# datachunk: WR

str(sg.bio)
range(sg.bio$rhi_length, na.rm = TRUE)
range(sg.bio$node1, na.rm = TRUE)
hist(sg.bio$node2)
hist(sg.bio$leaf_width1)
```

Change numerics to factors
# Is this necessary? 
```{r}
# datachunk: WR

#sg.bio$quadrat <- as.factor(sg.bio$quadrat)
#sg.bio$plant <- as.factor(sg.bio$plant)
```



# Cleaning Data for Analysis

Calculate dry weights of all flora and fauna; remove pad + foil data uneccessary for analysis
```{r}
# datachunk: TAS


# piped calculations for all
sg.bio = sg.bio %>% 
  mutate(epiphyte_mass_dw = pad_epiphyte_mass_g - pad_mass_g) %>%
  mutate(rhi_mass_dw = rhi_foil_dw_g - rhi_foil) %>%
  mutate(shoot_mass_dw = shoot_foil_dw - shoot_foil) %>%
  mutate(xs_shoot_mass_dw = xs_shoot_foil_dw - xs_shoot_foil) %>%
  mutate(xs_pad_mass_dw = xs_epiphyte_pad_mass_g - xs_pad_mass_g) %>%
  mutate(iso_mass_dw = iso_foil_dw - iso_foil) %>%
  mutate(gamm_amph_mass_dw = gamm_amph_foil_dw - gamm_amph_foil) %>%
  mutate(caprel_mass_dw = caprel_foil_dw - caprel_foil) %>%
  mutate(limpet_mass_dw = limpet_foil_dw - limpet_foil) %>%
  mutate(gastropod_mass_dw = gastropod_foil_dw - gastropod_foil) %>%
  mutate(crab_mass_dw = crab_foil_dw - crab_foil) 

# check new column names
colnames(sg.bio)

# remove pad and foil weights from dataframe 
#sg.bio = sg.bio %>% 
 #select(-pad_epiphyte_mass_g, -pad_mass_g, -xs_epiphyte_pad_mass_g, -xs_pad_mass_g) %>% #pads
  #select(-rhi_foil_dw_g, -rhi_foil, -shoot_foil, -shoot_foil_dw, -xs_shoot_foil_dw, -xs_shoot_foil) %>% #seagrass
  #select(-iso_foil_dw, -iso_foil, -gamm_amph_foil_dw, -gamm_amph_foil, -caprel_foil_dw, -caprel_foil, -crab_foil_dw, -crab_foil) %>% #crustaceans
  #select(-limpet_foil_dw, -limpet_foil, -gastropod_foil_dw, -gastropod_foil) #molluscs

# check new column names
#colnames(sg.bio)
```


Calculate leaf areas for each blade measured
```{r, echo=FALSE}
# datachunk: TAS


# calculate the leaf area (cm^2) per blade per plant
sg.bio = sg.bio %>% 
  mutate(leaf_area1 = leaf_length1 * leaf_width1, na.rm = TRUE) %>%
  mutate(leaf_area2 = leaf_length2 * leaf_width2, na.rm = TRUE) %>%
  mutate(leaf_area3 = leaf_length3 * leaf_width3, na.rm = TRUE) %>%
  mutate(leaf_area4 = leaf_length4 * leaf_width4, na.rm = TRUE) %>%
  mutate(leaf_area5 = leaf_length5 * leaf_width5, na.rm = TRUE) %>%
  mutate(leaf_area6 = leaf_length6 * leaf_width6, na.rm = TRUE) %>%
  mutate(leaf_area7 = leaf_length7 * leaf_width7, na.rm = TRUE) %>%
  mutate(leaf_area8 = leaf_length8 * leaf_width8, na.rm = TRUE) %>%
  mutate(leaf_area9 = leaf_length9 * leaf_width9, na.rm = TRUE) %>%
  mutate(leaf_area10 = leaf_length10 * leaf_width10, na.rm = TRUE)

# check new column names
colnames(sg.bio)
```

Calculate total leaf area for each plant
```{r}
# datachunk: TAS


# calculate total leaf area per plant (there is no biomass data per blade so need to combine all blades)
sg.bio$tot_leaf_area <- rowSums(sg.bio[,c("leaf_area1", "leaf_area2", "leaf_area3", "leaf_area4", "leaf_area5", "leaf_area6", "leaf_area7", "leaf_area8", "leaf_area9", "leaf_area10")], na.rm = TRUE)

# check new column names
colnames(sg.bio)
```

Calculate mean canopy height (all blades from each plant included)
```{r}
# datachunk: TAS


# mean height of all blades
sg.bio = mutate(sg.bio, mean_leaf_length = rowMeans(select(sg.bio, starts_with("leaf_length")), na.rm = TRUE))

# check new column names
colnames(sg.bio)
```

Determine max canopy height per plant (only tallest blade from each plant included)
```{r, warning = FALSE, message = FALSE}
# datachunk: TAS

sg.bio$max_canopy_height = apply(sg.bio[, 12:21], 1, max, na.rm = TRUE)

colnames(sg.bio)
```

```{r}
#write.csv(eg.bio,'CLEAN_seagrass_biometrics_2017.csv')
```



```{r}
# datachunk: TAS 

library(DT) 

sg.bio = sg.bio %>%
  separate(collection_date, c("Day", "Month", "Year"), sep = "/")

ggplot(sg.bio, aes(site, mean_leaf_length)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~Month)


```


```{r}

ggplot(sg.bio = aes())
```










# TO DO: 

+ Fill absent grazers with 0s so that cacluations below will work (insert this code before the mass_dw calculations)
+ example -- eg.bio[,89:94][is.na(eg.bio[,89:94])] <- 0

























