---
title: "Eelgrass_community_sampling_method_analysis"
author: "Wendel Raymond"
date: "March 20, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Sampling Analysis
How much to we actually need to sample to know if we can detect differences at the eelgrass transect level assuming that we use the same general methodolgy at summer 2017?

```{r}
library(ggplot2)
library(dplyr)
library(pwr)

theme_set(theme_classic())
```


## Data from lab and field transects

```{r standar error funciton}
## standard error of the mean fucntion to use later ##
st.er <- function(x, na.rm = TRUE) {
  stopifnot(is.numeric(x))
  return(sd(x, na.rm = na.rm)/sqrt(length(x)))
}
```

```{r}
# Eelgrass Site
eg.site <- read.csv("../ALL_DATA/seagrass_site_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Biometrics (lab data)
eg.bio <- read.csv("../ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Transect
eg.tran <- read.csv("../ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

Cleaning up dates
```{r cleaning dates}
### Julian Day ###
## Biometrics ##
eg.bio$collection_date <- as.Date(eg.bio$collection_date, format = "%d/%m/%y")
eg.bio$collection_julian <- format(eg.bio$collection_date, "%j")

## Transect ##
eg.tran$date <- as.Date(eg.tran$date, format = "%m/%d/%Y")
eg.tran$date_julian <- format(eg.tran$date, "%j")

## Site ##
eg.site$date <- as.Date(eg.site$date, format = "%m/%d/%Y")
eg.site$date_julian <- format(eg.site$date, "%j")
```

## Calculations
```{r Calculations - biometrics}
### Effective Leaf Area ###
eg.bio$leaf_area1 <- (eg.bio$leaf_length1 * eg.bio$leaf_width1)
eg.bio$leaf_area2 <- (eg.bio$leaf_length2 * eg.bio$leaf_width2)
eg.bio$leaf_area3 <- (eg.bio$leaf_length3 * eg.bio$leaf_width3)
eg.bio$leaf_area4 <- (eg.bio$leaf_length4 * eg.bio$leaf_width4)
eg.bio$leaf_area5 <- (eg.bio$leaf_length5 * eg.bio$leaf_width5)
eg.bio$leaf_area6 <- (eg.bio$leaf_length6 * eg.bio$leaf_width6)
eg.bio$leaf_area7 <- (eg.bio$leaf_length7 * eg.bio$leaf_width7)
eg.bio$leaf_area8 <- (eg.bio$leaf_length8 * eg.bio$leaf_width8)
eg.bio$leaf_area9 <- (eg.bio$leaf_length9 * eg.bio$leaf_width9)
eg.bio$leaf_area10 <- (eg.bio$leaf_length10 * eg.bio$leaf_width10)

eg.bio$leaf_areaT <- rowSums(eg.bio[, 73:82], na.rm = TRUE)

### Epiphytes, Rhizomes, and Shoots Mass ###
## Epiphyte Mass ##
eg.bio$epi_mass <- (eg.bio$pad_epiphyte_mass_g - eg.bio$pad_mass_g)

## Rhizome Mass ##
eg.bio$rhi_mass <- ((eg.bio$rhi_foil_dw_g - eg.bio$rhi_foil) * (5 / eg.bio$rhi_length))

## Shoot Mass ##
eg.bio$shoot_mass <- (eg.bio$shoot_foil_dw - eg.bio$shoot_foil)

## Exess Shoot Mass ##
eg.bio$exshoot_mass <- (eg.bio$xs_shoot_foil_dw - eg.bio$xs_shoot_foil)

## Exess Epiphyte Mass ##
eg.bio$exepi_mass <- (eg.bio$xs_epiphyte_pad_mass_g - eg.bio$xs_pad_mass_g)

### Grazer Mass ###
## Isopod (Idothea rascata) Mass - bulk ##
eg.bio$iso_mass <- (eg.bio$iso_foil_dw - eg.bio$iso_foil)

## Gammarid Amphipod Mass - bulk ##
eg.bio$gamm_mass <- (eg.bio$gamm_amph_foil_dw - eg.bio$gamm_amph_foil)

## Caprellid Amphipod Mass - bulk ##
eg.bio$caprel_mass <- (eg.bio$caprel_foil_dw - eg.bio$caprel_foil)

## Limpet Mass - bulk ##
eg.bio$limp_mass <- (eg.bio$limpet_foil_dw - eg.bio$limpet_foil)

## Other Gastropod Mass - bulk ##
eg.bio$gast_mass <- (eg.bio$gastropod_foil_dw - eg.bio$gastropod_foil)

## Crab Mass ##
eg.bio$crab_mass <- (eg.bio$crab_foil_dw - eg.bio$crab_foil)

## Fill absent grazers with 0s so that cacluations below will work ##
eg.bio[,89:94][is.na(eg.bio[,89:94])] <- 0
```

Taxamonic summaries of grazers.
```{r calculations - biometrics special grazers}
## Crustacean Grazers Mass ##
eg.bio$crust_mass <- (eg.bio$iso_mass + eg.bio$gamm_mass +  eg.bio$caprel_mass + eg.bio$crab_mass)

## Gastropod Grazers Mass ##
eg.bio$gastro_mass <- (eg.bio$limp_mass + eg.bio$gast_mass)

## Total Grazer Mass ##
eg.bio$graz_massT <- rowSums(eg.bio[, 89:94], na.rm = TRUE)
```

Transect, basic calculations
```{r calculations - transect}
## Convert Transect data to per meter ##
eg.tran$eelgrass_shoots_msq <- (4 * eg.tran$eelgrass_shoots_0.25msq)
eg.tran$flowering_shoots_msq <- (4 * eg.tran$flowering_shoots_0.25msq)
eg.tran$macroalgae_cover_msq <- (1 * eg.tran$macroalgae_cover_0.25msq)
eg.tran$diatom_cover_msq <- (1 * eg.tran$diatom_cover_0.25msq)
```

Summarizing biometrics data by site and quadrat.
```{r biometrics - site, quadrat summaries}
## Biometrics data summarized by site and quadrat - shoots and rhizomes ##
quad.bio <- data.frame(
  eg.bio %>% 
    group_by(site, quadrat) %>% 
    summarise(s_shoot_area = mean(leaf_areaT, na.rm = TRUE),
              s_epi_mass = mean(epi_mass, na.rm = TRUE),
              s_shoot_mass = mean(shoot_mass, na.rm = TRUE),
              s_rhi_mass = mean(rhi_mass, na.rm = TRUE),
              s_node1 = mean(node1, na.rm = TRUE),
              s_node2 = mean(node2, na.rm = TRUE),
              s_node3 = mean(node3, na.rm = TRUE),
              s_node4 = mean(node4, na.rm = TRUE),
              s_node5 = mean(node5, na.rm = TRUE),
              s_exshoot_mass = mean(exshoot_mass, na.rm = TRUE),
              s_exepi_mass = mean(exepi_mass, na.rm = TRUE))
)
```

Separating grazers. Since we pooled grazers at the quadrat level that data needs to be pulled out of the master biometrics data and summarized separatly.
```{r biometrics - grazers}
# Extract Grazer biomasses
quad.graz <- data.frame(eg.bio[eg.bio$plant == 1,]) # extract just plant 1 which has all the grazer data
quad.graz <- quad.graz[order(quad.graz[,1], quad.graz[,4]),] # order so that it matches everything else
quad.graz <- data.frame(quad.graz[,c(1, 4, 89:97)]) # reduce to get grazer data only
quad.graz[is.na(quad.graz)] <- 0 # turn NAs to 0s becasue if we sampled everything so if it was not there its a 0
```

Now we can merege transect and biometric data to summaries by site and quadrat.
```{r merge tansect and biometrics data}
## Combined Transect and Biometrics data to give site summaries ##
site.quad <- merge(eg.site[,c(1, 2)], eg.tran, by = "site")
site.quad <- merge(site.quad, quad.bio, by = c("site", "quadrat"))
site.quad <- merge(site.quad, quad.graz, by = c("site", "quadrat"))
```

Now we can preform quadrat calculations at the quadrat level.
```{r calculation - quadrat level}
### Quadrat level caclulations ###
## Aboveground Biomass ##
site.quad$ag_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_shoot_mass)

## Below Ground Biomass ##
site.quad$bg_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_rhi_mass)

## Epiphytes per eeglrass area ##
site.quad$epimass_shootarea <- (site.quad$s_epi_mass / site.quad$s_shoot_area)

## Epiphytes per eelgrass mass ##
site.quad$epimass_shootmass <- (site.quad$s_epi_mass / site.quad$s_shoot_mass)

## Grazer Mass per Quadrat ##
# this is just equal to graz_massT

## Grazer mass per eelgrass mass ##
site.quad$grazmass_shootmass <- (site.quad$graz_massT / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Crustacean mass per eelgrass mass ##
site.quad$crustmass_shootmass <- (site.quad$crust_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Gastropod mass per eelgrass mass ##
site.quad$gastromass_shootmass <- (site.quad$gastro_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass)) 
```

## Comparison
Randomly select 5 qudrats to analyze.
```{r}
qs <- sample(c(1,2,3,4,5,6,7,8), replace = FALSE)
qs[1:5]

site.quad.5 <- site.quad %>% 
  filter(quadrat == 1 | quadrat == 2 | quadrat == 3 | quadrat == 5 | quadrat == 6)
```

Between site comparisons
```{r}
t.test(site.quad$ag_mass[site.quad$site=="2017_L_04"], site.quad$ag_mass[site.quad$site=="2017_H_04"], var.equal = FALSE)

t.test(site.quad.5$ag_mass[site.quad.5$site=="2017_L_04"], site.quad.5$ag_mass[site.quad.5$site=="2017_H_04"], var.equal = FALSE)

t.test(site.quad$bg_mass[site.quad$site=="2017_L_04"], site.quad$bg_mass[site.quad$site=="2017_H_04"], var.equal = FALSE)

t.test(site.quad.5$bg_mass[site.quad.5$site=="2017_L_04"], site.quad.5$bg_mass[site.quad.5$site=="2017_H_04"], var.equal = FALSE)
```


Site summary calcualtions
```{r}
site.bio <- data.frame(
  site.quad %>% 
    group_by(site) %>% 
    summarise(shoot_area = (mean(s_shoot_area, na.rm = TRUE)),
              shoot_area_se = (st.er(s_shoot_area)),
              epi_mass = (mean(s_epi_mass, na.rm = TRUE)),
              epi_mass_se = (st.er(s_epi_mass)),
              shoot_mass = (mean(s_shoot_mass, na.rm = TRUE)),
              shoot_mass_se = (st.er(s_shoot_mass)),
              rhi_mass = (mean(s_rhi_mass, na.rm = TRUE)),
              rhi_mass_se = (st.er(s_rhi_mass)),
              node1 = (mean(s_node1, na.rm = TRUE)),
              node1_se = (st.er(s_node1)),
              node2 = (mean(s_node2, na.rm = TRUE)),
              node2_se = (st.er(s_node2)),
              node3 = (mean(s_node3, na.rm = TRUE)),
              node3_se = (st.er(s_node3)),
              node4 = (mean(s_node4, na.rm = TRUE)),
              node4_se = (st.er(s_node4)),
              node5 = (mean(s_node5, na.rm = TRUE)),
              node5_se = (st.er(s_node5)),
              exshoot_mass = (mean(s_exshoot_mass, na.rm = TRUE)),
              exshoot_mass_se = (st.er(s_exshoot_mass)),
              exepi_mass = (mean(s_exepi_mass, na.rm = TRUE)),
              exepi_mass_se = (st.er(s_exepi_mass)),
              abvgnd_mass = (mean(ag_mass, na.rm = TRUE)),
              abvgnd_mass_se = (st.er(ag_mass)),
              blwgnd_mass = (mean(bg_mass, na.rm = TRUE)),
              blwgnd_mass_se = (st.er(bg_mass)),
              epiphmass_shootarea = (mean(epimass_shootarea, na.rm = TRUE)),
              epiphmass_shootarea_se = (st.er(epimass_shootarea)),
              epiphmass_shootmass = (mean(epimass_shootmass, na.rm = TRUE)),
              epiphmass_shootmass_se = (st.er(epimass_shootmass)),
              grazer_mass = (mean(graz_massT, na.rm = TRUE)),
              grazer_mass_se = (st.er(graz_massT)),
              crus_mass = (mean(crust_mass, na.rm = TRUE)),
              crus_mass_se = (st.er(crust_mass)),
              gast_mass = (mean(gastro_mass, na.rm = TRUE)),
              gast_mass_se = (st.er(gastro_mass)),
              grazermass_shootmass = (mean(grazmass_shootmass, na.rm = TRUE)),
              grazermass_shootmass_se = (st.er(grazmass_shootmass)),
              crusmass_shootmass = (mean(crustmass_shootmass, na.rm = TRUE)),
              crusmass_shootmass_se = (st.er(crustmass_shootmass)),
              gastmass_shootmass = (mean(gastromass_shootmass, na.rm = TRUE)),
              gastmass_shootmass_se = (st.er(gastromass_shootmass)))
)

site.bio.5 <- data.frame(
  site.quad.5 %>% 
    group_by(site) %>% 
    summarise(shoot_area = (mean(s_shoot_area, na.rm = TRUE)),
              shoot_area_se = (st.er(s_shoot_area)),
              epi_mass = (mean(s_epi_mass, na.rm = TRUE)),
              epi_mass_se = (st.er(s_epi_mass)),
              shoot_mass = (mean(s_shoot_mass, na.rm = TRUE)),
              shoot_mass_se = (st.er(s_shoot_mass)),
              rhi_mass = (mean(s_rhi_mass, na.rm = TRUE)),
              rhi_mass_se = (st.er(s_rhi_mass)),
              node1 = (mean(s_node1, na.rm = TRUE)),
              node1_se = (st.er(s_node1)),
              node2 = (mean(s_node2, na.rm = TRUE)),
              node2_se = (st.er(s_node2)),
              node3 = (mean(s_node3, na.rm = TRUE)),
              node3_se = (st.er(s_node3)),
              node4 = (mean(s_node4, na.rm = TRUE)),
              node4_se = (st.er(s_node4)),
              node5 = (mean(s_node5, na.rm = TRUE)),
              node5_se = (st.er(s_node5)),
              exshoot_mass = (mean(s_exshoot_mass, na.rm = TRUE)),
              exshoot_mass_se = (st.er(s_exshoot_mass)),
              exepi_mass = (mean(s_exepi_mass, na.rm = TRUE)),
              exepi_mass_se = (st.er(s_exepi_mass)),
              abvgnd_mass = (mean(ag_mass, na.rm = TRUE)),
              abvgnd_mass_se = (st.er(ag_mass)),
              blwgnd_mass = (mean(bg_mass, na.rm = TRUE)),
              blwgnd_mass_se = (st.er(bg_mass)),
              epiphmass_shootarea = (mean(epimass_shootarea, na.rm = TRUE)),
              epiphmass_shootarea_se = (st.er(epimass_shootarea)),
              epiphmass_shootmass = (mean(epimass_shootmass, na.rm = TRUE)),
              epiphmass_shootmass_se = (st.er(epimass_shootmass)),
              grazer_mass = (mean(graz_massT, na.rm = TRUE)),
              grazer_mass_se = (st.er(graz_massT)),
              crus_mass = (mean(crust_mass, na.rm = TRUE)),
              crus_mass_se = (st.er(crust_mass)),
              gast_mass = (mean(gastro_mass, na.rm = TRUE)),
              gast_mass_se = (st.er(gastro_mass)),
              grazermass_shootmass = (mean(grazmass_shootmass, na.rm = TRUE)),
              grazermass_shootmass_se = (st.er(grazmass_shootmass)),
              crusmass_shootmass = (mean(crustmass_shootmass, na.rm = TRUE)),
              crusmass_shootmass_se = (st.er(crustmass_shootmass)),
              gastmass_shootmass = (mean(gastromass_shootmass, na.rm = TRUE)),
              gastmass_shootmass_se = (st.er(gastromass_shootmass)))
)
```

OK how does n = 8 compare to n = 5 across all sites? Looks like they appear equal.
```{r}
t.test(site.bio$abvgnd_mass, site.bio.5$abvgnd_mass, var.equal = FALSE)

t.test(site.bio$blwgnd_mass, site.bio.5$blwgnd_mass, var.equal = FALSE)

t.test(site.bio$grazermass_shootmass, site.bio.5$grazermass_shootmass, var.equal = FALSE)

t.test(site.bio$epiphmass_shootmass, site.bio.5$epiphmass_shootmass, var.equal = FALSE)
```

