---
title: "Eelgrass_biometrics_data_analysis"
author: "Wendel Raymond"
date: "January 16, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Eelgrass data for analysis
This script generates a dataframe from the eelgrass biometrics data that will be ready for analysis. In genreal nothing will be summerized, data will report values from each replicate at each site.

```{r, echo=FALSE, message = FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)

theme_set(theme_classic())
```


## Data
Data to include here are the eelgrass biometrics data, the sea otter index values, general site level data, and sediment charteriation from the inside the bed transect.

```{r}
# Eelgrass Site
eg.site <- read.csv("../ALL_DATA/seagrass_site_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Biometrics (lab data)
eg.bio <- read.csv("../ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Transect
eg.tran <- read.csv("../ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Sea Otter Impact Index
so.index <- read.csv("../ALL_DATA/sea_otter_impact_index_2017_new.csv", stringsAsFactors = FALSE, header = TRUE)

# Sediment
sed.site <- read.csv("../ALL_DATA/seagrass_seaotter_pit_sediment_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
``` 

## Sediment data
We will use the primary sediment from the inside transect in each bin at each site.
```{r}
seds <- sed.site %>% 
  filter(trans_type == "Inside")

seds <- seds[, c(1, 5, 8, 10)]
```

## Biometric calculations
We need to calcualte things using transect and biometric data. The results will be values at the quadrat level.

We will start with biometric calculations
```{r}
### Effective Leaf Area ###
eg.bio$leaf_area1 <- (eg.bio$leaf_length1 * eg.bio$leaf_width1)
eg.bio$leaf_area2 <- (eg.bio$leaf_length2 * eg.bio$leaf_width2)
eg.bio$leaf_area3 <- (eg.bio$leaf_length3 * eg.bio$leaf_width3)
eg.bio$leaf_area4 <- (eg.bio$leaf_length4 * eg.bio$leaf_width4)
eg.bio$leaf_area5 <- (eg.bio$leaf_length5 * eg.bio$leaf_width5)
eg.bio$leaf_area6 <- (eg.bio$leaf_length6 * eg.bio$leaf_width6)
eg.bio$leaf_area7 <- (eg.bio$leaf_length7 * eg.bio$leaf_width7)
eg.bio$leaf_area8 <- (eg.bio$leaf_length8 * eg.bio$leaf_width8)
eg.bio$leaf_area9 <- (eg.bio$leaf_length9 * eg.bio$leaf_width9)
eg.bio$leaf_area10 <- (eg.bio$leaf_length10 * eg.bio$leaf_width10)

eg.bio$leaf_areaT <- rowSums(eg.bio[, 72:81], na.rm = TRUE)

### Epiphytes, Rhizomes, and Shoots Mass ###
## Epiphyte Mass ##
eg.bio$epi_mass <- (eg.bio$pad_epiphyte_mass_g - eg.bio$pad_mass_g)

## Rhizome Mass ##
eg.bio$rhi_mass <- ((eg.bio$rhi_foil_dw_g - eg.bio$rhi_foil) * (5 / eg.bio$rhi_length))

## Shoot Mass ##
eg.bio$shoot_mass <- (eg.bio$shoot_foil_dw - eg.bio$shoot_foil)

## Exess Shoot Mass ##
eg.bio$exshoot_mass <- (eg.bio$xs_shoot_foil_dw - eg.bio$xs_shoot_foil)

## Exess Epiphyte Mass ##
eg.bio$exepi_mass <- (eg.bio$xs_epiphyte_pad_mass_g - eg.bio$xs_pad_mass_g)

### Grazer Mass ###
## Isopod (Idothea rascata) Mass - bulk ##
eg.bio$iso_mass <- (eg.bio$iso_foil_dw - eg.bio$iso_foil)

## Gammarid Amphipod Mass - bulk ##
eg.bio$gamm_mass <- (eg.bio$gamm_amph_foil_dw - eg.bio$gamm_amph_foil)

## Caprellid Amphipod Mass - bulk ##
eg.bio$caprel_mass <- (eg.bio$caprel_foil_dw - eg.bio$caprel_foil)

## Limpet Mass - bulk ##
eg.bio$limp_mass <- (eg.bio$limpet_foil_dw - eg.bio$limpet_foil)

## Other Gastropod Mass - bulk ##
eg.bio$gast_mass <- (eg.bio$gastropod_foil_dw - eg.bio$gastropod_foil)

## Crab Mass ##
eg.bio$crab_mass <- (eg.bio$crab_foil_dw - eg.bio$crab_foil)

## Fill absent grazers with 0s so that cacluations below will work ##
eg.bio[,88:93][is.na(eg.bio[,88:93])] <- 0

### Taxamonic summaries of grazers ###

## Crustacean Grazers Mass ##
eg.bio$crust_mass <- (eg.bio$iso_mass + eg.bio$gamm_mass +  eg.bio$caprel_mass + eg.bio$crab_mass)

## Gastropod Grazers Mass ##
eg.bio$gastro_mass <- (eg.bio$limp_mass + eg.bio$gast_mass)

## Total Grazer Mass ##
eg.bio$graz_massT <- rowSums(eg.bio[, 88:93], na.rm = TRUE)
```

Transect basic calculations
```{r calculations - transect}
## Convert Transect data to per meter ##
eg.tran$eelgrass_shoots_msq <- (4 * eg.tran$eelgrass_shoots_0.25msq)
eg.tran$flowering_shoots_msq <- (4 * eg.tran$flowering_shoots_0.25msq)
eg.tran$macroalgae_cover_msq <- (1 * eg.tran$macroalgae_cover_0.25msq)
eg.tran$diatom_cover_msq <- (1 * eg.tran$diatom_cover_0.25msq)
```

Summarizing biometrics data by site and quadrat
```{r biometrics - site, quadrat summaries}
## Biometrics data summarized by site and quadrat - shoots and rhizomes ##
quad.bio <- data.frame(
  eg.bio %>% 
    group_by(site, quadrat) %>% 
    summarise(shoot_area = mean(leaf_areaT, na.rm = TRUE),
              epi_mass = mean(epi_mass, na.rm = TRUE),
              shoot_mass = mean(shoot_mass, na.rm = TRUE),
              rhi_mass = mean(rhi_mass, na.rm = TRUE),
              node1 = mean(node1, na.rm = TRUE),
              node2 = mean(node2, na.rm = TRUE),
              node3 = mean(node3, na.rm = TRUE),
              node4 = mean(node4, na.rm = TRUE),
              node5 = mean(node5, na.rm = TRUE),
              exshoot_mass = mean(exshoot_mass, na.rm = TRUE),
              exepi_mass = mean(exepi_mass, na.rm = TRUE))
)
```

Separating grazers. Since we pooled grazers at the quadrat level that data needs to be pulled out of the master biometrics data and summarized separatly.
```{r biometrics - grazers}
# Extract Grazer biomasses
quad.graz <- data.frame(eg.bio[eg.bio$plant == 1,]) # extract just plant 1 which has all the grazer data
quad.graz <- quad.graz[order(quad.graz[,1], quad.graz[,4]),] # order so that it matches everything else
quad.graz <- data.frame(quad.graz[,c(1, 4, 88:96)]) # reduce to get grazer data only
quad.graz[is.na(quad.graz)] <- 0 # turn NAs to 0s becasue if we sampled everything so if it was not there its a 0
```

Now we can merege transect and biometric data to summaries by site and quadrat.
```{r merge tansect and biometrics data}
## Combined Transect and Biometrics data to give site summaries ##
site.quad <- merge(eg.site[,c(1, 2)], eg.tran, by = "site")
site.quad <- merge(site.quad, quad.bio, by = c("site", "quadrat"))
site.quad <- merge(site.quad, quad.graz, by = c("site", "quadrat"))
```

Now we can preform quadrat calculations at the quadrat level.
```{r calculation - quadrat level}
### Quadrat level caclulations ###
## Aboveground Biomass ##
site.quad$ag_mass <- (site.quad$eelgrass_shoots_msq * site.quad$shoot_mass)

## Below Ground Biomass ##
site.quad$bg_mass <- (site.quad$eelgrass_shoots_msq * site.quad$rhi_mass)

## Epiphytes per eeglrass area ##
site.quad$epimass_shootarea <- ((site.quad$epi_mass + !is.na(site.quad$exepi_mass)) / site.quad$shoot_area)

## Epiphytes per eelgrass mass ##
site.quad$epimass_shootmass <- ((site.quad$epi_mass + !is.na(site.quad$exepi_mass)) / site.quad$shoot_mass)

## Total leaf area ##
site.quad$shoot_areaT <- (site.quad$shoot_area * site.quad$eelgrass_shoots_msq)

## Grazer Mass per Quadrat ##
# this is just equal to graz_massT

## Grazer mass per eelgrass mass ##
site.quad$grazmass_shootmass <- (site.quad$graz_massT / (site.quad$shoot_mass + site.quad$exshoot_mass))

## Crustacean mass per eelgrass mass ##
site.quad$crustmass_shootmass <- (site.quad$crust_mass / (site.quad$shoot_mass + site.quad$exshoot_mass))

## Gastropod mass per eelgrass mass ##
site.quad$gastromass_shootmass <- (site.quad$gastro_mass / (site.quad$shoot_mass + site.quad$exshoot_mass)) 
```

## Merging
Use caution when merging.

First we need to create continuity between "bins" and "quadrats". Everything will be renamed to quadrat. Also this needs to be converted to a numeric just to make sorting easier.
```{r}
colnames(seds)[2] <- "quadrat"

seds$quadrat <- as.numeric(seds$quadrat)

site.quad$quadrat <- as.numeric(site.quad$quadrat)
```

Now create a starter dataframe with all the site data. This includes cleaning up the site level data etc. This should be 210 rows long (deep?)
```{r}
# Data we care about
dat <- eg.site[, 1:27]

# light attenuation
dat$light_attenu <- dat$light_intensity_umol.m2.sec_transect / dat$light_intensity_umol.m2.sec_surface

# Date shananagans
dat$date <- as.Date(dat$date, format = "%m/%d/%Y")
dat$date_julian <- format(dat$date, "%j")
```

Append sea otter index values
```{r}
dat <- merge(dat, so.index[, c(1, 8:16)], by = "site")
```

The actual merge
```{r}
dat <- merge(dat, seds, by = "site")
dat <- merge(dat, site.quad[, c(1, 2, 8:47)], by = c("site", "quadrat"), all = TRUE)

colnames(dat)[7] <- "start_time_site"
colnames(dat)[8] <- "end_time_site"
colnames(dat)[42] <- "start_time_transect"
colnames(dat)[43] <- "end_time_transect"

str(dat)
```

### Export
```{r}
write.csv(dat, "../ALL_DATA/eelgrass_bio_sed_transect_derived.csv", row.names = FALSE)
```

# Crab Data for analysis
This script generates a dataframe from the crab pot data that will be ready for analysis. In genreal nothing will be summerized, data will report values from each replicate at each site.

## Data
We need the crab pot data and lenght weight conversion data
```{r}
crab <- read.csv("../ALL_DATA/seagrass_crab_pot_2017_RAW.csv", header = TRUE, stringsAsFactors = FALSE)

crabLW <- read.csv("../ALL_DATA/crab_length_weight_conversion_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

## Calculations
The first thing to do is to add the length - weight conversions to the staring data frame so that we can convert carapace widths the biomass. This will be done by adding the species specific coefficients to the data frame. Note the this conversion is to what is considered sea otter edible biomass. Also note that fish are recorded in this data that might be useful, but from this point on we are going to remove all fishes. 

```{r crabs only}
crab <- crab %>% 
  filter(taxon == "Decapoda")

unique(crab$sp_code)
```

Now we will add length weight conversion coefficients
```{r adding length to weight conversion}
crab <- merge(crab, crabLW, by = "sp_code")
crab <- crab[,c(1:21, 23:29)] # remove duplicated 
colnames(crab)[14] <- "taxon"
```

Calculate mass
```{r calcualte mass}
crab$mass_g <- (crab$a_mean * (crab$carapace_width_mm)^crab$b_mean)
range(crab$mass_g, na.rm = TRUE)

ggplot(crab, aes(x = mass_g, y = carapace_width_mm)) +
  geom_point(size = 1) +
  facet_wrap(~sp_code)
```

## Clean data and merge
Pool all pots but keep strings. Final dataframe should include instances where no crabs where caught, therefore there should be 3 X 21 X 6 = 378 rows. Now for later analysis we may only be interestedin total mass, but I htink its worht it to have it divided by in species if we, at some point, want to run analyses on differnet species.
```{r}
## Prepping data ##
crab.string <- crab %>% 
  group_by(site, string, sp_code) %>% 
  summarise(mass_g = sum(mass_g))

sites <- unique(eg.bio$site)
sp <- unique(crab$sp_code)
strings <- as.character(c(1:3))

crab.dat <- data.frame(c(rep(sites[1], 18), rep(sites[2], 18), rep(sites[3], 18), rep(sites[4], 18), rep(sites[5], 18), rep(sites[6], 18), rep(sites[7], 18), rep(sites[8], 18), rep(sites[9], 18), rep(sites[10], 18), rep(sites[11], 18), rep(sites[12], 18), rep(sites[13], 18), rep(sites[14], 18), rep(sites[15], 18), rep(sites[16], 18), rep(sites[17], 18), rep(sites[18], 18), rep(sites[19], 18), rep(sites[20], 18), rep(sites[21], 18)))

crab.dat$string <- rep(c(rep(strings[1], 6), rep(strings[2], 6), rep(strings[3], 6)), 21)

crab.dat$sp_code <- sp

colnames(crab.dat)[1] <- "site"

# Merge
crab.dat <- merge(crab.dat, crab.string, by = c("site", "string", "sp_code"), all.x = TRUE)
crab.dat$mass_g[is.na(crab.dat$mass_g)] <- 0
crab.dat <- merge(unique(crab[, 2:9]), crab.dat, by = "site", all.y = TRUE)

```

Export data for analysis
```{r}
write.csv(crab.dat, "../ALL_DATA/eelgrass_crab_pot_derived.csv", row.names = FALSE)
```

