---
title: "Eelgrass_biometrics_calculations"
author: "Wendel Raymond"
date: "December 5, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Eelgrass biometric data calculations
From the raw cleaned data this script will export a file summarized by site ready for analysis. Major task are the calculation of dry weights of eelgrass, rhizomes, and grazers. Other calculations include scaling transect data up to a per square meter.

## Libraries
Processing of this data will require the following
```{r libraries}
library(dplyr)
library(ggplot2)
```

## Functions
```{r standar error funciton}
## standard error of the mean fucntion to use later ##
st.er <- function(x, na.rm = TRUE) {
  stopifnot(is.numeric(x))
  return(sd(x, na.rm = na.rm)/sqrt(length(x)))
}
```

## Data to import
We want to combine a few sets of data here so that we can run meaning full analyses. These are site characterization data, eelgrass transect data, eelgrass biometrics data, sea otter index data, and site nutirent data.

```{r data import, echo = FALSE}
# Eelgrass Site
eg.site <- read.csv("../ALL_DATA/seagrass_site_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Biometrics (lab data)
eg.bio <- read.csv("../ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

# Eelgrass Transect
eg.tran <- read.csv("../ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

# Sea Otter Impact Index
so.index <- read.csv("../ALL_DATA/sea_otter_impact_index_new.csv", stringsAsFactors = FALSE, header = TRUE)
```

## Data Check
Checking the data. This is just a basic check of the data to make sure eveything looks right.
```{r checking data}
# datachunk creator: WR
# Structure
str(eg.tran)
str(eg.site)
str(eg.bio)
str(so.index)
str(nuts)

# Additional code could be added here at anytime.
```

## Data prep
We want the the structure of some columns to be a certain way to that they are treated correclty for our purposes. 

Eelgrass biometrics and transect: convert plant and quadrat columns to factors
```{r number to factors}
# datachunk creator: WR
# Transect #
eg.tran$quadrat <- as.factor(eg.tran$quadrat)

# Biometrics #
eg.bio$plant <- as.factor(eg.bio$plant)
eg.bio$quadrat <- as.factor(eg.bio$quadrat)
```

Changing start and end time column names so its not confusing ###
```{r changing column names}
# datachunk creator: WR

## Start and End times ##
# Site
colnames(eg.site)[6] <- "site_start_time"
colnames(eg.site)[7] <- "site_end_time"

# Transect
colnames(eg.tran)[6] <- "transect_start_time"
colnames(eg.tran)[7] <- "transect_end_time"

```

Cleaning up dates
```{r cleaning dates}
### Julian Day ###
## Biometrics ##
eg.bio$collection_date <- as.Date(eg.bio$collection_date, format = "%d/%m/%y")
eg.bio$collection_julian <- format(eg.bio$collection_date, "%j")

## Transect ##
eg.tran$date <- as.Date(eg.tran$date, format = "%m/%d/%Y")
eg.tran$date_julian <- format(eg.tran$date, "%j")

## Site ##
eg.site$date <- as.Date(eg.site$date, format = "%m/%d/%Y")
eg.site$date_julian <- format(eg.site$date, "%j")
```

## Calculations
This is broken up in chunks for clarity.
Biometrics, basic calculations
```{r Calculations - biometrics}
### Effective Leaf Area ###
eg.bio$leaf_area1 <- (eg.bio$leaf_length1 * eg.bio$leaf_width1)
eg.bio$leaf_area2 <- (eg.bio$leaf_length2 * eg.bio$leaf_width2)
eg.bio$leaf_area3 <- (eg.bio$leaf_length3 * eg.bio$leaf_width3)
eg.bio$leaf_area4 <- (eg.bio$leaf_length4 * eg.bio$leaf_width4)
eg.bio$leaf_area5 <- (eg.bio$leaf_length5 * eg.bio$leaf_width5)
eg.bio$leaf_area6 <- (eg.bio$leaf_length6 * eg.bio$leaf_width6)
eg.bio$leaf_area7 <- (eg.bio$leaf_length7 * eg.bio$leaf_width7)
eg.bio$leaf_area8 <- (eg.bio$leaf_length8 * eg.bio$leaf_width8)
eg.bio$leaf_area9 <- (eg.bio$leaf_length9 * eg.bio$leaf_width9)
eg.bio$leaf_area10 <- (eg.bio$leaf_length10 * eg.bio$leaf_width10)

eg.bio$leaf_areaT <- rowSums(eg.bio[, 73:82], na.rm = TRUE)
eg.bio$leaf_lengthT <- rowSums(eg.bio[, 12:21], na.rm = TRUE)

### Epiphytes, Rhizomes, and Shoots Mass ###
## Epiphyte Mass ##
eg.bio$epi_mass <- (eg.bio$pad_epiphyte_mass_g - eg.bio$pad_mass_g)

## Rhizome Mass ##
eg.bio$rhi_mass <- ((eg.bio$rhi_foil_dw_g - eg.bio$rhi_foil) * (5 / eg.bio$rhi_length))

## Shoot Mass ##
eg.bio$shoot_mass <- (eg.bio$shoot_foil_dw - eg.bio$shoot_foil)

## Exess Shoot Mass ##
eg.bio$exshoot_mass <- (eg.bio$xs_shoot_foil_dw - eg.bio$xs_shoot_foil)

## Exess Epiphyte Mass ##
eg.bio$exepi_mass <- (eg.bio$xs_epiphyte_pad_mass_g - eg.bio$xs_pad_mass_g)

### Grazer Mass ###
## Isopod (Idothea rascata) Mass - bulk ##
eg.bio$iso_mass <- (eg.bio$iso_foil_dw - eg.bio$iso_foil)

## Gammarid Amphipod Mass - bulk ##
eg.bio$gamm_mass <- (eg.bio$gamm_amph_foil_dw - eg.bio$gamm_amph_foil)

## Caprellid Amphipod Mass - bulk ##
eg.bio$caprel_mass <- (eg.bio$caprel_foil_dw - eg.bio$caprel_foil)

## Limpet Mass - bulk ##
eg.bio$limp_mass <- (eg.bio$limpet_foil_dw - eg.bio$limpet_foil)

## Other Gastropod Mass - bulk ##
eg.bio$gast_mass <- (eg.bio$gastropod_foil_dw - eg.bio$gastropod_foil)

## Crab Mass ##
eg.bio$crab_mass <- (eg.bio$crab_foil_dw - eg.bio$crab_foil)

## Fill absent grazers with 0s so that cacluations below will work ##
eg.bio[,90:95][is.na(eg.bio[,90:95])] <- 0
```

Taxamonic summaries of grazers.
```{r calculations - biometrics special grazers}
## Crustacean Grazers Mass ##
eg.bio$crust_mass <- (eg.bio$iso_mass + eg.bio$gamm_mass +  eg.bio$caprel_mass + eg.bio$crab_mass)

## Gastropod Grazers Mass ##
eg.bio$gastro_mass <- (eg.bio$limp_mass + eg.bio$gast_mass)

## Total Grazer Mass ##
eg.bio$graz_massT <- rowSums(eg.bio[, 89:94], na.rm = TRUE)
```

Transect, basic calculations
```{r calculations - transect}
## Convert Transect data to per meter ##
eg.tran$eelgrass_shoots_msq <- (4 * eg.tran$eelgrass_shoots_0.25msq)
eg.tran$flowering_shoots_msq <- (4 * eg.tran$flowering_shoots_0.25msq)
eg.tran$macroalgae_cover_msq <- (1 * eg.tran$macroalgae_cover_0.25msq)
eg.tran$diatom_cover_msq <- (1 * eg.tran$diatom_cover_0.25msq)
```

Summarizing biometrics data by site and quadrat.
```{r biometrics - site, quadrat summaries}
## Biometrics data summarized by site and quadrat - shoots and rhizomes ##
quad.bio <- data.frame(
  eg.bio %>% 
    group_by(site, quadrat) %>% 
    summarise(s_shoot_area = mean(leaf_areaT, na.rm = TRUE),
              s_shoot_length = mean(leaf_lengthT, na.rm = TRUE),
              s_epi_mass = mean(epi_mass, na.rm = TRUE),
              s_shoot_mass = mean(shoot_mass, na.rm = TRUE),
              s_rhi_mass = mean(rhi_mass, na.rm = TRUE),
              s_node1 = mean(node1, na.rm = TRUE),
              s_node2 = mean(node2, na.rm = TRUE),
              s_node3 = mean(node3, na.rm = TRUE),
              s_node4 = mean(node4, na.rm = TRUE),
              s_node5 = mean(node5, na.rm = TRUE),
              s_exshoot_mass = mean(exshoot_mass, na.rm = TRUE),
              s_exepi_mass = mean(exepi_mass, na.rm = TRUE))
)
```

Separating grazers. Since we pooled grazers at the quadrat level that data needs to be pulled out of the master biometrics data and summarized separatly.
```{r biometrics - grazers}
# Extract Grazer biomasses
quad.graz <- data.frame(eg.bio[eg.bio$plant == 1,]) # extract just plant 1 which has all the grazer data
quad.graz <- quad.graz[order(quad.graz[,1], quad.graz[,4]),] # order so that it matches everything else
quad.graz <- data.frame(quad.graz[,c(1, 4, 90:98)]) # reduce to get grazer data only
quad.graz[is.na(quad.graz)] <- 0 # turn NAs to 0s becasue if we sampled everything so if it was not there its a 0
```

Now we can merege transect and biometric data to summaries by site and quadrat.
```{r merge tansect and biometrics data}
## Combined Transect and Biometrics data to give site summaries ##
site.quad <- merge(eg.site[,c(1, 2)], eg.tran, by = "site")
site.quad <- merge(site.quad, quad.bio, by = c("site", "quadrat"))
site.quad <- merge(site.quad, quad.graz, by = c("site", "quadrat"))
```

Now we can preform quadrat calculations at the quadrat level.
```{r calculation - quadrat level}
### Quadrat level caclulations ###
## Aboveground Biomass ##
site.quad$ag_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_shoot_mass)

## Below Ground Biomass ##
site.quad$bg_mass <- (site.quad$eelgrass_shoots_msq * site.quad$s_rhi_mass)

## Epiphytes per eeglrass area ##
site.quad$epimass_shootarea <- (site.quad$s_epi_mass / site.quad$s_shoot_area)

## Epiphytes per total length ##
site.quad$epimass_shootlength <- (site.quad$s_epi_mass / site.quad$s_shoot_length)

## Epiphytes per eelgrass mass ##
site.quad$epimass_shootmass <- (site.quad$s_epi_mass / site.quad$s_shoot_mass)

## Grazer Mass per Quadrat ##
# this is just equal to graz_massT

## Grazer mass per eelgrass mass ##
site.quad$grazmass_shootmass <- (site.quad$graz_massT / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Grazer mass per total length ##
site.quad$grazmass_shootlength <- (site.quad$graz_massT / site.quad$s_shoot_length)

## Crustacean mass per eelgrass mass ##
site.quad$crustmass_shootmass <- (site.quad$crust_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass))

## Gastropod mass per eelgrass mass ##
site.quad$gastromass_shootmass <- (site.quad$gastro_mass / (site.quad$s_shoot_mass + site.quad$s_exshoot_mass)) 
```

## Compiling result of calculations to a usable data set.
We can now take the intermediate data frame generated above to make a complied data frame.
```{r Compiling}
#####----- Master Compile and Calculations -----#####
### Site Level Data ###
tran.dat <- eg.tran %>% 
  group_by(site) %>% 
  distinct(primary_observer, secondary_observer, transect_start_time, transect_end_time, depth_m)
  
### Master - more will be added later ###
dat <- data.frame(cbind(eg.site[, c(1:3, 32, 4:9)], tran.dat[, 2:5], so.index[, 12:16], eg.site[, 14:26]))
```

Final set of calculations at site level.
```{r calculations - site level}
## Transect data summarized by site ##
site.tran <- data.frame(
  eg.tran %>% 
    group_by(site) %>% 
    summarise(shoot_dens = (mean(eelgrass_shoots_0.25msq * 4)),
              shoot_dens_se = (st.er(eelgrass_shoots_0.25msq * 4)),
              macro_dens = (mean(macroalgae_cover_0.25msq * 1)),
              macro_dens_se = (st.er(macroalgae_cover_0.25msq * 1)),
              diatom_dens = (mean(diatom_cover_0.25msq * 1)),
              diatom_dens_se = (st.er(diatom_cover_0.25msq * 1)),
              flower_dens = (mean(flowering_shoots_0.25msq * 4)),
              flower_dens_se = (st.er(flowering_shoots_0.25msq * 4)))
)

## Biometrics data summarized by site ##
site.bio <- data.frame(
  site.quad %>% 
    group_by(site) %>% 
    summarise(shoot_area = (mean(s_shoot_area, na.rm = TRUE)),
              shoot_area_se = (st.er(s_shoot_area)),
              shoot_length = (mean(s_shoot_length, na.rm = TRUE)),
              shoot_length_se = (st.er(s_shoot_length, na.rm = TRUE)),
              epi_mass = (mean(s_epi_mass, na.rm = TRUE)),
              epi_mass_se = (st.er(s_epi_mass)),
              shoot_mass = (mean(s_shoot_mass, na.rm = TRUE)),
              shoot_mass_se = (st.er(s_shoot_mass)),
              rhi_mass = (mean(s_rhi_mass, na.rm = TRUE)),
              rhi_mass_se = (st.er(s_rhi_mass)),
              node1 = (mean(s_node1, na.rm = TRUE)),
              node1_se = (st.er(s_node1)),
              node2 = (mean(s_node2, na.rm = TRUE)),
              node2_se = (st.er(s_node2)),
              node3 = (mean(s_node3, na.rm = TRUE)),
              node3_se = (st.er(s_node3)),
              node4 = (mean(s_node4, na.rm = TRUE)),
              node4_se = (st.er(s_node4)),
              node5 = (mean(s_node5, na.rm = TRUE)),
              node5_se = (st.er(s_node5)),
              exshoot_mass = (mean(s_exshoot_mass, na.rm = TRUE)),
              exshoot_mass_se = (st.er(s_exshoot_mass)),
              exepi_mass = (mean(s_exepi_mass, na.rm = TRUE)),
              exepi_mass_se = (st.er(s_exepi_mass)),
              abvgnd_mass = (mean(ag_mass, na.rm = TRUE)),
              abvgnd_mass_se = (st.er(ag_mass)),
              blwgnd_mass = (mean(bg_mass, na.rm = TRUE)),
              blwgnd_mass_se = (st.er(bg_mass)),
              epiphmass_shootarea = (mean(epimass_shootarea, na.rm = TRUE)),
              epiphmass_shootarea_se = (st.er(epimass_shootarea)),
              epiphmass_shootlength = (mean(epimass_shootlength, na.rm = TRUE)),
              epiphmass_shootlength_se = (st.er(epimass_shootlength, na.rm = TRUE)),
              epiphmass_shootmass = (mean(epimass_shootmass, na.rm = TRUE)),
              epiphmass_shootmass_se = (st.er(epimass_shootmass)),
              grazer_mass = (mean(graz_massT, na.rm = TRUE)),
              grazer_mass_se = (st.er(graz_massT)),
              crus_mass = (mean(crust_mass, na.rm = TRUE)),
              crus_mass_se = (st.er(crust_mass)),
              gast_mass = (mean(gastro_mass, na.rm = TRUE)),
              gast_mass_se = (st.er(gastro_mass)),
              grazermass_shootmass = (mean(grazmass_shootmass, na.rm = TRUE)),
              grazermass_shootmass_se = (st.er(grazmass_shootmass)),
              grazermass_shootlength = (mean(grazmass_shootlength, na.rm = TRUE)),
              grazermass_shootlength_se = (st.er(grazmass_shootlength)),
              crusmass_shootmass = (mean(crustmass_shootmass, na.rm = TRUE)),
              crusmass_shootmass_se = (st.er(crustmass_shootmass)),
              gastmass_shootmass = (mean(gastromass_shootmass, na.rm = TRUE)),
              gastmass_shootmass_se = (st.er(gastromass_shootmass)))
)
```

## Final merge
Combine everything
```{r final merge}
### Merge Transect and Biometrics data to Master dat ###
## Transect ##
dat <- merge(dat, site.tran, by = "site")

## Biometrics ##
dat <- merge(dat, site.bio, by = "site")

### Clean up ###
dat$specific_conductivity_transect <- as.numeric(dat$specific_conductivity_transect)

### Add site number ###
dat <- dat[order(-dat$sea_otter_index_tr), ]
dat$site_num <- as.factor(1:21)
```

## Export
Export data to ALL_DATA folder for use
```{r export}
#####----- Export -----#####
write.csv(dat, "../ALL_DATA/eelgrass_and_grazer_2017_derived.csv", row.names = FALSE)
```
