---
title: "Shorzone_seagrass_analysis"
author: "Wendel Raymond"
date: "February 26, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Analysis of Shorezone data
We will compare the extent of seagrass in areas with and without sea otters.

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(rgeos)
library(raster)
library(gdistance)
library(spatstat)
library(leaflet)
library(spatialEco)
```

## Data
Spatial data for seagrass extent and sea otter accupation will be needed.
```{r load data}
## Shorezone data ##
shore <- readOGR(dsn = "../ALL_DATA/spatial_data", layer="SEAK_shoreline")
shore <- spTransform(shore, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))

## Sea Otter occupation ##
sd2003 <- readOGR(dsn = "../ALL_DATA/spatial_data", layer="Sea_Otter_disp_2003") 
sd2003 <- spTransform(sd2003, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))

# 2010 Sea Otters
sd2010 <- readOGR(dsn = "../ALL_DATA/spatial_data", layer="Sea_Otter_disp_2010") 
sd2010 <- spTransform(sd2010, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

### Defining shore types
Seagrass shorelines defined as continuous (C) or patch (P) and suitable shoreline as semi-protected, protected, or very protected with partailly mobile, mobile or esturanie sediment classifications.
```{r shore types}
## Seagrass shorelines ##
sg_c <- subset(shore, ZOS == "C")
sg_c <- spTransform(sg_c, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))

sg_p <- subset(shore, ZOS == "P")
sg_p <- spTransform(sg_p, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))

## Suitable for seagrass ##
sg_suit <- shore[which(shore$HabClass == 41 | shore$HabClass == 42 | shore$HabClass == 43 | shore$HabClass == 51 | shore$HabClass == 52 | shore$HabClass == 53 | shore$HabClass == 61 | shore$HabClass == 62 | shore$HabClass == 63), ]
sg_suit <- spTransform(sg_suit, CRS("+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
```

## Shoreline lengths
```{r lengths}
## Raw totals ##
dat <- data.frame(type = c("continuous", "patchy", "totalSG", "suitable"), length_km = c(sum(sg_c$Shape_Leng / 1000), sum(sg_p$Shape_Leng / 1000), 0, sum(sg_suit$Shape_Leng / 1000)))

dat[3,2] <- (dat[1,2] + dat[2,2])

## With Sea otters ##
so_sg_c <- intersect(sg_c, sd2010)

```

