---
title: "Exploration of sediment influence on seagrass"
author: "Tiff Stephens"
#date: "1/6/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr); library(tidyr); library(plyr); library(reshape2); library(ggplot2); library(DT); library(leaflet); library(htmlwidgets); library(htmltools); library(shiny); library(mapview); library(sp); library(sf); library(knitr); library(cowplot); library(ggpmisc)
theme_set(theme_classic())
```


<br><br>

#### The intention of this .Rmd script is to explore how sediment type (primary and secondary classifications) influences various variables that we measured in Summer 2017. The sediment type data presented here is qualitative, with a quantitative edge -- i.e. sediment type was classified as 1 of 10 types (1:10 :: fine:big). 
```{r, include = FALSE}
sed.table <- matrix(c('1','2','3','4','5','6','7','8','9','10', 'Mud', 'Sandy mud', 'Muddy sand', 'Sand', 'Coarse sand', 'Pebble', 'Gravel', 'Cobble', 'Boulder', 'Reef'), ncol = 2)
colnames(sed.table) <- c('Numeric Ordinal ID', 'Adjective ID')
```
<br><br>
```{r, echo = FALSE}
datatable(sed.table, options = list(backgroundPosition = 'center'), width = 400)
```

<br><br><br><br>




#### To attack this, we need the sediment_pit, biometrics, and transect dataframes from the seagrass sites. Also throw in the coordinate info. Import all of these cleaned files from the GitHub repositry. 
```{r}
df.sedpit <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/seagrass_seaotter_pit_sediment_2017_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

df.bio <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

df.trans <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

df.coords <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/sites_coordinates.csv", stringsAsFactors = FALSE, header = TRUE)
```
<br><br><br><br>


### 1. Tidy: delete unwanted variables from each dataframe to reduce clutter
<br>
```{r, include = FALSE}
str(df.sedpit)
na.omit(df.sedpit)

# don't need these columns
df.sedpit <- within(df.sedpit, rm(X)) # odd extra first column
df.sedpit <- within(df.sedpit, rm(sed1_type)) # redundant with the numeric values
df.sedpit <- within(df.sedpit, rm(sed2_type)) # redundant with the numeric values
df.sedpit <- within(df.sedpit, rm(field_collector)) # who cares for this
df.sedpit <- within(df.sedpit, rm(trans_m)) # don't need to binning factors
```


```{r, include = FALSE}
str(df.trans)
na.omit(df.trans)

# don't need these columns
df.trans <- within(df.trans, rm(primary_observer))
df.trans <- within(df.trans, rm(secondary_observer))
df.trans <- within(df.trans, rm(start_time))
df.trans <- within(df.trans, rm(end_time))
df.trans <- within(df.trans, rm(notes))
str(df.trans)

# convert everything to meter-squared values
df.trans <- df.trans %>%
  mutate(algae_cover_m2 = macroalgae_cover_0.25msq * 1, na.rm = TRUE) %>%
  mutate(epiphyte_cover_m2 = diatom_cover_0.25msq * 1, na.rm = TRUE) %>%
  mutate(seagrass_count_m2 = eelgrass_shoots_0.25msq * 4, na.rm = TRUE) %>%
  mutate(flower_count_m2 = flowering_shoots_0.25msq * 4, na.rm = TRUE) %>%
  select(-na.rm, -macroalgae_cover_0.25msq, -diatom_cover_0.25msq, -eelgrass_shoots_0.25msq, -flowering_shoots_0.25msq)
str(df.trans)
```


```{r, include = FALSE}
str(df.bio)
na.omit(df.bio)

# change column name for consistency with other DFs
colnames(df.bio)[which(names(df.bio) == "collection_date")] <- "date"


# so many obvious unwanted variables in the df for desired analysis; start by removing those
colnames(df.bio) # find which columns to delete in bulk (don't need grazers + epiphytes)
df.bio <- df.bio[, -c(40:71)] # delete columns (grazers + epiphytes)
df.bio <- within(df.bio, rm(rhi_mass_fw))
df.bio <- within(df.bio, rm(shoot_mass_fw))
colnames(df.bio) # recheck column names for accuracy (last should be "shoot_foil_dw")


# need to calculate the weights of shoots + rhizomes + epiphytes
df.bio <- df.bio %>% 
  mutate(epiphyte_mass_dw = pad_epiphyte_mass_g - pad_mass_g) %>%
  mutate(rhi_mass_dw = rhi_foil_dw_g - rhi_foil) %>%
  mutate(shoot_mass_dw = shoot_foil_dw - shoot_foil)

# delete derivitive weights not necessary for analysis
df.bio <- df.bio %>% 
  select(-pad_epiphyte_mass_g, -pad_mass_g) %>% #pads
  select(-rhi_foil_dw_g, -rhi_foil, -shoot_foil, -shoot_foil_dw) #seagrass
colnames(df.bio)


### Now we need to handle all the leaves. For expected analyses, leaf width/length/area might not matter but it will be interesting to look, anyway. 

## LEAF AREA, FIRST
# calculate the leaf area (cm^2) per blade per plant
df.bio <- df.bio %>% 
  mutate(leaf_area1 = leaf_length1 * leaf_width1, na.rm = TRUE) %>%
  mutate(leaf_area2 = leaf_length2 * leaf_width2, na.rm = TRUE) %>%
  mutate(leaf_area3 = leaf_length3 * leaf_width3, na.rm = TRUE) %>%
  mutate(leaf_area4 = leaf_length4 * leaf_width4, na.rm = TRUE) %>%
  mutate(leaf_area5 = leaf_length5 * leaf_width5, na.rm = TRUE) %>%
  mutate(leaf_area6 = leaf_length6 * leaf_width6, na.rm = TRUE) %>%
  mutate(leaf_area7 = leaf_length7 * leaf_width7, na.rm = TRUE) %>%
  mutate(leaf_area8 = leaf_length8 * leaf_width8, na.rm = TRUE) %>%
  mutate(leaf_area9 = leaf_length9 * leaf_width9, na.rm = TRUE) %>%
  mutate(leaf_area10 = leaf_length10 * leaf_width10, na.rm = TRUE)

# mean leaf area per blade
df.bio <- mutate(df.bio, mean_leaf_area_perblade = rowMeans(select(df.bio, starts_with("leaf_area")), na.rm = TRUE))

# calculate total leaf area per plant (there is no biomass data per blade so need to combine all blades)
#df.bio$tot_leaf_area <- rowSums(df.bio[,c("leaf_area1", "leaf_area2", "leaf_area3", "leaf_area4", "leaf_area5", "leaf_area6", "leaf_area7", "leaf_area8", "leaf_area9", "leaf_area10")], na.rm = TRUE)

# total leaf area per plant
df.bio <- mutate(df.bio, tot_leaf_area_perplant = rowSums(select(df.bio, starts_with("leaf_area")), na.rm = TRUE))

# after all of that, we no longer need areas for individual blades...
colnames(df.bio) # find which columns to delete in bulk
df.bio <- df.bio[, -c(35:45)] 



## LEAF LENGTH, SECOND
# mean leaf length per plant (or mean canopy height)
df.bio <- mutate(df.bio, mean_leaf_length_perplant = rowMeans(select(df.bio, starts_with("leaf_length")), na.rm = TRUE))

# max leaf length per plant
colnames(df.bio)
df.bio$max_leaf_length_perplant = apply(df.bio[, 12:21], 1, max, na.rm = TRUE) # ignore warning messages

# after all of that, we no longer need lengths for individual blades...
colnames(df.bio) # find which columns to delete in bulk
df.bio <- df.bio[, -c(12:21)] # delete columns



## LEAF WIDTH, THIRD
# mean leaf width per blade
df.bio <- mutate(df.bio, mean_leaf_width_perblade = rowMeans(select(df.bio, starts_with("leaf_width")), na.rm = TRUE))

# max leaf width per plant
df.bio$max_leaf_width_perplant = apply(df.bio[, 12:21], 1, max, na.rm = TRUE) # ignore warning messages

# after all of that, we no longer need lengths for individual blades...
colnames(df.bio) # find which columns to delete in bulk
df.bio <- df.bio[, -c(12:21)] # delete columns



# RHIZOMES and NODES, let's deal with those.
# mean node length per plant
df.bio <- mutate(df.bio, mean_node_length = rowMeans(select(df.bio, starts_with("node")), na.rm = TRUE))

# not all rhizomes were 5 cm, need to standardize Find rhizome mass per cm
df.bio <- df.bio %>% 
  mutate(rhi_mass_dw_percm = rhi_mass_dw / rhi_length, na.rm = TRUE)
df.bio <- within(df.bio, rm(na.rm))
str(df.bio)




# find total nodes per rhizome segment
nodes_only <- df.bio %>% 
  select(node1, node2, node3, node4, node5)

df.bio <- df.bio %>%
  mutate(tot_nodes = rowSums(nodes_only!=0, na.rm = TRUE)) %>%
  mutate(node1_dw = (node1 / rhi_length) * rhi_mass_dw, na.rm = TRUE) %>%
  mutate(node2_dw = (node2 / rhi_length) * rhi_mass_dw, na.rm = TRUE) %>%
  mutate(node3_dw = (node3 / rhi_length) * rhi_mass_dw, na.rm = TRUE) %>%
  mutate(node4_dw = (node4 / rhi_length) * rhi_mass_dw, na.rm = TRUE) %>%
  mutate(node5_dw = (node5 / rhi_length) * rhi_mass_dw, na.rm = TRUE) %>%
  select(-na.rm)
  
# rename node length variables for clarity
colnames(df.bio)[which(names(df.bio) == "node1")] <- "node1_length"
colnames(df.bio)[which(names(df.bio) == "node2")] <- "node2_length"
colnames(df.bio)[which(names(df.bio) == "node3")] <- "node3_length"
colnames(df.bio)[which(names(df.bio) == "node4")] <- "node4_length"
colnames(df.bio)[which(names(df.bio) == "node5")] <- "node5_length"
colnames(df.bio)

rm(nodes_only)



# there are some values that show up as non-numeric or zeros when they should be NA (consistent rows)...fixing those! 
df.bio[293:295,"mean_leaf_area_perblade"] = NA
df.bio[663,"mean_leaf_area_perblade"] = NA
df.bio[680,"mean_leaf_area_perblade"] = NA
df.bio[704:705,"mean_leaf_area_perblade"] = NA

df.bio[293:295,"tot_leaf_area_perplant"] = NA
df.bio[663,"tot_leaf_area_perplant"] = NA
df.bio[680,"tot_leaf_area_perplant"] = NA
df.bio[704:705,"tot_leaf_area_perplant"] = NA

df.bio[293:295,"mean_leaf_length_perplant"] = NA
df.bio[663,"mean_leaf_length_perplant"] = NA
df.bio[680,"mean_leaf_length_perplant"] = NA
df.bio[704:705,"mean_leaf_length_perplant"] = NA

df.bio[293:295,"max_leaf_length_perplant"] = NA
df.bio[663,"max_leaf_length_perplant"] = NA
df.bio[680,"max_leaf_length_perplant"] = NA
df.bio[704:705,"max_leaf_length_perplant"] = NA

df.bio[293:295,"mean_leaf_width_perblade"] = NA
df.bio[663,"mean_leaf_width_perblade"] = NA
df.bio[680,"mean_leaf_width_perblade"] = NA
df.bio[704:705,"mean_leaf_width_perblade"] = NA

df.bio[293:295,"max_leaf_width_perplant"] = NA
df.bio[663,"max_leaf_width_perplant"] = NA
df.bio[680,"max_leaf_width_perplant"] = NA
df.bio[704:705,"max_leaf_width_perplant"] = NA

df.bio[293:295,"mean_node_length"] = NA
df.bio[663,"mean_node_length"] = NA
df.bio[680,"mean_node_length"] = NA
df.bio[704:705,"mean_node_length"] = NA

df.bio[293:295,"tot_nodes"] = NA
df.bio[663,"tot_nodes"] = NA
df.bio[680,"tot_nodes"] = NA
df.bio[704:705,"tot_nodes"] = NA

# check the overall structure of df.bio
str(df.bio) 
```

All of the coding steps are included in the .Rmd file but not displayed here. However, here is the structure of each df, up to this point:
```{r}
str(df.sedpit)
str(df.trans)
str(df.bio)
```
<br><br><br><br>



### 2. Reshape DFs: prep each DF for site-level replication for analysis
<br>

#### df.sedpit ---> df.sedpit2 (only the code for this DF is displayed as an example)
```{r}
# calculate sum of all pits per site
pits_all <- df.sedpit %>% 
  select(site, date, pit_bin) # takes only the pit data from DF

m.pits_all <- melt(pits_all, id = 1:2, na.rm = TRUE) # prepares temporary DF for breakdown using dcast

trim_pits <- dcast(m.pits_all, site + date ~ ., sum) # sums all pits per site, trimming class info to just site and date
colnames(trim_pits)[which(names(trim_pits) == ".")] <- "pits_tot_site" # give data column appropriate name



# average all primary sediment values within each site
sed1_all <- df.sedpit %>% 
  select(site, date, sed1_no)

m.sed1_all <- melt(sed1_all, id = 1:2, na.rm = TRUE)

trim_sed1 <- dcast(m.sed1_all, site + date ~ ., mean)
colnames(trim_sed1)[which(names(trim_sed1) == ".")] <- "sed1_site"




# average all secondary sediment values per site
sed2_all <- df.sedpit %>% 
  select(site, date, sed2_no)

m.sed2_all <- melt(sed2_all, id = 1:2, na.rm = TRUE)

trim_sed2 <- dcast(m.sed2_all, site + date ~ ., mean)
colnames(trim_sed2)[which(names(trim_sed2) == ".")] <- "sed2_site"




# joining manipulated sub-DFs back together
df.sedpit2 <- left_join(trim_pits, trim_sed1, by = c("site", "date"))
df.sedpit2 <- left_join(df.sedpit2, trim_sed2, by = c("site", "date"))

# find the mean of the primary and secondary sediment types for later analysis
df.sedpit2$sedmean_site <- rowMeans(subset(df.sedpit2, select = c(sed1_site, sed2_site)), na.rm = TRUE)


# remove [now] extra dataframes to keep working space clean
rm(pits_all, m.pits_all, sed1_all, m.sed1_all, sed2_all, m.sed2_all, trim_pits, trim_sed1, trim_sed2)
```
<br>




#### df.sedpit ---> df.sedpit_trans (reshape df.sedpit in a slightly different way than above to keep transects seperated)
```{r, include = FALSE}
# calculate sum of all pits per transect, within each site
pits_trans <- df.sedpit %>% 
  select(site, date, trans_type, pit_bin) # takes only the pit data from DF, per transect

m.pits_trans <- melt(pits_trans, id = 1:3, na.rm = TRUE) # prepares temporary DF for breakdown using dcast

trim_pits_trans <- dcast(m.pits_trans, site + date + trans_type ~ ., sum) # sums all pits per site, trimming class info to just site and date
colnames(trim_pits_trans)[which(names(trim_pits_trans) == ".")] <- "pits_trans" # give data column appropriate name



# average all primary sediment values within each site
sed1_trans <- df.sedpit %>% 
  select(site, date, trans_type, sed1_no)

m.sed1_trans <- melt(sed1_trans, id = 1:3, na.rm = TRUE)

trim_sed1_trans <- dcast(m.sed1_trans, site + date + trans_type ~ ., mean)
colnames(trim_sed1_trans)[which(names(trim_sed1_trans) == ".")] <- "sed1_trans"




# average all secondary sediment values per site
sed2_trans <- df.sedpit %>% 
  select(site, date, trans_type, sed2_no)

m.sed2_trans <- melt(sed2_trans, id = 1:3, na.rm = TRUE)

trim_sed2_trans <- dcast(m.sed2_trans, site + date + trans_type ~ ., mean)
colnames(trim_sed2_trans)[which(names(trim_sed2_trans) == ".")] <- "sed2_trans"




# use dcast to expand the 'trans_type' column, so that each transect has it's own row for each variable (this is necessary for later looking at just the inside transect for biomass stuff)

# pits
c.pits_trans <- dcast(trim_pits_trans, site + date ~ trans_type) # dcast spread
colnames(c.pits_trans)[which(names(c.pits_trans) == "Edge")] <- "pits_edge" # apply unique names
colnames(c.pits_trans)[which(names(c.pits_trans) == "Inside")] <- "pits_in"
colnames(c.pits_trans)[which(names(c.pits_trans) == "Outside")] <- "pits_out"


# sed1
c.sed1_trans <- dcast(trim_sed1_trans, site + date ~ trans_type)
colnames(c.sed1_trans)[which(names(c.sed1_trans) == "Edge")] <- "sed1_edge"
colnames(c.sed1_trans)[which(names(c.sed1_trans) == "Inside")] <- "sed1_in"
colnames(c.sed1_trans)[which(names(c.sed1_trans) == "Outside")] <- "sed1_out"


# sed1
c.sed2_trans <- dcast(trim_sed2_trans, site + date ~ trans_type)
colnames(c.sed2_trans)[which(names(c.sed2_trans) == "Edge")] <- "sed2_edge"
colnames(c.sed2_trans)[which(names(c.sed2_trans) == "Inside")] <- "sed2_in"
colnames(c.sed2_trans)[which(names(c.sed2_trans) == "Outside")] <- "sed2_out"




# joining manipulated sub-DFs back together
df.sedpit_trans <- left_join(c.pits_trans, c.sed1_trans, by = c("site", "date"))
df.sedpit_trans <- left_join(df.sedpit_trans, c.sed2_trans, by = c("site", "date"))



# find the means of the primary and secondary sediments for later analysis
df.sedpit_trans$sedmean_edge <- rowMeans(subset(df.sedpit_trans, select = c(sed1_edge, sed2_edge)), na.rm = TRUE)
df.sedpit_trans$sedmean_in <- rowMeans(subset(df.sedpit_trans, select = c(sed1_in, sed2_in)), na.rm = TRUE)
df.sedpit_trans$sedmean_out <- rowMeans(subset(df.sedpit_trans, select = c(sed1_out, sed2_out)), na.rm = TRUE)


# remove [now] extra dataframes to keep working space clean
rm(pits_trans, m.pits_trans, sed1_trans, m.sed1_trans, sed2_trans, m.sed2_trans, trim_pits_trans, trim_sed1_trans, trim_sed2_trans, c.pits_trans, c.sed1_trans, c.sed2_trans)
```

```{r}
colnames(df.sedpit_trans)
# final column names for this DF
```
<br>



#### df.transect --> df.transect2 (theory + code similar to df.sedpit process)
```{r, include=FALSE}
str(df.trans)

# calculate mean macroalgae (% cover) per site
macroalgae <- df.trans %>% 
  select(site, date, depth_m, algae_cover_m2)

m.macroalgae <- melt(macroalgae, id = 1:3, na.rm = TRUE)

trim_macroalgae <- dcast(m.macroalgae, site + date + depth_m ~ ., mean)
colnames(trim_macroalgae)[which(names(trim_macroalgae) == ".")] <- "macroalgae_percent_cover"




# calculate mean epiphyte (% cover) per site
epiphyte <- df.trans %>% 
  select(site, date, depth_m, epiphyte_cover_m2)

m.epiphyte <- melt(epiphyte, id = 1:3, na.rm = TRUE)

trim_epiphyte <- dcast(m.epiphyte, site + date + depth_m ~ ., mean)
colnames(trim_epiphyte)[which(names(trim_epiphyte) == ".")] <- "epiphyte_percent_cover"




# calculate mean shoots (per m^2) per site
shoot_count <- df.trans %>% 
  select(site, date, depth_m, seagrass_count_m2)

m.shoot_count <- melt(shoot_count, id = 1:3, na.rm = TRUE)

trim_shoot_count <- dcast(m.shoot_count, site + date + depth_m ~ ., mean)
colnames(trim_shoot_count)[which(names(trim_shoot_count) == ".")] <- "shoot_density_m2"




# calculate mean shoots (per m^2) per site
flower_count <- df.trans %>% 
  select(site, date, depth_m, flower_count_m2)

m.flower_count <- melt(flower_count, id = 1:3, na.rm = TRUE)

trim_flower_count <- dcast(m.flower_count, site + date + depth_m ~ ., mean)
colnames(trim_flower_count)[which(names(trim_flower_count) == ".")] <- "flower_density_m2"





# MERGING back together
df.trans2 <- left_join(trim_macroalgae, trim_epiphyte, by = c("site", "date", "depth_m"))
df.trans2 <- left_join(df.trans2, trim_shoot_count, by = c("site", "date", "depth_m"))
df.trans2 <- left_join(df.trans2, trim_flower_count, by = c("site", "date", "depth_m"))


# remove extra DFs to keep working space clean
rm(macroalgae, m.macroalgae, epiphyte, m.epiphyte, shoot_count, m.shoot_count, flower_count, m.flower_count, trim_epiphyte, trim_macroalgae, trim_flower_count, trim_shoot_count)
```

```{r}
colnames(df.trans2)
# final column names for this DF
```
<br>



#### df.bio --> df.bio2 (theory + code similar to df.sedpit process)
```{r, include = FALSE}
colnames(df.bio)

########## there are a lot of variables...let's do this by tissue type. 

# leaves + epiphytes first
epiphyte_mass <- df.bio %>% 
  select(site, date, epiphyte_mass_dw)

m.epiphyte_mass <- melt(epiphyte_mass, id = 1:2, na.rm = TRUE)

trim_epiphyte_mass <- dcast(m.epiphyte_mass, site + date ~ ., mean)
colnames(trim_epiphyte_mass)[which(names(trim_epiphyte_mass) == ".")] <- "epiphyte_mass"




shoot_mass <- df.bio %>% 
  select(site, date, shoot_mass_dw)

m.shoot_mass <- melt(shoot_mass, id = 1:2, na.rm = TRUE)

trim_shoot_mass <- dcast(m.shoot_mass, site + date ~ ., mean)
colnames(trim_shoot_mass)[which(names(trim_shoot_mass) == ".")] <- "shoot_mass_mean"




leaf_area_blade <- df.bio %>% 
  select(site, date, mean_leaf_area_perblade)

m.leaf_area_blade <- melt(leaf_area_blade, id = 1:2, na.rm = TRUE)

trim_leaf_area_blade <- dcast(m.leaf_area_blade, site + date ~ ., mean)
colnames(trim_leaf_area_blade)[which(names(trim_leaf_area_blade) == ".")] <- "leaf_area_blade"




leaf_area_plant <- df.bio %>% 
  select(site, date, tot_leaf_area_perplant)

m.leaf_area_plant <- melt(leaf_area_plant, id = 1:2, na.rm = TRUE)

trim_leaf_area_plant <- dcast(m.leaf_area_plant, site + date ~ ., mean)
colnames(trim_leaf_area_plant)[which(names(trim_leaf_area_plant) == ".")] <- "leaf_area_plant"




leaf_length_mean <- df.bio %>% 
  select(site, date, mean_leaf_length_perplant)

m.leaf_length_mean <- melt(leaf_length_mean, id = 1:2, na.rm = TRUE)

trim_leaf_length_mean <- dcast(m.leaf_length_mean, site + date ~ ., mean)
colnames(trim_leaf_length_mean)[which(names(trim_leaf_length_mean) == ".")] <- "leaf_length_mean"




leaf_length_max <- df.bio %>% 
  select(site, date, max_leaf_length_perplant)

m.leaf_length_max <- melt(leaf_length_max, id = 1:2, na.rm = TRUE)

trim_leaf_length_max <- dcast(m.leaf_length_max, site + date ~ ., mean)
colnames(trim_leaf_length_max)[which(names(trim_leaf_length_max) == ".")] <- "leaf_length_max"




leaf_width_mean <- df.bio %>% 
  select(site, date, mean_leaf_width_perblade)

m.leaf_width_mean <- melt(leaf_width_mean, id = 1:2, na.rm = TRUE)

trim_leaf_width_mean <- dcast(m.leaf_width_mean, site + date ~ ., mean)
colnames(trim_leaf_width_mean)[which(names(trim_leaf_width_mean) == ".")] <- "leaf_width_mean"




leaf_width_max <- df.bio %>% 
  select(site, date, max_leaf_width_perplant)

m.leaf_width_max <- melt(leaf_width_max, id = 1:2, na.rm = TRUE)

trim_leaf_width_max <- dcast(m.leaf_width_max, site + date ~ ., mean)
colnames(trim_leaf_width_max)[which(names(trim_leaf_width_max) == ".")] <- "leaf_width_max"





# MERGING back together
df.bio2 <- left_join(trim_epiphyte_mass, trim_shoot_mass, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_area_blade, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_area_plant, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_length_max, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_length_mean, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_width_max, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_leaf_width_mean, by = c("site", "date"))


# remove extra DFs to keep working space clean
rm(epiphyte_mass, m.epiphyte_mass, trim_epiphyte_mass, leaf_area_blade, leaf_area_plant, leaf_length_max, leaf_length_mean, leaf_width_max, leaf_width_mean, m.leaf_area_blade, m.leaf_area_plant, m.leaf_length_max, m.leaf_length_mean, m.leaf_width_max, m.leaf_width_mean, trim_leaf_area_blade, trim_leaf_area_plant, trim_leaf_length_max, trim_leaf_length_mean, trim_leaf_width_max, trim_leaf_width_mean, shoot_mass, m.shoot_mass, trim_shoot_mass)


# check DF
str(df.bio2)
```

```{r, include=FALSE}
colnames(df.bio)


rhi_length <- df.bio %>% 
  select(site, date, rhi_length)

m.rhi_length <- melt(rhi_length, id = 1:2, na.rm = TRUE)

trim_rhi_length <- dcast(m.rhi_length, site + date ~ ., mean)
colnames(trim_rhi_length)[which(names(trim_rhi_length) == ".")] <- "rhi_length"




rhi_mass_tot <- df.bio %>% 
  select(site, date, rhi_mass_dw)

m.rhi_mass_tot <- melt(rhi_mass_tot, id = 1:2, na.rm = TRUE)

trim_rhi_mass_tot <- dcast(m.rhi_mass_tot, site + date ~ ., mean)
colnames(trim_rhi_mass_tot)[which(names(trim_rhi_mass_tot) == ".")] <- "rhi_mass_tot"





rhi_mass_percm <- df.bio %>% 
  select(site, date, rhi_mass_dw_percm)

m.rhi_mass_percm <- melt(rhi_mass_percm, id = 1:2, na.rm = TRUE)

trim_rhi_mass_percm <- dcast(m.rhi_mass_percm, site + date ~ ., mean)
colnames(trim_rhi_mass_percm)[which(names(trim_rhi_mass_percm) == ".")] <- "rhi_mass_percm"






node1_length <- df.bio %>% 
  select(site, date, node1_length)

m.node1_length <- melt(node1_length, id = 1:2, na.rm = TRUE)

trim_node1_length <- dcast(m.node1_length, site + date ~ ., mean)
colnames(trim_node1_length)[which(names(trim_node1_length) == ".")] <- "node1_length"




node2_length <- df.bio %>% 
  select(site, date, node2_length)

m.node2_length <- melt(node2_length, id = 1:2, na.rm = TRUE)

trim_node2_length <- dcast(m.node2_length, site + date ~ ., mean)
colnames(trim_node2_length)[which(names(trim_node2_length) == ".")] <- "node2_length"




node3_length <- df.bio %>% 
  select(site, date, node3_length)

m.node3_length <- melt(node3_length, id = 1:2, na.rm = TRUE)

trim_node3_length <- dcast(m.node3_length, site + date ~ ., mean)
colnames(trim_node3_length)[which(names(trim_node3_length) == ".")] <- "node3_length"




node4_length <- df.bio %>% 
  select(site, date, node4_length)

m.node4_length <- melt(node4_length, id = 1:2, na.rm = TRUE)

trim_node4_length <- dcast(m.node4_length, site + date ~ ., mean)
colnames(trim_node4_length)[which(names(trim_node4_length) == ".")] <- "node4_length"




node5_length <- df.bio %>% 
  select(site, date, node5_length)

m.node5_length <- melt(node5_length, id = 1:2, na.rm = TRUE)

trim_node5_length <- dcast(m.node5_length, site + date ~ ., mean)
colnames(trim_node5_length)[which(names(trim_node5_length) == ".")] <- "node5_length"




node1_dw <- df.bio %>% 
  select(site, date, node1_dw)

m.node1_dw <- melt(node1_dw, id = 1:2, na.rm = TRUE)

trim_node1_dw <- dcast(m.node1_dw, site + date ~ ., mean)
colnames(trim_node1_dw)[which(names(trim_node1_dw) == ".")] <- "node1_dw"




node2_dw <- df.bio %>% 
  select(site, date, node2_dw)

m.node2_dw <- melt(node2_dw, id = 1:2, na.rm = TRUE)

trim_node2_dw <- dcast(m.node2_dw, site + date ~ ., mean)
colnames(trim_node2_dw)[which(names(trim_node2_dw) == ".")] <- "node2_dw"




node3_dw <- df.bio %>% 
  select(site, date, node3_dw)

m.node3_dw <- melt(node3_dw, id = 1:2, na.rm = TRUE)

trim_node3_dw <- dcast(m.node3_dw, site + date ~ ., mean)
colnames(trim_node3_dw)[which(names(trim_node3_dw) == ".")] <- "node3_dw"




node4_dw <- df.bio %>% 
  select(site, date, node4_dw)

m.node4_dw <- melt(node4_dw, id = 1:2, na.rm = TRUE)

trim_node4_dw <- dcast(m.node4_dw, site + date ~ ., mean)
colnames(trim_node4_dw)[which(names(trim_node4_dw) == ".")] <- "node4_dw"




node5_dw <- df.bio %>% 
  select(site, date, node5_dw)

m.node5_dw <- melt(node5_dw, id = 1:2, na.rm = TRUE)

trim_node5_dw <- dcast(m.node5_dw, site + date ~ ., mean)
colnames(trim_node5_dw)[which(names(trim_node5_dw) == ".")] <- "node5_dw"








# MERGING back together
df.bio2 <- left_join(df.bio2, trim_rhi_length, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_rhi_mass_tot, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_rhi_mass_percm, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node1_dw, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node2_dw, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node3_dw, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node4_dw, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node5_dw, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node1_length, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node2_length, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node3_length, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node4_length, by = c("site", "date"))
df.bio2 <- left_join(df.bio2, trim_node5_length, by = c("site", "date"))



# remove extra DFs to keep working space clean
rm(rhi_length, rhi_mass_tot, rhi_mass_percm, node1_length, node2_length, node3_length, node4_length, node5_length, node1_dw, node2_dw, node3_dw, node4_dw, node5_dw, m.rhi_length, m.rhi_mass_tot, m.rhi_mass_percm, m.node1_length, m.node2_length, m.node3_length, m.node4_length, m.node5_length, m.node1_dw, m.node2_dw, m.node3_dw, m.node4_dw, m.node5_dw, trim_rhi_length, trim_rhi_mass_tot, trim_rhi_mass_percm, trim_node1_length, trim_node1_dw, trim_node2_length, trim_node2_dw, trim_node3_length, trim_node3_dw, trim_node4_length, trim_node4_dw, trim_node5_length, trim_node5_dw)


# check DF
str(df.bio2)
```

```{r}
colnames(df.bio2)
# final column names for this DF
```
<br><br>



#### Before we join all the DFs together, biomass per area still needs to be added. This was handled differently than the rest because of the order of operations for calculations were different. 

#### scratch --> df.mass_area
```{r, include = FALSE}

# extract shoot biomass and reshape to quadrat for working with count data
shoot_mass_perp <- df.bio %>% 
  select(site, date, quadrat, shoot_mass_dw)

m.shoot_mass_perp <- melt(shoot_mass_perp, id = 1:3, na.rm = TRUE)

trim_shoot_mass_perp <- dcast(m.shoot_mass_perp, site + date + quadrat ~ ., mean)
colnames(trim_shoot_mass_perp)[which(names(trim_shoot_mass_perp) == ".")] <- "shoot_mass_perp"



# extract rhizome biomass and reshape to quadrat for working with count data
rhizome_mass_percm_perp <- df.bio %>% 
  select(site, date, quadrat, rhi_mass_dw_percm)

m.rhizome_mass_percm_perp <- melt(rhizome_mass_percm_perp, id = 1:3, na.rm = TRUE)

trim_rhizome_mass_percm_perp <- dcast(m.rhizome_mass_percm_perp, site + date + quadrat ~ ., mean)
colnames(trim_rhizome_mass_percm_perp)[which(names(trim_rhizome_mass_percm_perp) == ".")] <- "rhizome_mass_percm_perp"



# gather shoot count data
shoot_count_perm <- df.trans %>% 
  select(site, date, quadrat, seagrass_count_m2)



# join shoot and rhizome masses + shoot counts
mass.temp <- left_join(trim_rhizome_mass_percm_perp, trim_shoot_mass_perp, by = c("site", "date", "quadrat"))
mass.temp <- left_join(mass.temp, shoot_count_perm, by = c("site", "quadrat"))

mass.temp <- within(mass.temp, rm(date.y))
colnames(mass.temp)[which(names(mass.temp) == "date.x")] <- "date"

# remove extra DFs to keep working space clean
rm(shoot_mass_perp, m.shoot_mass_perp, trim_shoot_mass_perp, rhizome_mass_percm_perp, m.rhizome_mass_percm_perp, trim_rhizome_mass_percm_perp, shoot_count_perm)





# calculate the masses per area per quadrat! 
mass.temp <- mass.temp %>%
  mutate(shoot_mass_m2 = shoot_mass_perp * seagrass_count_m2, na.rm = TRUE) %>%
  mutate(rhi_mass_percm_m2 = rhizome_mass_percm_perp * seagrass_count_m2, na.rm = TRUE)




# extract rhizome biomass and reshape to quadrat for working with count data
shoot_mass_m2 <- mass.temp %>% 
  select(site, date, quadrat, shoot_mass_m2)

m.shoot_mass_m2 <- melt(shoot_mass_m2, id = 1:3, na.rm = TRUE)

trim_shoot_mass_m2 <- dcast(m.shoot_mass_m2, site + date ~ ., mean)
colnames(trim_shoot_mass_m2)[which(names(trim_shoot_mass_m2) == ".")] <- "shoot_mass_m2"



rhi_mass_percm_m2 <- mass.temp %>% 
  select(site, date, quadrat, rhi_mass_percm_m2)

m.rhi_mass_percm_m2 <- melt(rhi_mass_percm_m2, id = 1:3, na.rm = TRUE)

trim_rhi_mass_percm_m2 <- dcast(m.rhi_mass_percm_m2, site + date ~ ., mean)
colnames(trim_rhi_mass_percm_m2)[which(names(trim_rhi_mass_percm_m2) == ".")] <- "rhi_mass_percm_m2"

rm(shoot_mass_m2, m.shoot_mass_m2, rhi_mass_percm_m2, m.rhi_mass_percm_m2)



# join shoot and rhizome masses + shoot counts
colnames(mass.temp)

df.mass_area <- left_join(trim_rhi_mass_percm_m2, trim_shoot_mass_m2, by = c("site", "date"))

rm(trim_rhi_mass_percm_m2, trim_shoot_mass_m2, mass.temp)
```

```{r}
colnames(df.mass_area)
# final column names for this DF
```
<br><br><br><br>






### 3. Join all DFs together
<br>

OK. From the previous reshaping, we have 6 DFs (df.coords, df.trans2, df.sedpit2, df.sedpit_trans, df.bio2, df.mass_area) that we want to join into one big DF. This results in 49 columns of unique variables/info (!)...that's a lot but we aren't concerned about ALL of them...they are just there for exploration, afterall. 

```{r}
df.all <- left_join(df.coords, df.trans2, by = c("site"))
df.all <- left_join(df.all, df.sedpit2, by = c("site"))
df.all <- left_join(df.all, df.sedpit_trans, by = c("site"))
df.all <- left_join(df.all, df.bio2, by = c("site"))
df.all <- left_join(df.all, df.mass_area, by = c("site"))
```

```{r, include = FALSE}
# get rid of extra date columns
df.all <- within(df.all, rm(date.y))
df.all <- within(df.all, rm(date.x.x))
df.all <- within(df.all, rm(date.y.y))
df.all <- within(df.all, rm(date))
colnames(df.all)[which(names(df.all) == "date.x")] <- "date"
```
<br>

#### Check out the final structure of the DF
```{r}
str(df.all)
```
<br><br><br><br>








### 4. Large-scale pattern in sediment type
These maps represent the numeric ordinal data, where the circle size scales with the numeric classification (larger circle = larger numeric).
<br>

Classifications: (1) mud, (2) muddy sand, (3) sandy mud, (4) sand, (5) coarse sand, (6) pebble, (7) gravel, (8) cobble, (9) boulder, (10) reef
<br>



#### First set of maps compare primary, secondary, and their mean for the entire site (transects averaged). 
##### RED -- primary sediment; ORANGE -- secondary sediment; YELLOW -- mean of primary and secondary
```{r, echo = FALSE}
map1 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sed1_site) * 2,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'Red',
    label = as.character(df.all$sed1_site)
  )


map2 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sed2_site) * 2,
    stroke = FALSE, fillOpacity = 0.6, 
    color = ~'Orange',
    label = as.character(df.all$sed2_site)
  )


map3 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sedmean_site) * 2,
    stroke = FALSE, fillOpacity = 0.7, 
    color = ~'Gold',
    label = as.character(df.all$sedmean_site)
  )



tagList(
  tags$head(tags$script(
    type="text/javascript",
    src="https://cdn.rawgit.com/turban/Leaflet.Sync/master/L.Map.Sync.js"
  )),
  tags$div(style="display:inline;width:33%;float:left;",map1),
  tags$div(style="display:inline;width:33%;float:left;",map2),
  tags$div(style="display:inline;width:33%;float:left;",map3),
  onStaticRenderComplete(
'
var leaf_widgets = Array.prototype.map.call(
  document.querySelectorAll(".leaflet"),
  function(ldiv){
    return HTMLWidgets.find("#" + ldiv.id);
  }
);

// make this easy since we know only two maps
leaf_widgets[0].sync(leaf_widgets[1]);
leaf_widgets[1].sync(leaf_widgets[0]);
'
  )
) %>%
  browsable
```

<br><br><br><br>

#### Second set of maps compare inside, edge, and outside sediments, across sites (mean primary and secondary).
##### GREEN -- inside transect; BLUE -- edge transect; PURPLE -- outside transect
```{r, echo = FALSE}
map4 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sedmean_in) * 2,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'Green',
    label = as.character(df.all$sedmean_in)
  )


map5 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sedmean_edge) * 2,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'Blue',
    label = as.character(df.all$sedmean_edge)
  )


map6 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~(sedmean_out) * 2,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'Purple',
    label = as.character(df.all$sedmean_out)
  )



tagList(
  tags$head(tags$script(
    type="text/javascript",
    src="https://cdn.rawgit.com/turban/Leaflet.Sync/master/L.Map.Sync.js"
  )),
  tags$div(style="display:inline;width:33%;float:left;",map4),
  tags$div(style="display:inline;width:33%;float:left;",map5),
  tags$div(style="display:inline;width:33%;float:left;",map6),
  onStaticRenderComplete(
'
var leaf_widgets = Array.prototype.map.call(
  document.querySelectorAll(".leaflet"),
  function(ldiv){
    return HTMLWidgets.find("#" + ldiv.id);
  }
);

// make this easy since we know only two maps
leaf_widgets[0].sync(leaf_widgets[1]);
leaf_widgets[1].sync(leaf_widgets[0]);
'
  )
) %>%
  browsable
```


<br><br><br><br><br>

#### Third set of maps compare #pits dug at inside, edge, and outside transects (larger circle = more pits).
##### BLACK -- inside transect; D.RED -- edge transect; D.BLUE -- outside transect
```{r, echo = FALSE}
map7 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~log(pits_in) * 3,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'Black',
    label = as.character(df.all$pits_in)
  )


map8 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~log(pits_edge) * 3,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'DarkRed',
    label = as.character(df.all$pits_edge)
  )


map9 <- leaflet(df.all) %>% addTiles() %>% 
  addCircleMarkers(
    lng = ~longitude, lat =  ~latitude,
    radius = ~log(pits_out) * 3,
    stroke = FALSE, fillOpacity = 0.5, 
    color = ~'DarkBlue',
    label = as.character(df.all$pits_out)
  )



tagList(
  tags$head(tags$script(
    type="text/javascript",
    src="https://cdn.rawgit.com/turban/Leaflet.Sync/master/L.Map.Sync.js"
  )),
  tags$div(style="display:inline;width:33%;float:left;",map7),
  tags$div(style="display:inline;width:33%;float:left;",map8),
  tags$div(style="display:inline;width:33%;float:left;",map9),
  onStaticRenderComplete(
'
var leaf_widgets = Array.prototype.map.call(
  document.querySelectorAll(".leaflet"),
  function(ldiv){
    return HTMLWidgets.find("#" + ldiv.id);
  }
);

// make this easy since we know only two maps
leaf_widgets[0].sync(leaf_widgets[1]);
leaf_widgets[1].sync(leaf_widgets[0]);
'
  )
) %>%
  browsable
```
<br><br>

#### OK! Mapping patterns is fun, but anything else is overkill. 

<br><br><br><br>


### 5. Exploratory analysis

<br><br>

#### 5A. Sediment x seagrass
<br><br>

```{r}
colnames(df.all)

my.formula <- y ~ x
p1 = ggplot(df.all, aes(sedmean_site, shoot_mass_m2)) +
  geom_point(size=4)+
  geom_smooth(method=lm, formula=y~x, se=FALSE, fullrange=FALSE)+
  stat_poly_eq(formula = my.formula, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    stat_fit_glance(method = 'lm',
                  method.args = list(formula = my.formula),
                  geom = 'text',
                  aes(label = paste("P-value = ", signif(..p.value.., digits = 4), sep = "")),
                  label.x.npc = 'right', label.y.npc = 0.35, size = 3)
plot(p1)




m1 <- lm(shoot_mass_m2~sed1_in, data = df.all)  #Create a linear model
resid(m1) #List of residuals
plot(density(resid(m1))) #A density plot
qqnorm(resid(m1)) # A quantile normal plot - good for checking normality
qqline(resid(m1))
```


