---
title: "Stable Isotopes - Seasonality (short version)"
author: "Nicole LaRoche"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
I am working on sea otter whisker analysis over time from the root to the tip of the whisker.  This includes 29 sea otters as a population between Klawock and Naukati on Prince of Wales Island. Sea otter whiskers were collected from June 26- August 6, 2019. We are looking at seasonality (so I gave each whisker segment a season association), and if there are diet shifts from season to season. A diet shift can be a change in nitrogen (d15N) or carbon (d13C), but generally are considered to be greater than 1‰. 

# Analysis

First, loading programs and files. Otter ID (a numeric, treated as a name in this case) should be read as a factor.

```{r, libraries and data, message= FALSE}
library(ggplot2)
library(dplyr)
library(ggthemes)
library(scales)
library(MASS)

#load whisker data
whisker <- read.csv("whiskers.csv")
whisker$OtterID<-as.character(whisker$OtterID)
```


#### Data Cleaning - Temp until final decision is made for the odd otter

Otter 163532 has very odd values, while it is being re-run I have seperated out the values and am going to make the whisker file without this sea otter. I also want the seasons to print in date order, as opposed to alphabetical order

```{r, data cleaning}
whisker<- filter(whisker, OtterID != "163532")

whisker$Season<-factor(whisker$Season , levels=c("Spring", "Summer", "Fall", "Winter"))
```


## Results - Seasons

#### Carbon

```{r, boxplot Carbon seasons, echo=FALSE, message=FALSE}
ggplot(data=whisker) +
  geom_boxplot(aes(x=Season, y=C)) +
  labs(y=expression(paste(delta^13, "C" ))) +
  theme_few()
```

#### Nitrogen

```{r, boxplot Nitrogen seasons, echo=FALSE, message=FALSE}
ggplot(data=whisker) +
  geom_boxplot(aes(x=Season, y=N)) +
  labs(y=expression(paste(delta^15, "N" ))) +
  theme_few()
```

Looks like there is very little variation from season to season, with the biggest mean value shifts at about 0.5‰. 


## Stats for Seasons

#### Anova 
```{r, anova seasons, message=FALSE}
cseason.aov <- aov(C~Season*OtterID, data = whisker)
summary(cseason.aov)

nseason.aov <- aov(N~Season*OtterID, data = whisker)
summary(nseason.aov)
```

Season for both C and N are significant. But you can also see that there is an interaction with Otter ID. Which is where my problem starts.

#### Pairwise test for seasons 
```{r, pairwise seasons, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="none")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="none")
```


Carbon: Spring/Fall, Spring/Summer, Winter/Fall, and Winter/Summer are significant. This doesn't match with how I originally matched the seasons (combining spring and summer, and then fall and winter). 

Nitrogen: Spring/Fall, Spring/Winter, Summer/Fall, and Winter/Summer are significant, which is how I originally matched up the seasons. 


```{r, pairwise bonferroni seasons, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="bonferroni")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="bonferroni")
```

Using bonferrroni, Spring/Fall are significant for carbon, but nothing else. And all the same Nitrogen seasons remain the same as above.


```{r, pairwise holm, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="holm")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="holm")
```

This method is generally considered superior to the Bonferroni adjustment, and adds Winter/Fall as stat sig for Carbon.


#### Tukey HSD
```{r, tukey, message=FALSE}
TukeyHSD(aov(C~Season, data=whisker))
TukeyHSD(aov(N~Season, data=whisker))
```

Tukey's gives similar as Bonferroni and Holm. There are significant values here, but really - the main takeaway needs to be that these means are only 0.3-0.5‰. which is VERY SMALL in and ecological sense. 


## Normality

I didn't initially test for normality in either Carbon or Nitrogen values

```{r, normality}
plot(density(whisker$C));plot(density(whisker$N))

shapiro.test(whisker$C); shapiro.test(whisker$N)
qqnorm(whisker$C); qqnorm(whisker$N)
```

```{r, residuals}
lm<- aov(data= whisker, C~Season)
lm.sum <- summary.lm(lm)
lm.sum
e <- residuals(lm)
h <- hatvalues(lm)
r <- e/(lm.sum$sigma*sqrt(1-h))
yHat <- fitted.values(lm)
```

```{r, graphs residuals}
with(data = whisker, expr = stripchart(abs(r) ~ Season,
    ylab = expression(abs(hat(" "*r*" " ))), xlab = "season",
    method = "jitter", pch = 1, vertical = TRUE))
qqnorm(r); abline(a=0, b=1, lty = 2)
plot(abs(r) ~ yHat, ylab = expression(abs(hat(" "*r*" " ))),
    xlab = "Fitted Values")
abline(a = 0, b = 0.055, lty = 2)

shapiro.test(r)

```
```{r, lme}

```

