---
title: "Stable Isotopes - Time"
author: "Nicole LaRoche"
date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
I am working on sea otter whisker analysis over time from the root to the tip of the whisker. As my analysis is not complete, this is includes 27 sea otters as a population between Klawock and Naukati on Prince of Wales Island. Sea otter whiskers were collected from June 26- August 6, 2019. 

# Analysis

First, I want to load the correct programs and files. I am loading ggplot to print some nice graphs, and load the stable isotope whisker data. Otter ID should be read as a factor.

```{r, message= FALSE}
library(ggplot2)
library(dplyr)
library(ggthemes)

#load whisker data
whisker <- read.csv("whiskers.csv")
whisker$OtterID<-as.character(whisker$OtterID)

```

#### Data Cleaning

Otter 163532 has very odd values, while it is being re-run I have seperated out the values and am going to make the whisker file without this sea otter.
```{r}

# for right now, I want to separate 163532 because it is an odd otter
oddotter<- filter(whisker, OtterID=="163532")
whisker<- filter(whisker, OtterID != "163532")
```


# Results 
Here is each individual sea otter from the root to the tip for Carbon in Teal and Nitrogen in Red. 

```{r, echo= FALSE}
ggplot(data=whisker) +
  geom_line(aes(x=distance, y=N), colour="tomato") +
  geom_line(aes(x=distance, y=C+25), colour="lightseagreen") +
  labs(x= "Distance from root (cm)", 
       y=expression(paste(delta^15, "N (\u2030)" )), 
       colour = "Isotope")  +
  scale_y_continuous(sec.axis = sec_axis(~.-25, 
       name = expression(paste(delta^13, "C (\u2030)" )))) +
  facet_wrap(vars(OtterID), nrow=5) +
  theme_light()
```

##### Odd otter graph - for reference
I want to make a new column that has which run the values were a part of. 
```{r, echo= FALSE}

ggplot(data=oddotter) + theme_classic() +
  geom_line(aes(x=SIN, y=N), colour="tomato") +
  geom_line(aes(x=SIN, y=C+25), colour="lightseagreen") +
  labs(x= "Distance from root (cm)", 
       y=expression(paste(delta^15, "N (\u2030)" )), 
       colour = "Isotope")  +
  scale_y_continuous(sec.axis = sec_axis(~.-25, 
       name = expression(paste(delta^13, "C (\u2030)" ))))

```

