---
title: "Stable Isotopes - Time and Seasonality"
author: "Nicole LaRoche"
date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
I am working on sea otter whisker analysis over time from the root to the tip of the whisker. As my analysis is not complete, this is includes 29 sea otters as a population between Klawock and Naukati on Prince of Wales Island. Sea otter whiskers were collected from June 26- August 6, 2019. 

# Analysis

First, loading programs and files. Otter ID should be read as a factor.

```{r, libraries and data, message= FALSE}
library(ggplot2)
library(dplyr)
library(ggthemes)

#load whisker data
whisker <- read.csv("whiskers.csv")
whisker$OtterID<-as.character(whisker$OtterID)
oddotter <- read.csv("oddotter.csv")
oddotter$OtterID<-as.factor(oddotter$OtterID)
oddotter$Run<-as.factor(oddotter$Run)



#load prey data
si.prey <- read.csv("sifinal.csv")
```


#### Data Cleaning - Temp until final decision is made for the odd otter

Otter 163532 has very odd values, while it is being re-run I have seperated out the values and am going to make the whisker file without this sea otter.

```{r, data cleaning}
whisker<- filter(whisker, OtterID != "163532")
```


## Results 

Here is each individual sea otter from the root to the tip for Carbon in Teal and Nitrogen in Red. 

```{r, graph indiv otters, echo= FALSE}
ggplot(data=whisker) +
  geom_line(aes(x=distance, y=N), colour="tomato") +
  geom_line(aes(x=distance, y=C+25), colour="lightseagreen") +
  labs(x= "Distance from root (cm)", 
       y=expression(paste(delta^15, "N (\u2030)" )), 
       colour = "Isotope")  +
  scale_y_continuous(sec.axis = sec_axis(~.-25, 
       name = expression(paste(delta^13, "C (\u2030)" )))) +
  facet_wrap(vars(OtterID), nrow=5) +
  theme_light()
```


### Odd otter graphs - for reference


#### Carbon

```{r, odd otter carbon, echo= FALSE}
ggplot(data=oddotter, aes(x=distance, y=C, colour=Run)) +
  geom_line() +
  geom_point() +
  labs(x= "Distance from root (cm)", 
       y=expression(paste(delta^13, "C (\u2030)" )))  +
  theme_few()

```

#### Nitrogen

```{r, odd otter nitrogen, echo=FALSE}
ggplot(data=oddotter, aes(x=distance, y=N, colour=Run)) +
  geom_line() +
  geom_point() +
  labs(x= "Distance from root (cm)", 
       y=expression(paste(delta^15, "N (\u2030)" )))  +
  theme_few()
```


## Seasons

#### Carbon

```{r, overlay carbon graph by season, echo=FALSE, message=FALSE}
ggplot() +   
  theme_few() +
  geom_density(data=filter(whisker, Season == "Summer"), 
                 aes(x=C), alpha=.5, fill= "darkgoldenrod1") +
  geom_density(data=filter(whisker, Season == "Spring"), 
                 aes(x=C), alpha=.5, fill= "palegreen3") +
  geom_density(data=filter(whisker, Season == "Fall"), 
                 aes(x=C), alpha=.5, fill= "darkorange3") +
  geom_density(data=filter(whisker, Season == "Winter"), 
                 aes(x=C), alpha=.5, fill = "paleturquoise1") +
  labs(x=expression(paste(delta^13, "C" )), y="Kernel Density") 

```


#### Nitrogen

```{r, overlay nitrogen graph by season, echo=FALSE, message=FALSE}
ggplot() +   
  theme_few() +
  geom_density(data=filter(whisker, Season == "Summer"), 
               aes(x=N), alpha=.9, fill= "darkgoldenrod1") +
  geom_density(data=filter(whisker, Season == "Spring"), 
               aes(x=N), alpha=.6, fill= "palegreen3") +
  geom_density(data=filter(whisker, Season == "Fall"), 
               aes(x=N), alpha=.5, fill= "darkorange3") +
  geom_density(data=filter(whisker, Season == "Winter"), 
               aes(x=N), alpha=.4, fill = "paleturquoise1") +
  labs(x=expression(paste(delta^15, "N" )), y="Kernel Density") 
```



The graphs above are ok, but too messy for a paper, and the kernel density is not what I want to talk about, so here are some boxplots of the same data. 

#### Carbon

```{r, boxplot Carbon seasons, echo=FALSE, message=FALSE}
ggplot(data=whisker) +
  geom_boxplot(aes(x=Season, y=C)) +
  labs(y=expression(paste(delta^13, "C" ))) +
  theme_few()
```

#### Nitrogen

```{r, boxplot Nitrogen seasons, echo=FALSE, message=FALSE}
ggplot(data=whisker) +
  geom_boxplot(aes(x=Season, y=N)) +
  labs(y=expression(paste(delta^15, "N" ))) +
  theme_few()
```


## Stats for Seasons

#### Anova 
```{r, anova seasons, message=FALSE}
cseason.aov <- aov(C~Season, data = whisker)
summary(cseason.aov)

nseason.aov <- aov(N~Season, data = whisker)
summary(nseason.aov)
```

Season for both C and N are significant. 

#### Pairwise test for seasons 
```{r, pairwise seasons, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="none")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="none")
```


Carbon: Spring/Fall, Spring/Summer, Winter/Fall, and Winter/Summer are significant. This doesn't match with how I originally matched the seasons. 

Nitrogen: Spring/Fall, Spring/Winter, Summer/Fall, and Winter/Summer are significant, which is how I originally matched up the seasons. 


```{r, pairwise bonferroni seasons, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="bonferroni")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="bonferroni")
```

Using bonferrroni, SPring/Fall are significant for carbon, but nothing else. And all the same Nitrogen seasons remain the same as above.


```{r, pairwise holm, message=FALSE}
pairwise.t.test(x=whisker$C, g=whisker$Season, p.adj="holm")
pairwise.t.test(x=whisker$N, g=whisker$Season, p.adj="holm")
```

This method is generally considered superior to the Bonferroni adjustment, and adds Winter/Fall as stat sig for Carbon.


#### Tukey HSD
```{r, tukey, message=FALSE}
TukeyHSD(aov(C~Season, data=whisker))
TukeyHSD(aov(N~Season, data=whisker))
```

Tukey's gives similar as Bonferroni and Holm. There are significant values here, but really - the main takeaway needs to be that these means are only .3-.5. which is VERY SMALL. 



### Biplot by season

Making mean values for Prey and adding in TDFs for prey

```{r, prey means and TDFs, message=FALSE}
si.mean <-si.prey %>%
  group_by(PreyCat) %>% 
  summarise(Cmean=mean(Cnorm), Nmean=mean(N), Csd=sd(Cnorm), Nsd=sd(N), 
            Cse=sd(Cnorm)/sqrt(length(Cnorm)), Nse=sd(N)/sqrt(length(N)))
si.mean<-si.mean[-1,] #removing blank
si.mean<-si.mean[-6,] #removing stars

si.mean$Ctdf<-si.mean$Cmean+2
si.mean$Ntdf<-si.mean$Nmean+2.8
```


```{r, seasonal biplot, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
  geom_point(data= si.mean, aes(x=Ctdf, y=Ntdf, color=PreyCat), size=3) +
  labs(x=expression(paste(delta^13, "C (\u2030)")), 
       y=expression(paste(delta^15, "N (\u2030)" )))  +
  scale_color_discrete(name  ="Prey Group") +
  geom_errorbar(data= si.mean, aes(x=Ctdf, y=Ntdf, ymin = Ntdf-Nse, ymax = Ntdf+Nse,
                                   color= PreyCat), width=0) + 
  geom_errorbarh(data= si.mean, aes(x=Ctdf, y=Ntdf, xmin = Ctdf-Cse,xmax = Ctdf+Cse,
                                    color= PreyCat), height=0) +
  geom_point(data=whisker, aes(x=C, y=N, shape=Season), size=2)+
  theme_few()
```

