---
title: "Preliminary OM and IM results"
author: "Tiff Stephens"
date: "12/1/2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, include=FALSE}
library(dplyr); library(tidyr); library(plyr); library(reshape2); library(lubridate); library(ggplot2); library(DT); library(leaflet); library(htmlwidgets); library(htmltools); library(shiny); library(mapview); library(sp); library(sf); library(knitr); library(cowplot); library(ggpmisc); library(DT); library(plyr)

theme_set(theme_classic())
```





### 1. Import cleaned .csv file and look at dataframe.
```{r, echo = FALSE, include = FALSE}
# read clean file from github
df.core <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/core_matter_2017_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

# check 
str(df.core)
```





### 2. Remove excess columns and calcuate other factors of interest. <br>
```{r, echo = FALSE, include = FALSE}
# remove pan, crucible, and sediment combo weights not necessary here
df.core = df.core %>% 
  select(-pan_weight, -pan_sed_ww_pre_60C, -pan_sed_dw_post_60C, -pan_sed_dw_pre_450C, -pan_sed_dw_post450C, -crucible_weight, -crucible_sed_dw_pre_950C, -crucible_sed_dw_post_950C)
```

```{r, echo = FALSE, include = FALSE}
df.core = df.core %>% 
  mutate(om_percent_dw = (om_dw / sed_dw_pre_450C) * 100, na.rm = TRUE) %>%
  mutate(im_percent_dw = (im_dw / sed_dw_pre_950C) * 100, na.rm = TRUE) %>%
  mutate(om.im_ratio = om_dw / im_dw, na.rm = TRUE) %>%
  mutate(om_density = om_dw * dry_bulk_density, na.rm = TRUE) %>%
  mutate(im_density = im_dw * dry_bulk_density, na.rm = TRUE) %>%
  mutate(porewater_volume_cm3 = sed_ww_pre_60C - sed_dw_post_60C, na.rm = TRUE)
```

```{r, echo = FALSE, include = FALSE}
df.core = df.core %>% 
  select(-sed_ww_pre_60C, -sed_dw_post_60C, -sed_dw_pre_450C, -sed_dw_post_450C, -sed_dw_pre_950C, -sed_dw_post_950C, -na.rm)
```

```{r, echo = FALSE, include = FALSE}
# TEMPORARILY remove these rows...clear mistake in data collection or data entry.
df.core <- df.core[-c(52,195,206,276,365,403,470,481,482,484,513,515,516),]
```





### 3. Where are the processed cores from?
```{r, echo = FALSE}
# new data frame for all cores
locations_all = df.core %>%
  distinct(df.core, latitude, longitude, site) %>%
  drop_na()

# map "locations_all"
leaflet(locations_all) %>%
  addTiles() %>%
  addMarkers(~longitude, ~latitude, popup = ~site, label = ~site)
```
<br>





### 4. Plotting by site and region
#### Total OM (right column) and IM content (left column)
```{r, fig.height = 35, fig.width = 8, echo = FALSE, warning = FALSE}
df.core$site=factor(df.core$site, levels=c("2017_L_01","2017_L_02","2017_L_03","2017_L_04","2017_L_05","2017_L_06","2017_L_07","2017_M_02","2017_M_03","2017_M_04","2017_M_05","2017_M_06","2017_M_07","2017_M_08","2017_H_01","2017_H_02","2017_H_03","2017_H_04","2017_H_05","2017_H_06","2017_H_07")) # order sites

df.core$otter_region=factor(df.core$otter_region, levels=c("Low","Mid","High")) # order zones


# plot organic matter
plot_om_all = ggplot(df.core, aes(layer_depth, om_density)) +
  stat_summary(fun.y=mean, geom="point")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  coord_flip() +
  scale_x_reverse() +
  xlab("Core Depth (cm)") +
  ylab("Organic Matter (g cm^3)") +
  #scale_x_continuous(position = "top") +
  #scale_y_continuous(position = "left") +
  facet_wrap(~site, ncol = 1)

# plot inorganic matter
plot_im_all = ggplot(df.core, aes(layer_depth, im_density)) +
  stat_summary(fun.y=mean, geom="point")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  coord_flip() +
  scale_x_reverse() +
  xlab("Core Depth (cm)") +
  ylab("Organic Matter (g cm^3)") +
  #scale_x_continuous(position = "top") +
  #scale_y_continuous(position = "left") +
  facet_wrap(~site, ncol = 1)

# organize om and im side-by-side
plot_grid(plot_om_all, plot_im_all, align = "hv", ncol = 2)
```
<br>

#### You will notice that site L06 is way different than the rest. This core was loaded with chunky woody debris and this site had a lot of woody debris at the surface; it's real data but an outlier compared to the other sites. Here are two images of the sliced core from site L06:
```{r, include = FALSE}
img1_path = "images/woodchunk1.JPG"
img2_path = "images/woodchunk2.JPG"
```

```{r out.width = "50%", echo = FALSE}
include_graphics(img1_path)
include_graphics(img2_path)
```
<br>


#### For the sake of looking at regional patterns, let's remove site L06.
```{r}
df.core_noL06 = df.core[-c(1:30),] # remove L06 (for now) because organic matter is off the scale
```

<br>
<br>










<br><br><br><br>

### Here are the data grouped by sea otter zone (without L06)
#### The red lines represent the mean values for the length of the entire core.

```{r fig2, fig.height = 10, fig.width = 8, echo = FALSE, warning = FALSE}
df.core_noL06$site=factor(df.core_noL06$site, levels=c("2017_L_01","2017_L_02","2017_L_03","2017_L_04","2017_L_05","2017_L_06","2017_L_07","2017_M_02","2017_M_03","2017_M_04","2017_M_05","2017_M_06","2017_M_07","2017_M_08","2017_H_01","2017_H_02","2017_H_03","2017_H_04","2017_H_05","2017_H_06","2017_H_07")) # order zones

df.core_noL06$otter_region=factor(df.core_noL06$otter_region, levels=c("Low","Mid","High")) # order zones



hlinedat_om <- ddply(df.core_noL06, "otter_region", summarize, regionmean_om = mean(om_density, na.rm = TRUE))

# plot organic matter
plot_om = ggplot(df.core_noL06, aes(layer_depth, om_density)) +
  stat_summary(fun.y=mean, geom="point")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  coord_flip() +
  scale_x_reverse() +
  xlab("Core Depth (cm)") +
  ylab("Organic Matter (g cm^3)") +
  #scale_x_continuous(position = "top") +
  #scale_y_continuous(position = "left") +
  facet_wrap(~otter_region, ncol = 1) +
  geom_hline(aes(yintercept = regionmean_om), hlinedat_om, color = "red")



hlinedat_im <- ddply(df.core_noL06, "otter_region", summarize, regionmean_im = mean(im_density, na.rm = TRUE))

#plopt inorganic matter
plot_im = ggplot(df.core_noL06, aes(layer_depth, im_density)) +
  stat_summary(fun.y=mean, geom="point")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.5) +
  coord_flip() +
  scale_x_reverse() +
  xlab("Core Depth (cm)") +
  ylab("Inorganic Matter (g cm^3)") +
  #scale_x_continuous(position = "top") +
  #scale_y_continuous(position = "left") +
  facet_wrap(~otter_region, ncol = 1) +
  geom_hline(aes(yintercept = regionmean_im), hlinedat_im, color = "red")



# organize om and im side-by-side
plot_grid(plot_om, plot_im, align = "hv", ncol = 2)
```

```{r, echo = FALSE, message = FALSE}
# make new dataframe for mapping
#locations = df.core_noL06 %>%
  #distinct(df.core_noL06, latitude, longitude, site) %>%
  #drop_na()

# turn into leaflet map
#leaflet(locations) %>%
  #addTiles() %>%
  #addMarkers(~longitude, ~latitude, popup = ~site, label = ~site)
```

<br>

#### It looks like the low sea otter zone has more organic and inorganic matter in the sediments, and the mid sites have a nice range that tracks through depth.  

<br>
<br>














### 4. Plotting across the SOI
```{r, echo = FALSE, include = FALSE, warning = FALSE}
colnames(df.core)

om <- df.core %>% 
  select(otter_region, site, om_density)

m.om <- melt(om, id = 1:2, na.rm = TRUE)

trim_om <- dcast(m.om, otter_region + site ~ ., mean)
colnames(trim_om)[which(names(trim_om) == ".")] <- "om_density"






im <- df.core %>% 
  select(otter_region, site, im_density)

m.im <- melt(im, id = 1:2, na.rm = TRUE)

trim_im <- dcast(m.im, otter_region + site ~ ., mean)
colnames(trim_im)[which(names(trim_im) == ".")] <- "im_density"






om.im <- df.core %>% 
  select(otter_region, site, om.im_ratio)

m.om.im <- melt(om.im, id = 1:2, na.rm = TRUE)

trim_om.im <- dcast(m.om.im, otter_region + site ~ ., mean)
colnames(trim_om.im)[which(names(trim_om.im) == ".")] <- "om.im_ratio"





# join trimmed data of interest into one df
df.trim <- left_join(trim_om, trim_im, by = c("otter_region","site"))
df.trim <- left_join(df.trim, trim_om.im, by = c("otter_region","site"))





```

```{r, echo = FALSE, include = FALSE, warning = FALSE}
df.soi <- read.csv("https://raw.githubusercontent.com/APECS-ak/APECS-master-repos/master/ALL_DATA/sea_otter_impact_index_2017_new.csv", stringsAsFactors = FALSE, header = TRUE)
```

```{r, echo = FALSE, include = FALSE, warning = FALSE}
# join core data with soi data

df.core.trim <- left_join(df.trim, df.soi, by = c("site"))

colnames(df.core.trim)

df.core.trim <- df.core.trim %>% 
  select(otter_region, site, place_name, latitude, longitude, sea_otter_index, sea_otter_duration, om_density, im_density, om.im_ratio)
```

```{r, echo = FALSE, include = FALSE, warning = FALSE}
# remove L06

df.core.trim <- df.core.trim[-6,]
```








```{r, echo = FALSE, include = FALSE, warning = FALSE}
str(df.core.trim)
df.core.trim$otter_region <- as.factor(df.core.trim$otter_region)


p1 <- ggplot(df.core.trim, aes(otter_region, om_density)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p1)



p2 <- ggplot(df.core.trim, aes(otter_region, im_density)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p2)



p3 <- ggplot(df.core.trim, aes(otter_region, om.im_ratio)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p3)



```

```{r, echo = FALSE, fig.width = 12, fig.height = 5}
title.cp1 <- ggdraw() + draw_label("Trends with SO zone?", fontface='bold')

cp1 <- plot_grid(p1, p2, p3, labels=c('A', 'B', 'C'), align = 'h', ncol=3, nrow=1, rel_widths = c(1,1,1))

plot_grid(title.cp1, cp1, ncol=1, rel_heights=c(0.1, 1))
```
<br><br><br><br><br><br><br><br>
























```{r, echo = FALSE, include = FALSE, warning = FALSE}
str(df.core.trim)
df.core.trim$sea_otter_duration <- as.factor(df.core.trim$sea_otter_duration)


p7 <- ggplot(df.core.trim, aes(sea_otter_duration, om_density)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p7)



p8 <- ggplot(df.core.trim, aes(sea_otter_duration, im_density)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p8)



p9 <- ggplot(df.core.trim, aes(sea_otter_duration, om.im_ratio)) +
  geom_boxplot() +
  geom_point(size = 3, alpha = 0.6)
plot(p9)



```

```{r, echo = FALSE, fig.width = 12, fig.height = 5}
title.cp2 <- ggdraw() + draw_label("Trends with SO duration?", fontface='bold')

cp2 <- plot_grid(p7, p8, p9, labels=c('A', 'B', 'C'), align = 'h', ncol=3, nrow=1, rel_widths = c(1,1,1))

plot_grid(title.cp2, cp2, ncol=1, rel_heights=c(0.1, 1))
```
<br><br>








```{r, echo = FALSE, include = FALSE, warning = FALSE}
# plotting in scatter
my.formula <- y ~ x # defined formula (linear regression) for stats labels on plot

# shoot_mass_m2
p10 = ggplot(df.core.trim, aes(sea_otter_index, log(om_density))) +
  geom_point(size=3) +
  #geom_smooth(method=lm, formula=y~x, se=FALSE, fullrange=FALSE) +
  #xlab("Secondary sediment class (inside transect)\n")+ylab("\nBG biomass per cm rhizome (g per msq, DW)") +
  theme(legend.position="none")
  #stat_poly_eq(formula = my.formula, 
               #aes(label = paste(..rr.label.., sep = "~~~")), 
               #label.x.npc = 'right', label.y.npc = 'top', size = 4, parse = TRUE) +
  #stat_fit_glance(method = 'lm', method.args = list(formula = my.formula), geom = 'text',
                  #aes(label = paste("P-value = ", signif(..p.value.., digits = 3), sep = "")),
                  #label.x.npc = 'left', label.y.npc = 'top', size = 4)
plot(p10)




p11 = ggplot(df.core.trim, aes(sea_otter_index, log(im_density))) +
  geom_point(size=3) +
  #geom_smooth(method=lm, formula=y~x, se=FALSE, fullrange=FALSE) +
  #xlab("Secondary sediment class (inside transect)\n")+ylab("\nBG biomass per cm rhizome (g per msq, DW)") +
  theme(legend.position="none")
  #stat_poly_eq(formula = my.formula, 
               #aes(label = paste(..rr.label.., sep = "~~~")), 
               #label.x.npc = 'right', label.y.npc = 'top', size = 4, parse = TRUE) +
  #stat_fit_glance(method = 'lm', method.args = list(formula = my.formula), geom = 'text',
                  #aes(label = paste("P-value = ", signif(..p.value.., digits = 3), sep = "")),
                  #label.x.npc = 'left', label.y.npc = 'top', size = 4)
plot(p11)




p12 = ggplot(df.core.trim, aes(sea_otter_index, log(om.im_ratio))) +
  geom_point(size=3) +
  geom_smooth(method=lm, formula=y~x, se=FALSE, fullrange=FALSE) +
  #xlab("Secondary sediment class (inside transect)\n")+ylab("\nBG biomass per cm rhizome (g per msq, DW)") +
  theme(legend.position="none")
  #stat_poly_eq(formula = my.formula, 
               #aes(label = paste(..rr.label.., sep = "~~~")), 
               #label.x.npc = 'right', label.y.npc = 'top', size = 4, parse = TRUE) +
  #stat_fit_glance(method = 'lm', method.args = list(formula = my.formula), geom = 'text',
                  #aes(label = paste("P-value = ", signif(..p.value.., digits = 3), sep = "")),
                  #label.x.npc = 'left', label.y.npc = 'top', size = 4)
plot(p12)

```
<br>

```{r, echo = FALSE, fig.width = 12, fig.height = 5}
title.cp3 <- ggdraw() + draw_label("Trends with SO index?", fontface='bold')

cp3 <- plot_grid(p10, p11, p12, labels=c('A', 'B', 'C'), align = 'h', ncol=3, nrow=1, rel_widths = c(1,1,1))

plot_grid(title.cp3, cp3, ncol=1, rel_heights=c(0.1, 1))
```
<br><br>