---
title: "Eelgrass_POM_calculations_2018"
author: "Wendel Raymond"
date: "July 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Particulate organic matter (POM) calculations
From the raw cleaned data this script will export a file summarized by site ready for analysis. Major task are the calculation 

## Libraries
Processing of this data will require the following
```{r libraries}
library(dplyr)
library(ggplot2)
```

## Data to import
Data includes the field POM collection data, filter masses
```{r data}
pom <- read.csv("../ALL_DATA/POM_collections_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)

filt <- read.csv("../ALL_DATA/POM_filter_mass_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

## Caclulate POM organic and inorganic mass
```{r filter}
filt$POM_org_mass <- (filt$dry_mass_g - filt$pan_mass_g) - filt$pre_dry_mass_g
filt$POM_inorg_mass <- (filt$burn_dry_mass_g - filt$pan_mass_g) - filt$pre_dry_mass_g
```

## Merge POM org/inorg with POM data
```{r merge}
pom <- merge(pom, filt[, 3:9], by.x = "quant_filter_no", by.y = "filter_no")
```

## Export
```{r export}
write.csv(pom, "../ALL_DATA/POM_2018_derived.csv", row.names = FALSE)
```

