---
title: "ETR_data_exploration_2018"
author: "Wendel Raymond"
date: "October 9, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Eelgrass community trophic relationships (ETR) data exploration
Here I will conduct exploratory analysis of 2018 eelgrass community data

```{r libraries, echo = FALSE, warning=FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
library(DT)
library(cowplot)
library(RColorBrewer)
library(vegan)

theme_set(theme_classic())
```

## Load data
Load biomass/abundace data, stable isotope, and fatty acid data

Biomass and oceanography
```{r dat bio, echo=FALSE}
eg <- read.csv("../ALL_DATA/Eelgrass_biometrics_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

crb <- read.csv("../ALL_DATA/crab_simple_site_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

crb.sp <- read.csv("../ALL_DATA/crab_site_sp_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

clm <- read.csv("../ALL_DATA/eelgrass_clam_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

clm.sp <- read.csv("../ALL_DATA/eelgrass_clam_site_sp_2018.csv", header = TRUE, stringsAsFactors = FALSE)

fsh <- read.csv("../ALL_DATA/Fish_mass_site_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

pom <- read.csv("../ALL_DATA/POM_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

oce <- read.csv("../ALL_DATA/Site_oceanography_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

Stable Isotope - preliminary
```{r dat iso, echo = FALSE}
si <- read.csv("E:/wraymond2/My Documents/Graduate School/Eelgrass/Eelgrass trophic relationships/Data/SI_prelim_2018.csv", header = TRUE, stringsAsFactors = FALSE)
```

Fatty Acid
```{r dat fa, echo = FALSE}
fa_0.5 <- read.csv("../ALL_DATA/FA_proportions_0.5filter_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

fa_1.0 <- read.csv("../ALL_DATA/FA_proportions_1.0filter_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)
```

Biomarker metadata
```{r dat biomarker, echo = FALSE}
bimrk <- read.csv("../ALL_DATA/Biomarker_collections_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

### Biomarker metadata
Extract metadata on samples. N pooled, size, etc.
```{r biomarker sum, echo = FALSE}
## Filter out ones that I actualy processed all the way ##
bimrk_redu <- bimrk %>%
  filter(Biomarker_ID %in% fa_1.0$ID)

## Run some caculations ##
bimrk_redu$mean_size <- mean(bimrk_redu[, 11: 24], na.rm = TRUE)

## Summary table ##
bimrk_sum <- bimrk_redu %>% 
  group_by(Place_name, Species_common) %>% 
  summarise(n_samples = n())
```


### Complie biomass data
Merge all the different biomass data types into one data frame
```{r merge, echo = FALSE}
dat <- merge(eg, crb, by = c("site", "place_name"), all.x = TRUE)
dat <- merge(dat, clm[, c(1, 5:13)], by = "site")
dat <- merge(dat, fsh, by = "site")
dat <- merge(dat, oce[, c(1, 6:19)], by = "site")
```

## Data exploration
### Biomass
```{r exp plots, echo = FALSE}
## Eelgrass mass ##
ggplot(dat) +
  geom_col(aes(x = site, y  = eg_shoot_mass_m)) +
  geom_errorbar(aes(x = site, ymin = eg_shoot_mass_m - eg_shoot_mass_m_se, ymax = eg_shoot_mass_m + eg_shoot_mass_m_se), width = 0) +
  labs(x = "Site", y = "Eelgrass shoot mass (g/m2)")

## Macroalgae cover ##
ggplot(dat) +
  geom_col(aes(x = site, y  = macro_cover)) +
  geom_errorbar(aes(x = site, ymin = macro_cover - macro_cover_se, ymax = macro_cover + macro_cover_se), width = 0) +
  labs(x = "Site", y = "Macroalgae % cover")

## Diatom cover ##
ggplot(dat) +
  geom_col(aes(x = site, y  = diatom_cover)) +
  geom_errorbar(aes(x = site, ymin = diatom_cover - diatom_cover_se, ymax = diatom_cover + diatom_cover_se), width = 0) +
  labs(x = "Site", y = "Diatom % cover")

## Epiphyte load ##
ggplot(dat) +
  geom_col(aes(x = site, y  = epiph_load)) +
  geom_errorbar(aes(x = site, ymin = epiph_load - epiph_load_se, ymax = epiph_load + epiph_load_se), width = 0) +
  labs(x = "Site", y = "Epiphyte load (g/g eelgrass)")

## Grazer load ##
ggplot(dat) +
  geom_col(aes(x = site, y  = graz_load)) +
  geom_errorbar(aes(x = site, ymin = graz_load - graz_load_se, ymax = graz_load + graz_load_se), width = 0) +
  labs(x = "Site", y = "Grazer load (g/g eelgrass)")

## Idotea load ##
ggplot(dat) +
  geom_col(aes(x = site, y  = ido_load)) +
  geom_errorbar(aes(x = site, ymin = ido_load - ido_load_se, ymax = ido_load + ido_load_se), width = 0) +
  labs(x = "Site", y = "Idotea load (g/g eelgrass)")

## Limpet load ##
ggplot(dat) +
  geom_col(aes(x = site, y  = limp_load)) +
  geom_errorbar(aes(x = site, ymin = limp_load - limp_load_se, ymax = limp_load + limp_load_se), width = 0) +
  labs(x = "Site", y = "Limpet load (g/g eelgrass)")

## Clam mass ##
ggplot(dat) +
  geom_col(aes(x = site, y  = clm_mass_m)) +
  geom_errorbar(aes(x = site, ymin = clm_mass_m - clm_mass_m_se, ymax = clm_mass_m + clm_mass_m_se), width = 0) +
  labs(x = "Site", y = "Clam mass (g/m2)")

## Clam species ##
ggplot(clm.sp, aes(x = site, y = mass, fill = sp_code)) +
  geom_bar(position = position_dodge(), stat = "identity") +
  geom_errorbar(aes(ymin = mass - mass_se, ymax = mass + mass_se), width = 0, position=position_dodge(0.9)) +
  labs(x = "Site", y = "Clam mass (g/m2)")

## Crab mass ##
ggplot(dat) +
  geom_col(aes(x = site, y = crab_mass)) +
  geom_errorbar(aes(x = site, ymin = crab_mass - crab_mass_se, ymax = crab_mass + crab_mass_se, width = 0)) +
  labs(x = "Site", y = "Crab mass (g/string)")

## Crab species mass ##
ggplot(crb.sp, aes(x = site, y = mass, fill = sp_code)) +
  geom_bar(position = position_dodge(), stat = "identity") +
  geom_errorbar(aes(ymin = mass - mass_se, ymax = mass + mass_se), width = 0, position=position_dodge(0.9)) +
  labs(x = "Site", y = "Crab mass (g/string)")

## All Fish ##
ggplot(dat) +
  geom_col(aes(x = site, y = total_fish_mass / 1000)) +
  labs(x = "Site", y = "Fish mass (kg/site)")

## Shiner Perch ##
ggplot(dat) +
  geom_col(aes(x = site, y = PERCHSH / total_fish_mass)) +
  labs(x = "Site", y = "Proportion shiner perch mass")

## Staghorn Sculpin ##
ggplot(dat) +
  geom_col(aes(x = site, y = SCULPSTG / total_fish_mass)) +
  labs(x = "Site", y = "Proportion staghorn mass")

## Snake prickleback ##
ggplot(dat) +
  geom_col(aes(x = site, y = PRICKSN / total_fish_mass)) +
  labs(x = "Site", y = "Proportion snake prickleback mass")
```

### Particulate Organic Matter
summaries by site
```{r pom data, echo = FALSE}
pom_sum <- pom %>%
  group_by(site) %>% 
  summarise(POM_org_mass_mean = mean(POM_org_mass),
            POM_org_mass_se = sd(POM_org_mass) / sqrt(length(POM_org_mass)),
            POM_inorg_mass_mean = mean(POM_inorg_mass),
            POM_inorg_mass_se = sd(POM_inorg_mass) / sqrt(length(POM_inorg_mass)))
```

```{r plots, echo = FALSE}
## POM organic mass ##
ggplot(pom_sum) +
  geom_col(aes(x = site, y  = POM_org_mass_mean)) +
  geom_errorbar(aes(x = site, ymin = POM_org_mass_mean - POM_org_mass_se, ymax = POM_org_mass_mean + POM_org_mass_se), width = 0) +
  labs(x = "Site", y = "POM organic mass (g/100ml)")

## POM inorganic mass ##
ggplot(pom_sum) +
  geom_col(aes(x = site, y  = POM_inorg_mass_mean)) +
  geom_errorbar(aes(x = site, ymin = POM_inorg_mass_mean - POM_inorg_mass_se, ymax = POM_inorg_mass_mean + POM_inorg_mass_se), width = 0) +
  labs(x = "Site", y = "POM inorganic mass (g/100ml)")
```


### Oceanography
```{r oce, echo = FALSE}
ggplot(dat) +
  geom_col(aes(x = site, y = X1m_temp_C))

ggplot(dat) +
  geom_col(aes(x = site, y = X5m_temp_C))
```


### Stable Isotopes

#### SI data prep
Merge species with si values
```{r si, echo = FALSE}
si <- merge(si, bimrk, by = "Biomarker_ID", all.x = TRUE)
si$Species_common <- factor(si$Species_common, levels = c("Shiner perch", "Snake prickleback", "Staghorn sculpin", "Dungeness crab", "Helmet crab", "Red rock crab", "Dock shrimp", "Macoma sp.", "Bentnose Macoma", "Pointed Macoma", "Butter clam", "Idotea", "Limpet", "Eelgrass", "Eelgrass diatoms", "Fucus", "Particulate organic matter", "Sugar kelp", "Ulva"))
```

#### SI Plots
```{r si plots, echo = FALSE}
pal <- colorRampPalette(brewer.pal(9, "Paired"))

ggplot(si) +
  geom_point(aes(x = del_C, y = del_N, color = Species_common, shape = Species_common), size = 3) +
  scale_color_manual(values = pal(19))+
  scale_shape_manual(values = rep(c(15:19), 4))

ggplot(si) +
  geom_point(aes(x = del_C, y = del_N, color = Sea_otter_region), size = 3)
```

### Fatty acids
The ultimate goal will be to look at some basic nmds plots of all species. Then overlay some depended variables like site and sea otter treatment.

#### Examine FAs
What FAs do we have here.
```{r fa names, echo = FALSE}
FA_names <- colnames(fa_1.0[,3:67])
FA_names
```


First will will have to prep that data with some manipulations and transformations and standardizations.

#### Transformations and standardizations
Subsets
```{r subset, echo = FALSE}
## Aminals ##
fa_anm_1.0 <- fa_1.0 %>% 
  filter(Species_common != "Eelgrass" & Species_common != "Eelgrass diatoms" & Species_common != "Fucus" & Species_common != "Particulate organic matter" & Species_common != "Sugar kelp" & Species_common != "Ulva")

## Producers ##
fa_pro_1.0 <- fa_1.0 %>%
  filter(Species_common == "Eelgrass" | Species_common == "Eelgrass diatoms" | Species_common == "Fucus" | Species_common == "Particulate organic matter" | Species_common == "Sugar kelp" | Species_common == "Ulva")
```


I will use and arcsine sqrt transformation 
```{r trans std, echo = FALSE}
## Transformation ##
fa_0.5_trs <- asin(sqrt(fa_0.5[, 3:77]))

fa_all_1.0_trs <- asin(sqrt(fa_1.0[, 3: 67]))
fa_anm_1.0_trs <- asin(sqrt(fa_anm_1.0[, 3:67]))
fa_pro_1.0_trs <- asin(sqrt(fa_pro_1.0[, 3:67]))

## Standardization ##
fa_0.5_trs_std <- scale(fa_0.5_trs, center = FALSE, scale = apply(fa_0.5_trs, 2, max))

fa_all_1.0_trs_std <- scale(fa_all_1.0_trs, center = FALSE, scale = apply(fa_all_1.0_trs, 2, max))
fa_anm_1.0_trs_std <- scale(fa_anm_1.0_trs, center = FALSE, scale = apply(fa_anm_1.0_trs, 2, max))
fa_pro_1.0_trs_std <- scale(fa_pro_1.0_trs, center = FALSE, scale = apply(fa_pro_1.0_trs, 2, max))
```

#### NMDS
NMDS calculations
```{r fa nmds, include=FALSE}
## Calculate distances ##
fa_all_1.0_dist <- vegdist(fa_all_1.0_trs_std, method = "bray")
fa_anm_1.0_dist <- vegdist(fa_anm_1.0_trs_std, method = "bray")
fa_pro_1.0_dist <- vegdist(fa_pro_1.0_trs_std, method = "bray")

fa_0.5_dist <- vegdist(fa_0.5_trs_std, method = "bray")

## nmds ##
fa_all_1.0_mds <- metaMDS(fa_all_1.0_dist)
fa_anm_1.0_mds <- metaMDS(fa_anm_1.0_dist)
fa_pro_1.0_mds <- metaMDS(fa_pro_1.0_dist)

fa_0.5_mds <- metaMDS(fa_0.5_dist, try = 50)
```

FA vectors
```{r fa vector, echo = FALSE, eval = FALSE}
## get arrows of FAs correlating to first two dimensions ##
vec.fa <- envfit(fa_all_1.0_mds$points, fa_all_1.0_dist, perm = 9999) # fit vector arrows of FAs correlating with dimensions

## pull scores vector arrows of FAs correlating with dimensions ##
FA_arrows <- scores(vec.fa, display = c("vectors")) 

## calculate scaling multiplier based on min range of points in NMDS ##
scalefactor <- 0.3 * min(max(fa_all_1.0_mds$points[,1]) - min(fa_all_1.0_mds$points[,1]),max(fa_all_1.0_mds$points[,2]) - min(fa_all_1.0_mds$points[,2]))

FA_arrows <- FA_arrows * scalefactor # scaling of arrows to fit plot area based on scalefactor above

FA_arrows <- as.data.frame(FA_arrows) # save those as a datafullframe

## Naming arrows ##
```


##### NMDS plots
Data prep. Build dataframe from metaMDS output fo easy plotting
```{r plot data, echo = FALSE}
## All data ##
fa_all_1.0_mds_dat <- as.data.frame(scores(fa_all_1.0_mds))
fa_all_1.0_mds_dat$ID <- fa_1.0$ID 
fa_all_1.0_mds_dat$Species_common <- fa_1.0$Species_common
fa_all_1.0_mds_dat <- merge(fa_all_1.0_mds_dat, bimrk[, c(1:4, 7, 9, 10)], by.x = "ID", by.y = "Biomarker_ID")
fa_all_1.0_mds_dat$Species_common <- factor(fa_all_1.0_mds_dat$Species_common, levels = c("Shiner perch", "Snake prickleback", "Staghorn sculpin", "Dungeness crab", "Helmet crab", "Red rock crab", "Dock shrimp", "Macoma sp.", "Bentnose Macoma", "Pointed Macoma", "Butter clam", "Idotea", "Limpet", "Eelgrass", "Eelgrass diatoms", "Fucus", "Particulate organic matter", "Sugar kelp", "Ulva"))

## Animals ##
fa_anm_1.0_mds_dat <- as.data.frame(scores(fa_anm_1.0_mds))
fa_anm_1.0_mds_dat$ID <- fa_anm_1.0$ID 
fa_anm_1.0_mds_dat$Species_common <- fa_anm_1.0$Species_common
fa_anm_1.0_mds_dat <- merge(fa_anm_1.0_mds_dat, bimrk[, c(1:4, 7, 9, 10)], by.x = "ID", by.y = "Biomarker_ID")
fa_anm_1.0_mds_dat$Species_common <- factor(fa_anm_1.0_mds_dat$Species_common, levels = c("Shiner perch", "Snake prickleback", "Staghorn sculpin", "Dungeness crab", "Helmet crab", "Red rock crab", "Dock shrimp", "Macoma sp.", "Bentnose Macoma", "Pointed Macoma", "Butter clam", "Idotea", "Limpet"))

## Producers ##
fa_pro_1.0_mds_dat <- as.data.frame(scores(fa_pro_1.0_mds))
fa_pro_1.0_mds_dat$ID <- fa_pro_1.0$ID 
fa_pro_1.0_mds_dat$Species_common <- fa_pro_1.0$Species_common
fa_pro_1.0_mds_dat <- merge(fa_pro_1.0_mds_dat, bimrk[, c(1:4, 7, 9, 10)], by.x = "ID", by.y = "Biomarker_ID")
fa_pro_1.0_mds_dat$Species_common <- factor(fa_pro_1.0_mds_dat$Species_common, levels = c("Eelgrass", "Eelgrass diatoms", "Fucus", "Particulate organic matter", "Sugar kelp", "Ulva"))

fa_0.5_mds_dat <- as.data.frame(scores(fa_0.5_mds))
fa_0.5_mds_dat$ID <- fa_0.5$ID 
fa_0.5_mds_dat$Species_common <- fa_0.5$Species_common
```

Plots 
```{r nmds plots, echo = FALSE}
## Color Pallatte ##
pal <- colorRampPalette(brewer.pal(12, "Paired"))

## nmds species all ##
ggplot(fa_all_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, color = Species_common, shape = Species_common), size = 3) +
  scale_color_manual(values = pal(19)) +
  scale_shape_manual(values = rep(c(15:19), 4)) +
  geom_text(x = -0.27, y = -0.35, label = "stress = 0.1652")

## nmds sites and species ##
ggplot(fa_all_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, shape = Place_name, color = Species_common), size = 3) +
  scale_color_manual(values = pal(19)) +
  scale_shape_manual(values = c(0, 15, 16, 17, 18, 6)) +
  geom_text(x = -0.27, y = -0.35, label = "stress = 0.1652")

## nmds sea otter and species ##
ggplot(fa_all_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, shape = Sea_otter_region, color = Species_common), size = 3) +
  scale_color_manual(values = pal(19)) +
  scale_shape_manual(values = c(16, 1)) +
  geom_text(x = -0.27, y = -0.35, label = "stress = 0.1652")

## nmds species animals ##
ggplot(fa_anm_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, color = Species_common, shape = Species_common), size = 3) +
  scale_color_manual(values = pal(13)) +
  scale_shape_manual(values = rep(c(15:19), 3)) +
  geom_text(x = -0.24, y = -0.24, label = "stress = 0.1775")

## nmds sites and species ##
ggplot(fa_anm_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, shape = Place_name, color = Species_common), size = 3) +
  scale_color_manual(values = pal(13)) +
  scale_shape_manual(values = c(0, 15, 16, 17, 18, 6)) +
  geom_text(x = -0.24, y = -0.24, label = "stress = 0.1775")

## nmds sea otter and species ##
ggplot(fa_anm_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, shape = Sea_otter_region, color = Species_common), size = 3) +
  scale_color_manual(values = pal(13)) +
  scale_shape_manual(values = c(16, 1)) +
  geom_text(x = -0.24, y = -0.24, label = "stress = 0.1775")

## nmds species prodecers ##
ggplot(fa_pro_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, color = Species_common, shape = Species_common), size = 3) +
  scale_color_manual(values = pal(19)[14:19]) +
  scale_shape_manual(values = rep(c(15:19), 2)) +
  geom_text(x = -0.40, y = -0.22, label = "stress = 0.1306")

## nmds sites and species ##
ggplot(fa_pro_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, color = Species_common, shape = Place_name), size = 3) +
  scale_color_manual(values = pal(19)[14:19]) +
  scale_shape_manual(values = c(0, 15, 16, 17, 18, 6)) +
  geom_text(x = -0.40, y = -0.22, label = "stress = 0.1306")

## nmds sea otter and species ##
ggplot(fa_pro_1.0_mds_dat) +
  geom_point(aes(x = NMDS1, y = NMDS2, shape = Sea_otter_region, color = Species_common), size = 3) +
  scale_color_manual(values = pal(19)[14:19]) +
  scale_shape_manual(values = c(16, 1)) +
  geom_text(x = -0.40, y = -0.22, label = "stress = 0.1306")
```


