---
title: "ETR_analyses"
author: "Wendel Raymond"
date: "October 22, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Eelgrass trophic relationships - analyses
*Question:* Do sea otters effects the tropic structure of eelgrass communities in Southeast Alaska? From my 2017 data we found that sea otters have a large negative effect on crabs and are positively related to eelgrass biomass, suggesting that sea otter are influencing the eelgrass community. Furthermore we did not find evidence for all the hypothesized links between major community members necessary to complete the full trophic cascade. Notable we found no evidence of a relationship between crabs and grazer and fish and grazers. To this end we further investigated the dynamics of this community by measuring the biomass, stable isotopes, and fatty acids of key eelgrass community constituents.

*Some opening notes* There is a lot of data. There could be multiple papers here. Some more exploratory analysis is definitely warranted but the original goal was to look at the whole community. Crafting analyses so that we answer questions from that perspective should be the priority. However, if interesting stories arise maybe the approach will change. Just sayin. 

```{r libraries, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
library(DT)
library(cowplot)
library(RColorBrewer)
library(vegan)

theme_set(theme_classic())
```

## Data
Data falls under three broad categories. Biomass, stable isotopes, and fatty acids. Biomass data files are broken up by sampling type but can easily be combined. In addition, biomarker (SI and FA) metadata is useful to match those data with site, date, treatment, etc. data.
Biomass and oceanography
```{r dat bio, echo=FALSE}
eg <- read.csv("../ALL_DATA/Eelgrass_biometrics_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

crb <- read.csv("../ALL_DATA/crab_simple_site_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

crb.sp <- read.csv("../ALL_DATA/crab_site_sp_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

crb.all <- read.csv("../ALL_DATA/Crab_pots_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

clm <- read.csv("../ALL_DATA/eelgrass_clam_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

clm.sp <- read.csv("../ALL_DATA/eelgrass_clam_site_sp_2018.csv", header = TRUE, stringsAsFactors = FALSE)

fsh <- read.csv("../ALL_DATA/Fish_mass_site_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

pom <- read.csv("../ALL_DATA/POM_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

oce <- read.csv("../ALL_DATA/Site_oceanography_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

Stable Isotope - preliminary
```{r dat iso, echo = FALSE}
si <- read.csv("E:/wraymond2/My Documents/Graduate School/Eelgrass/Eelgrass trophic relationships/Data/SI_prelim_2018.csv", header = TRUE, stringsAsFactors = FALSE)
```

Fatty Acid
```{r dat fa, echo = FALSE}
fa_0.5 <- read.csv("../ALL_DATA/FA_proportions_0.5filter_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)

fa_1.0 <- read.csv("../ALL_DATA/FA_proportions_1.0filter_2018_derived.csv", header = TRUE, stringsAsFactors = FALSE)
```

Biomarker metadata
```{r dat biomarker, echo = FALSE}
bimrk <- read.csv("../ALL_DATA/Biomarker_collections_2018_RAW.csv", header = TRUE, stringsAsFactors = FALSE)
```

### Complie biomass data
Merge all the different biomass data types into one data frame
```{r merge, echo = FALSE}
dat <- eg
dat$sea_otter_tr <- c("high", "high", "high", "low", "low", "low")
dat <- cbind(dat[, c(1:10, 53, 11:52)])
dat <- merge(dat, crb, by = c("site", "place_name"), all.x = TRUE)
dat <- merge(dat, clm[, c(1, 5:13)], by = "site")
dat <- merge(dat, fsh, by = "site")
dat <- merge(dat, oce[, c(1, 6:19)], by = "site")
```


## Analyses
A critical piece for all analyses is testing the effect of site and sea otter treatment. Within each sea otter treatment three different sites were sampled. 

### Biomass
Compare biomass of community members between sea otter treatments

#### ANOVAS of sites and treatment
Eelgrass

Epiphytes

Grazers

Crabs

Fish

### Stable Isotopes
There are two perspectives in analysis. 1) The whole community (all data) comparisons and 2) by species comparisons.

#### Whole community
Convex hulls

#### Species specific
Convex hulls

Trophic level

### Fatty Acids
Similar to SI data there are two perspectives to analysis. 1) The whole community and 2) by species comparisons.

#### Whole community
PERMANOVA and PERMDISP of site by treatment. We know/suspect that species will differ from each other. We should show this (to make sure) but really this is not the story. They story will more be on the within species by treatment comparisons. 

#### Species specific
PERMANOVA and PERMDISP by treatment

FA vectors

SIMPER - what FAs are driving differences?

Specific FA comparisons - What this looks like will likely depend on the results from multivariate analyses.