---
title: '---in_progress(Sea_otter_impact_index_full)'
author: "Wendel Raymond"
date: "December 14, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Sea otter impact index
Sea otters are hard to keep track of. Until the 2017 field season the most reliable measure of sea otters in the Prince of Wales Island region were the USFWS aerial surveys. These data provided densities and time since occupation of sea otters. However the most recent survey was done in 2011. In an effort to add more resolution to how we think about sea otters we collected a variety of sea otter impact measures over the 2017 field season. This script summaries and then combined these measures to create a sea otter impact index. 

In this script we will calcualte the sea otter impact index from raw data to final index. This will be in contrast to relying on hard to track ArcGIS processing.

## Packages
Since we will be working with spatial data we need to load a bunch of packages that deal with spatial data.
```{r libraries}
library(dplyr)
library(dplyr)
library(ggplot2)
library(spatstat)
library(maptools)
library(rgdal)
library(rgeos)
library(raster)
library(gdistance)
library(leaflet)
```

## Data
You will need data on.
1. Sites from which sea otter surveys were centered from (points)
2. Sea otter survey data (points with an "n sea otter" data attribute)
3. The 2003 and 2010 USFWS aerial surveys distribution polygons
4. Tim's, in review, survey population density polygons 
5. Southeast Alaska water polygon
```{r data}
## Sites ##
sites <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/Eelgrass/Data/2017 Field Season/GIS", layer = "Otter_Survey_Sites_2017_All_UTM")
sites <- sites[1:38,] # remove the blank row thats in there

## Sea otters that where observed ##
otts <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/Eelgrass/Data/2017 Field Season/GIS", layer = "Otter_Survey_All_17Oct17_UTM")
otts@data$n_otters <- as.numeric(otts@data$n_otters) # data is imported as a factor

## USFWS polygons ##
# 2003 Sea Otters
sd2003 <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/GIS General/Sea Otter Distribution Polygons/South SEAK Sea Otter Distribution Polygons", layer="Clipped sea otter dist_2003") 

# 2010 Sea Otters
sd2010 <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/GIS General/Sea Otter Distribution Polygons/South SEAK Sea Otter Distribution Polygons", layer="Clipped sea otter dist_2010") 

## Tim's survey density blocks ##
poparea <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/Sea Otter Harvest/GIS Files/Hab_All_1.27.2017", layer = "Hab_All_UTM")

## Prince of Wales Water Polygon
h2o <- readOGR(dsn = "E:/wraymond2/My Documents/Graduate School/Eelgrass/Data/2017 Field Season/GIS", layer = "POW_water_UTM")
```

## Plot sites and sea otters
```{r plotting everything}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = sd2010, stroke = NA, fillColor = "orange", fillOpacity = 0.8, group = "2014") %>% 
  addPolygons(data = sd2003, stroke = NA, fillColor = "blue", fillOpacity = 0.8, group = "2010") %>%
  addMarkers(data = sites, ~longitude, ~latitude, label = ~site) %>% 
  addCircleMarkers(data = otts, ~longitude, ~latitude, color = "red", stroke = FALSE, radius = 5, fillOpacity = ~(n_otters/max(n_otters)))

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = poparea, stroke = NA, fillColor = "red", fillOpacity = 0.8, group = "Population Area")
```

## Calculating survey density
The general steps are as follows
1. Calculate survey area centered at each survey site and bounded by 2 nm "as the otter swims"
2. Calculate area of above survey area
3. Calculate density by counting number of otters in each area (and each survey instance if necessary) and dividing by the survey area

### Calcualte / generate survey area
Using the site points we will generate a unique polygon for each site that is bounded by 2 nm from the site "as the otter swims". The other way to think about this 2 nm over water.

Covert of water polygon to raster. We want the cells to be a certian size so you need to inspect extent of the polygon so htat you can devide in a way so that you have the cell sizes you want. We cant 50 meter raster cells so the x and y excents should be devidied so that each cell will be ~50 X 50 meters large.
```{r polygon to raster}
# check extent
extent(h2o)

# create blank raster with appropriate dimentions
r <- raster(ncol = (848183.9 - 75165.99) / 100, nrow = (6686378 - 6040098) / 100)

# create raster
h2o.rast <- rasterize(h2o, r)
crs(h2o.rast) <- "+proj=utm +zone=8 +ellps=GRS80 +towgs84=0,0,0"

# assign values to raster
h2o.rast@data@values <- 100
```

Create survey area for each site by selecting raster cells within 2nm == 3704 meters from the sites.
```{r survey area}
# Transition layer with 4 directions
h2o.trans.4 <- transition(h2o.rast, transitionFunction = function(x){50}, directions = 4)
h2o.trans.4 <- geoCorrection(h2o.trans.4, type = "r", scl = FALSE)

# Transition layer with 8 directions
h2o.trans.8 <- transition(h2o.rast, transitionFunction = function(x){100}, directions = 8)
h2o.trans.8 <- geoCorrection(h2o.trans.8, type = "r", scl = FALSE)


surv.area <- accCost(h2o.trans.8, sites)

```

