---
title: "elevations_2018"
author: "Tiff Stephens"
date: "10/1/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr); library(tidyr); library(plyr); library(reshape2); library(lubridate); library(ggplot2); library(DT); library(leaflet); library(htmlwidgets); library(htmltools); library(shiny); library(mapview); library(sp); library(sf); library(knitr); library(cowplot); library(ggpmisc); library(DT); library(plyr); library(magick)
```



\elevation \density
The true elevation of the seagrass and *Fucus* measurements were derived from knowing the elevation of the waterline at a specific time. For determining the elevation of the waterline, it is tempting to rely tidal elevation provided by a nearby tidal station -- this is fine for some sites due to their close proximity, but for others, the true waterline elevation will diverge from such measurements due to spatiotemporal influences on water movement. I corrected for this by reaching out to someone connected to the US Coast Guard and NOAA branches responsible for assessing the accuracy of marine benthic maps used for navigation. They re-surveyed a good chunk of POW in 2008, and their work required applying spatiotemporal corrections for tidal amplitude in subregions across POW (example shown below). Lucky us! 
```{r}
# import RAW data
df.elev <- read.csv("/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/Tiff/Seagrass elevation, density, biomass [2018]/elevation_density_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

```{r}
# look at structure of df. elev
glimpse(df.elev)
```

```{r}
# convert/calculate (1) MLLW feet to MLLW centimeters, (2) MLLW cm values for Fucus elevations, (3) MLLW cm values for seagrass elevations
df.elev = df.elev %>% 
  mutate(waterline_elev_mllw_cm = waterline_elev_mllw_ft * 30.48, na.rm = TRUE) %>%
  mutate(fucus_upper_elev_mllw_cm = waterline_elev_mllw_cm + (waterline_elev_stadia_avg_cm - fucus_upper_elev_stadia_cm), na.rm = TRUE) %>%
  mutate(fucus_lower_elev_mllw_cm = waterline_elev_mllw_cm + (waterline_elev_stadia_avg_cm - fucus_lower_elev_stadia_cm), na.rm = TRUE) %>%
  mutate(fucus_mean_elev_mllw_cm = (fucus_upper_elev_mllw_cm + fucus_lower_elev_mllw_cm) / 2, na.rm = TRUE) %>%
  mutate(fucus_band_height_cm = fucus_upper_elev_mllw_cm - fucus_lower_elev_mllw_cm, na.rm = TRUE) %>%
  mutate(edge_diffuse_elev_mllw_cm = waterline_elev_mllw_cm + (waterline_elev_stadia_avg_cm - edge_diffuse_elev_stadia_cm), na.rm = TRUE) %>%
  mutate(edge_continuous_elev_mllw_cm = waterline_elev_mllw_cm + (waterline_elev_stadia_avg_cm - edge_continuous_elev_stadia_cm), na.rm = TRUE) %>%
  mutate(diffuse_band_height_cm = edge_diffuse_elev_mllw_cm -edge_continuous_elev_mllw_cm, na.rm = TRUE)

names(df.elev)[names(df.elev) == 'distance_diffuse_band_cm'] <- 'diffuse_band_sloped_width_cm' # rename site columns

# calculate beach slope and diffuse band area
df.elev = df.elev %>%
  mutate(diffuse_band_horizontal_width_cm = sqrt(((diffuse_band_sloped_width_cm)^2)-((diffuse_band_height_cm)^2)), na.rm = TRUE) %>%
  mutate(beach_slope_percent = (diffuse_band_height_cm / diffuse_band_horizontal_width_cm) * 100, na.rm = TRUE) %>%
  mutate(beach_slope_angle = atan(diffuse_band_height_cm / diffuse_band_horizontal_width_cm), na.rm = TRUE)
```

```{r}
# convert all density data to meters squared
df.elev = df.elev %>% 
  mutate(shoot_density_inside_m2 = shoot_density_inside_0.25m2 * 4, na.rm = TRUE) %>%
  mutate(shoot_density_continuous_m2 = shoot_density_continuous_0.25m2 * 4, na.rm = TRUE) %>%
  mutate(shoot_density_diffuse_m2 = shoot_density_diffuse_0.25m2 * 4, na.rm = TRUE) %>%
  mutate(flower_density_inside_m2 = flower_density_inside_0.25m2 * 4, na.rm = TRUE) %>%
  mutate(flower_density_continuous_m2 = flower_density_continuous_0.25m2 * 4, na.rm = TRUE) %>%
  mutate(flower_density_diffuse_m2 = flower_density_diffuse_0.25m2 * 4, na.rm = TRUE)


colnames(df.elev)

df.elev <- df.elev[, -c(9:15,17:24)] # remove these columns
```




\biomass
```{r}
df.bmass <- read.csv("/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/Tiff/Seagrass elevation, density, biomass [2018]/biomass_cores_2018_RAW.csv", stringsAsFactors = FALSE, header = TRUE)
```

```{r}
df.bmass <- df.bmass %>%
  mutate(leaf_dw_g_m2 = (leaf_tissue_dw_beaker_g - leaf_beaker_g) * 16) %>%
  mutate(rhizome_dw_g_m2 = (rhizome_tissue_dw_beaker_g - rhizome_beaker_g) * 16) %>%
  mutate(total_biomass_dw_g_m2 = leaf_dw_g_m2 + rhizome_dw_g_m2) %>%
  mutate(leaf.rhizome = leaf_dw_g_m2 / rhizome_dw_g_m2) %>%
  select(-leaf_beaker_g, -leaf_tissue_dw_beaker_g, -rhizome_beaker_g, -rhizome_tissue_dw_beaker_g)
```


\join
```{r}
# joing two datasets together to get dates for each sampling
df.all <- merge(x = df.elev, y = df.bmass, by = c("site_code", "replicate"), all.x = TRUE)

glimpse(df.all)

names(df.all)[names(df.all) == 'site_name.x'] <- 'site_name' # rename site columns
df.all <- df.all[, -c(26:27)] # remove these columns

glimpse(df.all)
df.all <- df.all[c("site_name","site_code","latitude_N","longitude_E","so_region","date_dd.mm.yy","cage_present","replicate","beach_slope_percent","beach_slope_angle","fucus_upper_elev_mllw_cm","fucus_lower_elev_mllw_cm","fucus_mean_elev_mllw_cm","fucus_band_height_cm","edge_diffuse_elev_mllw_cm","edge_continuous_elev_mllw_cm","diffuse_band_height_cm","diffuse_band_sloped_width_cm","diffuse_band_horizontal_width_cm","shoot_density_diffuse_m2","shoot_density_continuous_m2","shoot_density_inside_m2","flower_density_diffuse_m2","flower_density_continuous_m2","flower_density_inside_m2","leaf_dw_g_m2", "rhizome_dw_g_m2", "total_biomass_dw_g_m2", "leaf.rhizome")]
```


\DataExport
```{r export}
# Data Export
write.csv(df.all, "/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/Tiff/Seagrass elevation, density, biomass [2018]/elevation_density_biomass_2018_CLEAN.csv", row.names = FALSE)
```







