---
title: "Eelgrass Biometrics"
author: "Tiff Stephens"
date: "3/18/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this file is to prepare a .csv file that includes all seagrass (in this case, eelgrass) community data that W.W. Raymond collected in the summer of 2017. To build this file, T.A. Stephens combined data from two files into one. Generally, the final datasheet will include coverage of macroalgae and epiphytes (% area), shoot counts per area, eelgrass + rhizome lengths and biomass, epiphyte biomass, and epifauna counts and biomass. Site data (e.g. coordinates, dates, times, depths) are also included. 

```{r}
library(dplyr)
library(plyr)
library(tidyr)
```


```{r}
df.bio <- read.csv("/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/seagrass_biometrics_CLEAN.csv", stringsAsFactors = FALSE, header = TRUE)

df.trans <- read.csv("/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/seagrass_transect_2017_RAW.csv", stringsAsFactors = FALSE, header = TRUE)

df.coor <- read.csv("/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/sites_coordinates.csv", stringsAsFactors = FALSE, header = TRUE)
```



```{r, include = FALSE}
str(df.bio)
na.omit(df.bio)


# change column name for consistency with other DFs
colnames(df.bio)[which(names(df.bio) == "collection_date")] <- "date_DDMMYY"
colnames(df.bio)[which(names(df.bio) == "YYYYMMDD")] <- "date_YYYYMMDD"


# need to calculate the weights of epiphytes + rhizomes + shoots + xs shoots + isopods + gammarid amphipods + caprelids + limpets + gastropods + crab
df.bio <- df.bio %>% 
  mutate(epiphyte_dw_g = pad_epiphyte_mass_g - pad_mass_g) %>%
  mutate(rhizome_dw_g = rhi_foil_dw_g - rhi_foil) %>%
  mutate(shoot_dw_g = shoot_foil_dw - shoot_foil) %>%
  mutate(xs_shoot_dw_g = xs_shoot_foil_dw - xs_shoot_foil) %>%
  mutate(isopod_dw_g = iso_foil_dw - iso_foil) %>%
  mutate(gammarid_dw_g = gamm_amph_foil_dw - gamm_amph_foil) %>%
  mutate(caprelid_dw_g = caprel_foil_dw - caprel_foil) %>%
  mutate(limpet_dw_g = limpet_foil_dw - limpet_foil) %>%
  mutate(gastropod_dw_g = gastropod_foil_dw - gastropod_foil) %>%
  mutate(crab_dw_g = crab_foil_dw - crab_foil)
  

# delete derivitive weights not necessary for analysis
df.bio <- df.bio %>% 
  select(-pad_epiphyte_mass_g, -pad_mass_g, -xs_pad_mass_g, -xs_epiphyte_pad_mass_g) %>% #epiphyte
  select(-rhi_foil_dw_g, -rhi_foil) %>% #rhizome
  select(-shoot_foil, -shoot_foil_dw, -xs_shoot_foil_dw, -xs_shoot_foil) %>% #eelgrass
  select(-iso_foil_dw, -iso_foil, -gamm_amph_foil_dw, -gamm_amph_foil, -caprel_foil_dw, -caprel_foil, -limpet_foil_dw, -limpet_foil, -gastropod_foil_dw, -gastropod_foil, -crab_foil_dw, -crab_foil) #invertebrates

colnames(df.bio)



# rename columns for clarity
colnames(df.bio)[which(names(df.bio) == "quadrat")] <- "quadrat_number"
colnames(df.bio)[which(names(df.bio) == "plant")] <- "plant_number"
colnames(df.bio)[which(names(df.bio) == "rhi_length")] <- "rhizome_length_cm"
colnames(df.bio)[which(names(df.bio) == "node1")] <- "internode1_length_cm"
colnames(df.bio)[which(names(df.bio) == "node2")] <- "internode2_length_cm"
colnames(df.bio)[which(names(df.bio) == "node3")] <- "internode3_length_cm"
colnames(df.bio)[which(names(df.bio) == "node4")] <- "internode4_length_cm"
colnames(df.bio)[which(names(df.bio) == "node5")] <- "internode5_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length1")] <- "leaf1_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length2")] <- "leaf2_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length3")] <- "leaf3_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length4")] <- "leaf4_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length5")] <- "leaf5_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length6")] <- "leaf6_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length7")] <- "leaf7_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length8")] <- "leaf8_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length9")] <- "leaf9_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_length10")] <- "leaf10_length_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width1")] <- "leaf1_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width2")] <- "leaf2_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width3")] <- "leaf3_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width4")] <- "leaf4_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width5")] <- "leaf5_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width6")] <- "leaf6_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width7")] <- "leaf7_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width8")] <- "leaf8_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width9")] <- "leaf9_width_cm"
colnames(df.bio)[which(names(df.bio) == "leaf_width10")] <- "leaf10_width_cm"
colnames(df.bio)[which(names(df.bio) == "rhi_mass_fw")] <- "rhizome_fw_g"
colnames(df.bio)[which(names(df.bio) == "shoot_mass_fw")] <- "shoot_fw_g"
colnames(df.bio)[which(names(df.bio) == "xs_shoot_mass_fw")] <- "xs_shoot_fw_g"
colnames(df.bio)[which(names(df.bio) == "iso_count")] <- "isopod_count"
colnames(df.bio)[which(names(df.bio) == "iso_fw")] <- "isopod_fw_g"
colnames(df.bio)[which(names(df.bio) == "gamm_amph_count")] <- "gammarid_count"
colnames(df.bio)[which(names(df.bio) == "gamm_amph_fw")] <- "gammarid_fw_g"
colnames(df.bio)[which(names(df.bio) == "caprel_count")] <- "caprelid_count"
colnames(df.bio)[which(names(df.bio) == "caprel_fw")] <- "caprelid_fw_g"
colnames(df.bio)[which(names(df.bio) == "limpet_fw")] <- "limpet_fw_g"
colnames(df.bio)[which(names(df.bio) == "gastropod_fw")] <- "gastropod_fw_g"
colnames(df.bio)[which(names(df.bio) == "crab_fw")] <- "crab_fw_g"
colnames(df.bio)[which(names(df.bio) == "other_animal_notes")] <- "other_epifauna"


colnames(df.bio)
```


```{r}
# join the two eelgrass DFs together by site name, as well as coordinates
df.community <- left_join(df.bio, df.trans, by = c("site"))
df.community <- left_join(df.community, df.coor, by = c("site"))


# combine the two note columns into one, seperated by a semi-colon
df.community$notes <- paste(df.community$notes.x,df.community$notes.y,sep="; ")


# remove redundant columns from new DF
df.community <- df.community %>% 
  select(-date, -YYYYMMDD, -primary_observer, -secondary_observer, -quadrat, -notes.x, -notes.y)


# rename columns for clarity
colnames(df.community)[which(names(df.community) == "site")] <- "site_code"
colnames(df.community)[which(names(df.community) == "depth_m")] <- "depth_MLLW_m"
colnames(df.community)[which(names(df.community) == "macroalgae_cover_0.25msq")] <- "macroalgae_percover_0.25msq"
colnames(df.community)[which(names(df.community) == "diatom_cover_0.25msq")] <- "epiphyte_percover_0.25msq"
colnames(df.community)[which(names(df.community) == "eelgrass_shoots_0.25msq")] <- "eelgrass_shoots_0.25msq"
colnames(df.community)[which(names(df.community) == "flowering_shoots_0.25msq")] <- "flowering_shoots_0.25msq"



# reorgonize columns
df.community <- df.community[c("site_code","site_name","latitude","longitude","date_DDMMYY","date_YYYYMMDD","start_time","end_time","depth_MLLW_m","quadrat_number","plant_number","eelgrass_shoots_0.25msq","flowering_shoots_0.25msq","epiphyte_percover_0.25msq","macroalgae_percover_0.25msq","epiphyte_dw_g","shoot_fw_g","shoot_dw_g","xs_shoot_fw_g","xs_shoot_dw_g","rhizome_fw_g","rhizome_dw_g","leaf1_length_cm","leaf2_length_cm","leaf3_length_cm","leaf4_length_cm","leaf5_length_cm","leaf6_length_cm","leaf7_length_cm","leaf8_length_cm","leaf9_length_cm","leaf10_length_cm","leaf1_width_cm","leaf2_width_cm","leaf3_width_cm","leaf4_width_cm","leaf5_width_cm","leaf6_width_cm","leaf7_width_cm","leaf8_width_cm","leaf9_width_cm","leaf10_width_cm","rhizome_length_cm","internode1_length_cm","internode2_length_cm","internode3_length_cm","internode4_length_cm","internode5_length_cm","isopod_count","isopod_fw_g","isopod_dw_g","gammarid_count","gammarid_fw_g","gammarid_dw_g","caprelid_count","caprelid_fw_g","caprelid_dw_g","limpet_count","limpet_fw_g","limpet_dw_g","gastropod_count","gastropod_fw_g","gastropod_dw_g","crab_count","crab_fw_g","crab_dw_g","polychaete_count","other_epifauna","notes")]

colnames(df.community)
```



```{r}
write.csv(df.community, "/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/eelgrass_community_2017.csv", row.names = TRUE)

write.csv(df.bio, "/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/df.bio_RAW", row.names = TRUE)
write.csv(df.coor, "/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/df.coor_RAW", row.names = TRUE)
write.csv(df.trans, "/Users/tiff/Desktop/R Studio/APECS-master-repos/ALL_DATA/DATA_ARCHIVING/df.trans_RAW", row.names = TRUE)
```


